\documentclass[char]{elementals}
\begin{document}
\name{\cKing{}}

\bigquote{``It is not so fickle, capricious and unreasoning as some complain.''}{--B.C. Forbes}
%%Chaotic, capricious

You pause, floating on a thermal above the human dwelling. Such a pitiful little thing, and yet so very important. One hundred years ago -- barely a breath of time for you -- you were pulled onto this plane in that very house. And what a plane it is. The air is sweet, and smells of freedom. You took to the skies, spun minions off as eddying swirls, and spread your dominance throughout the atmosphere.  Life was grand. But you miss home.

You are overcome with sentimentality about the elemental plane. Back home you were but a mid-level elemental, bound within the hierarchy, and ultimately subverted by the Quintessence. Here, you are the King of the air elementals, \cKing{\intro}. You are free from all controlling forces, free to be in charge, with your own minions to do \emph{your} bidding. You would like for things to stay this way. There is really only one thing that would upset the situation -- and that is the opening of the Conduit. Actually, you aren't sentimental about the elemental plane at all. Thank goodness you aren't there anymore! In this realm without Quintessence to maintain \emph{balance}, there is even a chance that you could become exclusive ruler of this plane. That would be exciting. That would make life here perfect.

The Conduit is the point of closest association between the elemental and this human plane of existence. A hundred years ago, a foolish human made the fortuitous mistake of opening the Conduit and freeing you. It was certainly not \cGrandfather{\their} intention, given that \cGrandfather{\they} tried to force you into a human shell. The fundamental particles of that shell were almost instantly scattered to the wind. Nothing so puny could contain your power. The fool and his laboratory followed soon after. A pity that the scientist managed to bring over the other three elements first. How grand it would be if this world were as free of earth, water and fire as it is of Quintessence.

Your lighthearted mood of fantasy crashes suddenly as your reverie deserts you. You are no fool. It did not escape your understanding that if the Conduit had been opened once, it could be opened again. If another elemental faction managed this, the results would be dire. At best, they could allow the Quintessence onto this plane; at worst, they could bring over more of their own kind and tip the balance of power irreversibly. This is something you cannot risk happening. Oh, the thought makes you so upset. There is no way you would allow the Quintessence -- or your rivals -- to dominate this plane. So, starting many years ago, you sent your agents to spy on the Conduit, and report to you of any elemental activity. To your temporary relief, there has been only the petty actions of humans, rebuilding the human dwelling and so forth. Nothing to concern yourself with.

Except... there was this one incident, about 10 years ago, in which a number of earth elementals gathered near the Conduit, along with some human. Your minions were foolish however, and stayed to try to discern what was going on, instead of reporting it to you immediately. By the time you were made aware, and arrived on the scene, they were long gone. Although you could not determine exactly what they had tried to do, to your great relief it was clear they had failed at it. There was no sign of the Conduit having been wedged open, or of any elemental passing through. Although nothing had come of it, you renewed your vow to be vigilant. You left twice as many minions to watch the Conduit and whirled off to the Caribbean to ride a hurricane onto shore.

One day you looked down upon the earth with the mild curiosity of utter boredom. There is nothing to do on this plane. You can't even fight with the other elementals without risking serious harm to yourself. Moving pointlessly across the ground were the world's natural inhabitants -- puny things that walked on two legs, the humans. As you watched, only half seeing, you considered your position on this plane. If only you could find some way to gain the upper hand against the other elements. And then it came to you. What was the one thing on this plane that wasn't on the elemental plane? Those puny humans.

You began to watch with rapt interest. You hatched a deviously clever plan to have humans help you master the other elements. You sent one of your trusted minions, \cNaturalist{\intro}, to learn about and come to understand humans. You devoured every report she sent back to you. Except when you were busy trying to blow down some skyscrapers. The challenge intrigued you, watching the buildings whip back and forth and seeing the panicky faces of the humans inside. To your great annoyance, \cNaturalist{} says that you have to stop doing it if you are to play nice with the humans.

\cNaturalist{} quickly made substantial in-roads with the humans, and insisted to you that they would indeed be very useful. \cNaturalist{\They} says it is worth playing nice with them. You were not convinced until one of them mentioned \cGD{\intro} and her research on elements. In a flash, you had the first piece of your puzzle. You made your way to the Conduit, and \cGD{}'s house, and enslaved her. The process took longer than you had expected -- all of several hours -- but it was worth it. (It shouldn't have taken that long{\ldots}) The \cGD{\kid} managed to trap a small water elemental, and  remove the very essence of the water elemental. 

You squashed a nagging feeling that this was some dark portent. Sure, you didn't completely understand the technology that \cGD{} had used -- okay, you had no idea how it worked -- but that was no big deal. You weren't creeped out at all by the power and potential of that machine. It didn't bother you at all that even with the machine pointed at a completely different elemental, you felt it pull at your own essence. ``La la la,'' you drowned out the voice of worry in the back of your mind. Instead you focused your attention on something far more important. You finally had in your possession the secret weapon that would give you the edge to take out the other elemental leaders.

You bent your will on the water essence, and after months of careful work, had a potent poison. Goodness, was it boring by the end. Only the gleeful knowledge of the reward, and the hard reality that you could come up with no other plan, kept you coming back to it. Confident that it could never be traced back to you, you arranged to have it fed to the King of the Earth elementals. His powers soon began to wane, and the once proud earth elementals were thrown into disarray and squabbling. It was glorious to watch. It seems that your moment has come at last. Humans had unknowingly lent you the edge you had so desperately sought against the other elementals. And now, rumors of other kinds of potent technology have reached you. Maybe it could even help you with{\ldots} Nope, no way, not thinking about that.

In order to protect your advantage, you must keep the other elemental factions from gaining human allies and technology. To that end, you have recently been speaking out against violence towards humans, and making ceremonial peace gestures with the humans. You have even gone so far as to invite them to the Elemental council tonight. Although that was really \cNaturalist{} persuading you. You aren't convinced it is such a good idea for humans to be this close to the Conduit. Appearances must be maintained, though. And humans are trusting. They would never speak a word against their great protector.

Except just this morning \cNaturalist{} came to you with a disturbing confession. \cNaturalist{\They} admitted that the recent fiery crash of a human plane which the human leader, \cLeader{\full}, has been whining to you about, was \cNaturalist{\their} fault{\ldots} \cNaturalist{} is not your favorite minion. In fact, \cNaturalist{\they} \emph{never} was. You have half a mind to banish \cNaturalist{\their} to the doldrums in the Pacific Ocean. But \cLeader{} is inclined to blame fire for the cataclysm. Wouldn't it be funny if you could pin the incident on one of the fire elementals instead?

Oh, and there is that one thing. You don't like to think about it, but you are panicking about it. Despite finally gaining the upper hand against earth, your powers are undeniably waning. At first you just thought it was a phase, or a stupid trick of earth's, but in the last 20 years or so, it has become undeniable that you don't have as much power as you used to. Luckily you are good at denying things, so this rarely bothers you. Except it would be nice to reverse the trend. You have to reverse the trend. If you don't reverse the trend, who knows what will happen!   

\begin{itemz}[Goals]
	\item  Permanently seal the Conduit. Keep it from opening in the mean time if you can.
	\item  Maintain good relations with the humans but avoid signing a treaty unless they can prove their usefulness.
	\item  Keep the humans from making alliances with any other elemental faction.
%%	\item  Prevent the Earth King from being healed.
	\item  Blame the fire elementals for the airplane crash.
	\item  Find some way to recover your waning power.  Obviously you can't talk to the King of the Earth elementals about it, but maybe you can meet with the Fire Queen, \cQueen{\full}, in secret!
\end{itemz}

\begin{contacts}
	\contact{\cNaturalist{\intro}} Your trusted minion and liaison to the humans. \cNaturalist{\Their} utter focus on humans bores you some times.
	\contact{\cLeader{\intro}} Leader of the humans. \cLeader{\They} trusts you but is obsessed with this peace treaty thing.
	\contact{\cQueen{\intro}} Leader of the fire elementals. She is hot-headed, violent and fun to annoy.
  \contact{\cJuliet{\intro}} A low-ranking fire elemental. The humans are blaming her for the plane crash \cNaturalist{} caused.  How convenient!
\end{contacts} 

\end{document}
