\documentclass[char]{elementals}
\begin{document}
\name{\cAvatar{}}

You are \cAvatar{\intro}.  You are a Cit, one of the human diplomats converging on the assembly of elementals in the hopes of brokering some kind of permanent cease-fire.

Unfortunately, you are of two minds about the proposed conference.

Literally two minds.

Ten years ago, you were one of the top police negotiators in this part of the country.  You had dealt with the most desperate criminals and even a few cornered elementals.  And then you made a mistake.  After a particularly long and frustrating day (it's always bad when somebody has to call the LN2 SWAT team to handle a fire elemental), you decided to go out for ice cream in compensation.

Your memory of what happened after about the half-way point to the ice cream shop is foggy.  There were earth elementals, and they forced you to go with them.  Enslavement is a nuisance.  There was some kind of laboratory equipment, and crashing noises, and a bright light...

You returned to your senses some time later, in the middle of a badly smashed-up lab.  The earth elementals seemed to have failed at whatever they were working on.  You met \cGD{\intro}, the scientist who ran the lab, and only returned after seeing that the elementals were gone.  The law doesn't hold you responsible for what you do while enslaved, but common courtesy compelled you to help her pick up.  It was only later, after \cGD{\they} had given you instructions on how to get back into town, that you realized just who she was descended from -- the Konrad Strauss who was responsible for bringing the elementals to Earth in the first place.  At least \cGD{\they} was reasonably concerned about the dangers that elementals posed.

The incident inspired you to push further in your work.  You moved from hostage negotiations to politics, where the stakes were at least as great.  When you started working with elementals, you discovered that you could tell them apart quite easily, unlike most of the other human diplomats.

Gradually, you realized that not all was well -- the earth elementals had succeeded better than you realized.  After a couple of years of strange flashes in the corner of your eye and an unclear voice no one else could hear, both resolved themselves with sufficient clarity that you concluded you couldn't possibly be going crazy.

You are also Vitality, an elemental drawn through the Conduit from the elemental plane to this world, ten years ago, apparently by the earth elementals.  You don't actually know this for sure; you can only guess based on what this human you're living with knows.  You are a quintessence elemental, the fifth element.  Back home in the elemental plane, the quintessence maintain balance between the other four kinds, ruling over them.  As a relatively young and weak elemental, you were sent to investigate some additional reports of strange occurrences near the place where four mid-level elementals had vanished almost a century ago.  You got sucked through something while poking around a cave, and were knocked out for a little while.  When you woke up, you realized you were sharing space with a ``human''.  You were also kind of stuck, and it took a while to figure out how to communicate with your unwilling host.

Meanwhile, you were horrified at the world you discovered.  In this world, without the quintessence to keep them in check, the other four elements have run wild.  And without the support of the quintessence, all the elementals on Earth will eventually perish.  Vitality and \cAvatar{} are in hearty agreement that elementals running wild is a bad thing.

On the other hand, \cAvatar{} doesn't mind the idea of all elementals being dead, since that would eliminate their threat to humans.  But, \cAvatar{} also recognizes that sending them all home would accomplish that goal on a much shorter timescale and with a lot fewer bodies on the deck, and is willing to go with it for now.  Both parts of you have considered the idea of bringing over more quintessence elementals to calm down all the others, but Vitality is homesick and \cAvatar{} doesn't like the idea of having even more elementals around.  That idea has been tabled for now.

As a consequence, both parts of you have been working together to find a way to stop the fighting and return balance.  Unfortunately, since Vitality is a fairly weak quintessence elemental, you can't just control every elemental in the world.  On the elemental plane, the view of quintessence by other elementals ranges from grudging respect to outright adoration, but here?  They are likely to be unhappy about having someone around who could potentially take control of them.  Worse, Vitality is afraid of being captured and forced to provide \iWhiteQ{}, the primal essence that all elementals require to sustain themselves. Without sufficiently quantities of \iWhiteQ{\MYname{}}, the elementals on this plane will die out. You definitely can't provide enough to sustain all the elementals here, but you still fear what would happen to you if your current state becomes known.

Thus, you made sure you were placed in the delegation returning to the Conduit.  Both halves of you suspect that the Conduit will be opened here again, and you hope that this is a chance of sending the elementals, including Vitality, home (@Rachel: does Vitality have any hint that this is at all possible? GD is working on this but seems like Vitality knows nothing of that).  You are willing to consider other options, but they would have to include stopping the fighting between elementals and the careless killing of humans.

You will be working under the direction of president \cLeader{\intro}, whom you have helped before in prior political negotiations.  \cDema{\intro}, another major political figure and \cLeader{}'s right-hand man, is also present.  Their intent is to seal a treaty with the air elementals, providing them with technology in return for their protection.  Both sides of you are concerned about this, especially your elemental half.  To your knowledge, no one has gained the most dangerous technologies, which would either allow control of elementals by direct enslavement or by having a source of \iWhiteQ{\MYname{}}. (@Rachel: hmm, this sentence seems to be sort of ``floating'' at present but I'm not sure what the most elegant way to connect it is. Some claim about just how far Vitality would go to prevent these from falling into human/elemental hands, or some suspicion that people might indeed be working on these techs?)

The humans are closest to making an agreement with the air elementals, and their leader, \cKing{}.  You are concerned that this may tip the balance, allowing the air elementals to gain too much power.  You are also concerned about the ambitions of fire, as always.  They will be in attendance, though you have not worked with them personally on this plane.  You have had some prior contact with \cLoyal{}, whom you know will be representing the earth elementals and their King, \cEarthKing{}.  Given that they were responsible for your current condition, you're both angry with them and concerned you might be recognized.  The latter hasn't been a problem in your work with them so far, including a visit to \cEarthKing{}'s court,  and you've managed your anger.  \cLoyal{} has mentioned some concerns about the degradation of the strength of elementals during their tenure on Earth, and may be helpful in solving the ``elemental problem''.

Since this is a major event, you have also been assigned an expert Azi diplomat, by the name of \cDiplomat{}.  \cDiplomat{\They} is, of course, a focused and skilled negotiator, and has been working primarily with the air elementals.  You're also aware that \cDiplomat{\they} was subject to an unauthorized, fast re-taping a number of years ago.  The details aren't known to you, but you do know that the repair process afterwards is long and complex, and even then, the victim is typically left with permanent mental scars.  While you have seen little evidence of such problems so far, it is possible that the high-stakes negotiations that will be happening soon may trigger something.  Since you consider \cDiplomat{} a friend and colleague, you are naturally concerned.

Unfortunately, there's also one more wrinkle that you need to keep in mind.  \cGD{} reported to you that \cGD{\they} was recently enslaved by an elemental for unknown purposes.  \cGD{\They} is fairly certain that \cGD{\they} was enslaved by a powerful elemental, and that \cGD{\their} equipment was used to seriously wound or otherwise affect a water elemental.  \cGD{} doesn't remember what happened, and there were no elementals around when \cGD{\they} recovered \cGD{\their} senses.  All you are certain of is that this is unusual behavior for any elementals to clearly target specific humans and use their technology.  You so far have chosen to keep this fairly quiet, at least until you have a better idea of the implications of what happened.  The incident might also be a useful lever in negotiations at some point or to help \cGD{}, if you can figure out what happened.

While \cAvatar{} is usually the one in control, since \cAvatar{\they} has more experience operating a human body, Vitality will often produce a hallucination of a bright light and a speaking voice to get a point across.  \cAvatar{} has developed something of a reputation for talking to \cAvatar{\themself}.

%Matt: can Avatar accomplish goal #1 without granddaughter? If so, how, and if not, then might want to make avatar aware that s/he'll need to seek her out (there are some suggestions towards this end already, but might want to make it less subtle as the GD is already going to be a bit secretive).  -- Agreed.  And, given the problems if GD dies, it'd be good to have a backup plan.

%Goal #2 is also interesting and it's likewise something to ponder what the avatar needs to accomplish it. One method is using the GD's electromagnet. We could go down the route of it being possible for Vitality to be ``externalized'' as a new NPC.  -- Yeah, the idea here was something to do with the electromagnet, but an alternative might be a "tug" felt while the Conduit is held open.

If you choose to explain your joint condition to someone, once they know that you are both \cAvatar{} and the elemental Vitality, tell them to open their \mUnstickAvatar{}.  (If they don't have one, then don't worry about it.)

Psychlim:  If think you are alone, take the opportunity for \cAvatar{} and Vitality to have a chat, since just talking is easier for \cAvatar{}.  If \cAvatar{} says or does something Vitality objects to, Vitality wants \cAvatar{} to do something \cAvatar{\they} finds objectionable, \cAvatar{} will ``talk to himself'' regardless of the presence of others.  Volume should be proportional to the intensity of the disagreement.

Another limit is not psychological.  If you choose to attack or defend using a CR greater than 2 (plus any technological weapons or defenses), you are using Vitality's abilities in addition to \cAvatar{}'s.  In this case, your \aGlowInDark{} ability is automatically activated, and your attack is suitably glowy.  You should make sure this is clear to any players who can see you.

\begin{itemz}[Goals]
	\item  Send all the elementals home.  Or, short of that, find some other way of restoring balance.  \cAvatar{} thinks letting them all die is a reasonable solution, though Vitality doesn't like it.  You'll probably need a scientist's help to do this.
	\item If you think the situation is starting to get out of hand, you think you could summon one of your Quintessence brethren from the elemental plane during a \emph{momentary opening} of the Conduit. If things are spiraling \textbf{really} out of control, you might even consider summoning one of the elder Quintessence elementals during a \emph{terminal opening} of the Conduit. Either way, you don't currently know how to work any of the machinery that can open the Conduit.
	\item  Find a way to separate Vitality from \cAvatar{}. %(@Rachel: We chatted about this briefly. Do we still want this as a goal? Maybe some indication that this is something that should happen towards the end of the conference?)
	\item  Prevent the humans from giving too much power to the air elementals.  This may require delaying or dismantling the potential treaty with the air elementals, or potentially supporting the earth elementals as a balance to air.
	\item  Find a way to keep the humans out of the elemental mess and protect them.  This may require supporting the potential treaty with the air elementals.
	\item  Since you're going to need all the help you can get, try to find anyone willing to join the cause of returning the elementals home.  The earth elementals you already know might be a good start.
	\item  Help \cDiplomat{} avoid undue mental stress.
	\item  Get some mint-chocolate chip ice cream.  You're pretty sure that after all this, you're going to want some.
\end{itemz}

\begin{contacts}
	\contact{\cLeader{}}  The elected leader of the majority of humanity.  You are working under \cLeader{\their} leadership towards establishing a treaty.
	\contact{\cDema{}}  A well-spoken politician.  \cDema{\They}'s more prone to flowery speeches than you would like, but the \cDema{\human} generally has a good point.
	\contact{\cGD{}}  The scientist you met after being merged.  \cGD{\They} has an unlovely reputation due to \cGD{\their} ancestor's actions, but the related expertise in elementals and the Conduit will be essential.
	\contact{\cLoyal{}}  An earth elemental you reached out to.  \cLoyal{\They} is currently representing the earth elementals, in the absence of the Earth King.
	\contact{\cDiplomat{}}  The Azi diplomat assigned to work with you.  You are \cDiplomat{\their} supervisor.
\end{contacts}

\end{document}
