\documentclass[char]{elementals}
\begin{document}
\name{\cDiplomat{}}

You are \cDiplomat{\intro}, an established Azi diplomat.  You're the behind-the-scenes person, there to smooth things over and open up previously blocked lines of communication.  You may look like a go-fer at times, but you relish the subtle manipulations that help make the world that much better.  It's what you were made for.  And now you're at the laboratory of the man who started the elemental problem, looking for a way to change the elementals from a problem to allies.

You have had your own troubles.  Three years ago, your driving sense of purpose was shattered.  Your memory of the event is almost entirely lost.

You were retaped, rapidly, violently, unwillingly, by a person or persons unknown, for uncertain purposes.  It's suspected that some sort of general mind-control technique was being tested by taping you to use it, but the precise details are unknown even to the investigators.  For you, it is probably best left that way.  The repair of your mind afterwards, a slow, careful taping combined with psychotherapy, has been largely successful.  Nonetheless, triggering the buried memories is likely dangerous to your sanity, as is severe psychological stress.  At times, you can still feel the echoes of that lost experience -- a strange, twisted desire to make other beings into your puppets.

But today is not the day for madness.  You have been working with \cNaturalist{\intro}, an air elemental who is impressively fond of and careful around humans.  While many elementals are as careless around humans as humans are around anthills, you have found in your interactions with them, and especially \cNaturalist{}, that they can be willing friends, if slightly strange sometimes.  You had to teach \cNaturalist{\them} how to use a pen, for instance.  You've been successful in convincing President \cLeader{\intro}, your supervisor \cAvatar{\intro}, and others that an alliance with the elementals can be forged, and that the air elementals are the most amenable.  \cAvatar{} has been working more with the earth elementals than air, but the president is very supportive of your efforts in this area.  You get along well with your supervisor, but \cAvatar{} has a problematic habit of talking to \cAvatar{\themself}.

You are a bit worried about having \cDema{\intro}, the Secretary of State, here.  \cDema{\They} is truly charismatic, but you worry \cDema{\their} rhetoric may get people too worked up.  Excited elementals have a tendency to break things on accident.  That, and you are concerned that \cDema{}'s more flamboyant gestures may distract from the main point.

Of course, it is your hope that the air elementals are only the start.  You also see great, and surprising, promise in working the with fire elementals.  In particular, you caught \cRomeo{\intro}, \cLeader{}'s Azi bodyguard, and \cJuliet{\intro}, a fire elemental, making out several months ago.  You didn't realize fire elementals could do that...  Anyway, you think this is awesome.  You've been helping them meet in more private areas, until they're ready to go public.  You're encouraging them to do so.  After all, what helps cross cultural boundaries better than a good love story?  The idea of fire elementals as passionate rather than destructive could go a long way.  Your position as a diplomat authorizes you to officiate at human weddings.

With such lofty goals, it follows that there will be obstacles.  You know you can handle them, but they are still a nuisance.  The most serious one you see at the moment is a recent incident involving an airplane crash over Hawai'i.  All the evidence so far points to elemental involvement, rather than mechanical failure or pilot error.  It's made a serious mess, and a lot of people are reflexively blaming the fire elementals.  You know that \cScientist{\intro} has been working on solving the problem, and figuring out exactly what happened.  You'll want to know \cScientist{\their} results as soon as possible, so you can control the fallout.  \cScientist{} is a good friend of yours, since before the retaping incident, who has discussed \cScientist{\their} discoveries with you before.  \cScientist{\Their} help has been invaluable in helping understand what all this new science stuff is doing.  In turn, you have helped \cScientist{} evaluate the possible ethical and political ramifications of \cScientist{\their} work.

Occasionally, when \cScientist{} has too many people pestering \cScientist{\them}, you step in to make sure \cScientist{\they} get enough space to think and work.

%%My head hurts. Could we maybe reword that last sentence? It seems very confusing to me.

You also need to make sure that you know about, and can smooth over, any other issues that might pop up to threaten the treaty or good relations between humans and elementals.  From past experience, the easiest way to doing that is to know everything about everybody.  You can't solve a problem if you don't know about it.  Besides, knowledge is power, and it's always good to have extra bargaining chips.  You're not above blackmail, but you realize that it's not a good long-term solution and therefore won't use it except as a last resort.

\begin{itemz}[Goals]
	\item  Secure a long-term treaty with the air elementals.
	\item  Learn as much as you can about the plans and psychology of elementals.  You need to know everything that could impact human-elemental relations.
	\item  Find out what elementals were responsible for the downing of an airplane, and prevent this from harming interspecies relations.
	\item  Promote the cross-cultural romance!  With the consent of the parties concerned, of course.  A big, public wedding would be best.
	\item  Help \cScientist{} with \cScientist{\their} research, and make sure \cScientist{\they} keeps you up-to-date on the latest developments.
	\item  Avoid undue stress, which may trigger a mental relapse.
\end{itemz}

\begin{contacts}
	\contact{\cLeader{}}  The elected president of the free world.
	\contact{\cDema{}}  The Secretary of State, and second-in-command at this gathering.
	\contact{\cAvatar{}}  Your supervisor, and the senior diplomat present.
	\contact{\cScientist{}}  An expert Azi scientist and a close friend.
	\contact{\cNaturalist{}}  The air elemental you know best. 
	\contact{\cRomeo{}}  The Azi who has fallen in love with a fire elemental.  Also \cLeader{}'s bodyguard.
	\contact{\cJuliet{}}  The fire elemental who has fallen in love with a human.
        \contact{\cQueen{}}  The leader of the fire elemental faction.
        \contact{\cKing{}}  The leader of the air elemental faction.
        \contact{\cEarthKing{}}  The leader of the earth elemental faction.
\end{contacts}

\end{document}
