\documentclass[char]{elementals}
\begin{document}
\name{\cElderQ{}}

You are an elder quintessence elemental, an immense white ball of quintessence living on the elemental plane.  Your solemn task is to keep the other types of elementals in perfect balance.  Though their nature is to be in conflict, and it is not possible to fully suppress that, great care must be taken by all of the quintessence to control their small conflicts to avoid a devastating conflagration. Being an elder, you are in charge of the most serious of conflicts. Smaller spats are left to your younger brethren.

One day, you were surveying the vast territory of water. Suddenly, you sensed a vortex in the distance. This vortex took a form you had never witnessed before in your considerable lifetime, so sensing the potential for trouble you went to investigate the disturbance. You found what seemed to be a hole in space, and felt a powerful song calling you to the other side. Sensing a strong imbalance in the elements on the other side, you propelled yourself through the tunnel and after being pulled through space along dimensions you do not fully understand, you appeared in a strange, alien cave.

Your powers are weaker than they should be here, but they are still formidable. Upon arriving you immediately encountered some fleshy beings and elementals from several different factions. There were also some odd metallic devices scattered about. Things are very wrong here --- there are almost no quitessence here, and the four primal elementals should \textbf{never} be unsupervised! You do faintly sense a fellow quintessence elemental, but he or she is very weak. You are in charge here, and you are going to have to figure out what is going on very fast.

If these elementals have been without quintessence for so long, they are likely starting to suffer the effects of \iWhiteQ{} deprivation. Without this substance they will eventually die out, but they are probably starting to realize that they disparately need \iWhiteQ{\MYname{}} to survive.

What are these fleshy things that aren't elementals?

Your CR is 7. You can still be enslaved if someone uses an enslave attack against you higher than your CR (see ``The Elemental Enslavement Mechanic'' greensheet and your corresponding enslavement ability).

You start the game immediately after having left the elemental plane and arriving on this alien world. The connection which brought you here promptly seals shut behind you.

\end{document}
