\documentclass[green]{elementals}
\begin{document}
\name{\cElder{}}

You are Blaze, one of the most powerful fire elementals on the elemental plane and the daughter of Vul, the Primal fire elemental who rules over the entire fire elemental hierarchy. In your thousands of years of life, you have gained vast understanding, and should Vul one day fade away, you are situated to replace him.

You are a paragon of the traits of Fire. In you, they are exaggerated in their purest fashion: you are brazen, forceful, and few can stand in your presence for long without backing down or being burned. The only order that you respect is the hierarchy itself. You do not appreciate the Quintessence elementals, but you are too busy dealing with the complexities of the fire hierarchy to concern yourself with them much.

One day, you were surveying the vast territory of fire. Suddenly, you sensed a vortex in the distance. This vortex took a form you had never witnessed before in your considerable lifetime, so naturally you went to investigate the disturbance. Much to your shock, upon arriving you found yourself pulled into it, and upon realizing that despite your immense power you could not resist its pull, you pushed yourself forward. You are afraid of nothing, and as this anomaly might pose a threat to the hierarchy, it is your duty to investigate it and stop the threat by whatever means possible. Nothing else is important to you, even your own life.

After being pulled through space along dimensions you could not understand, you found yourself appearing in a small enclosed room. Your powers are weaker than they should be here, but they are still formidable. Upon arriving you immediately encountered some fleshy beings and elementals from several different factions. There were also some odd metallic devices scattered about. The other factions do not concern you, but you sense that things in the fire hierarchy have reached an unacceptable state. You intend to immediately get to the bottom of this situation. You can feel that the strongest fire elemental here is your granddaughter \cQueen{\intro}, and she bears the full responsibility for allowing things to degenerate as far as they have. You are very, very displeased with her.

Your CR is 12. You can resist all attempts to be enslaved, with the exception of three Enslave A abilities used in conjunction. You are not sure what these fleshy things are (you should interrogate \cQueen{} about that), so you intend to leave them alone unless they annoy you. You have a special enslave ability called Dominate that allows you to order around a single target (most likely \cQueen{} although you could control someone else if you feel like it, but doing so frees the previous victim).

You do not yet know what to make of this bizarre new reality you find yourself in, but you intend to take control of the situation as quickly as possible. 

\end{document}
