\documentclass[char]{elementals}
\begin{document}
\name{\cGD{}}

You are \cGD{\intro}. To your friends, you are an accomplished Cit scientist. Unfortunately, the vast majority of the human population knows you not as a researcher, but only as the great granddaughter of the infamous Konrad Strauss, the eccentric scientist who was responsible for humanity's first encounter with the elementals one hundred years ago. No matter what others say, you have always admired your grandfather's work despite the trouble it has caused. While Konrad has often been vilified as mad and dangerous, you have every intention of building upon his work and using this knowledge to fix ``the elemental problem''.

At present, you are making your way to a converging assembly of elementals and humans at the ruins of your great grandfather's lab. You are not certain exactly what everyone else is planning to accomplish here, but you have spent over a decade making preparations for exactly this day and are very, very anxious to see them through.

%Several years after the incident, your grandfather was murdered by an Azi who was forcibly re-taped by a criminal who was never caught. 

For as long as you can remember, you have been fascinated with elementals. Where did they come from, why are they here, and how do they work? These questions always called to you as a young child, and as a budding researcher they became an important focus for your work. In particular, you are the leading expert on the Conduit, the mysterious connection between Earth and the elemental planes. As far as you have been able to determine, this connection was first established in the incident 100 years ago in your grandfather's lab, but for most of the time it remains dormant and closed. From your studies, you have determined that approximately every 10 years Earth and the elemental planes again become close enough that a connection can be formed. Disconcertingly, your simulations have also shown that this connection between Earth and the elemental planes is quite unstable -- continued use of the Conduit is very likely to cause unrepairable damage the fabric of space with ramifications you wouldn't even dare to guess.

Your lifelong study of elementals has revealed a myriad of discoveries. But one trend stands out above the rest: the elementals appear to be getting weaker. It's not very noticeable on small time scales, but their powers are definitely subtly diminishing. As far as you can tell, something important to the functioning of elementals is simply not present on Earth. According to your projections, they may reach a critical point anywhere between 50 to 100 years from now. Without a more rigorous study with willing elemental participants you can't be sure, but you also believe that the elementals whose powers start to rapidly fade are likely to exhibit extremely unstable and erratic behavior (even for elementals). The potential devastation they could cause in such a state is enormous, but unfortunately this steady decline is not something that is widely agreed upon or has been well publicized. You have only discussed it with a few close colleagues who have agreed that if the elementals aren't already aware of their decline, it will do humans little good to point it out to them.

Realizing the dangers caused by use of the Conduit and the presence of the elementals in general, over a decade ago you decided that there is only one safe course of action: you must send all the elementals back home. This is no easy task, but with the help of your great grandfather's research, you are confident it is possible. Working off one of Konrad's more outlandish designs, you have been developing a device that has the potential to function as a super-powered electromagnet that is attuned to elemental beings. Your experiments to date have been met with one rather critical problem: there is no source of power on Earth big enough for your electromagnet to run even close to full capacity. To make it work, you will have to use the Conduit to connect it directly to the elemental plane. In theory, it can use this connection to pull the vast majority of the elementals to it and channel them back where they came from. In practice, you are not quite certain such a thing will work, but you have been working tirelessly to overcome the considerable engineering challenges needed to make the device function correctly. Considering the implications of your project and the likely violent reception it would receive from the elemental factions, you have also not been overly vocal with describing it to others.

TODO: The paragraph below doesn't really fit anywhere and breaks the flow wherever I try to put it. Find a good place for it or remove it.

Partially motivated by your great grandfather's rather abrupt demise, you take your science very seriously. Especially in a day and age when humanity is stretched thin, there have been quite a number of horror stories involving scientists who went beyond the bounds of acceptability to accomplish their goals. The worst of these involve using unwilling human subjects, forcibly retaping Azi, or conducting research without appropriately strict safety protocols, resulting in disfigurement, dismemberment, or even death. It is very, very important to you that science be perceived in a positive light and that those who conduct such research hold themselves to uncompromisingly strict ethical codes to make up for the damage already done. You have trouble containing your hatred for anyone who acts carelessly when dealing with dangerous areas of scientific research, and if you were to ever discover that a scientist \emph{intentionally} risked someone's life in the name of scientific progress, you would have to restrain yourself from murdering them. You are notoriously watchful of the scientists who you work with, and given your growing prominence within the scientific community and your complicated person history, most of those you interact with are quite cautious indeed.

%At the very least, you would see them publicly exposed, prosecuted, and imprisoned, with their lab and funding disbanded forever. 

%Given your grandfather's murder, even the thought that a scientist might conduct a rapid retaping of an Azi gets your blood boiling. 

Given its geographical significance, a natural place for you to conduct your research is your grandfather's laboratory. Twelve years ago, you began restoring Konrad's lab space and moving key parts of your own research equipment there, preparing to gather important experimental data from the next Conduit opening. This was going quite well indeed and preparations were complete, until the day before the Conduit opening ten years ago. On that day, a pack of relatively high-tier earth elementals showed up accompanied by a captive human. Wisely realizing the need for caution, you fled the premises before they could notice you. To your dismay, you watched from a distance as they attempted a limited opening of the Conduit using your infrastructure. They left shortly afterwards. Returning to your lab, you were infuriated to see the damage they had wrecked to your equipment. You still managed to salvage some data, and your logs showed that \emph{something} transferred through the Conduit, although you don't really know what it was or even which direction it was traveling in.

Shortly after you returned to the lab, the human who had been accompanying the earth elementals also came back and introduced \cAvatar{\themself} as~\cAvatar{\intro}. \cAvatar{\They} was kind enough to help you pick up the mess, but seemed to have equally little idea what the earth elementals were trying to accomplish. After doing some basic checks to make sure the enslavement had fully faded from \cAvatar{\their} mind, you saw \cAvatar{\them} safely to a nearby town. You haven't kept in touch, but when you saw the list of humans attending this elemental gathering, you were pretty surprised to learn that \cAvatar{} is now the head Cit diplomat.

You decided to take what equipment you could salvage back to safer human-controlled territory and haven't been back to your grandfather's lab in ten years; but in all that time you still haven't exactly forgiven the earth elementals for the damage they caused and the recklessness with which they opened something as dangerous as a conduit between two planes of existence. You still intend to find out exactly what they were trying to accomplish and what they moved through the connection.

Research had been going quite well since then, until three months ago when you had a very unsettling experience. One minute you were sitting in your lab, working on your electromagnet. Two hours later, you were recovering on the floor in a pool of water. Doing a quick MRI, you discovered that your brain had psionic reside consistent with enslavement by a fairly powerful elemental. While it's true elementals occasionally enslave humans who wander away from protected human encampments, for them to sneak into a human facility and so selectively target a single human is practically unprecedented. Even more mysteriously, upon investigating the pool of water on the ground, it appears to belong to a \emph{wounded} water elemental. After extensive investigation, your best guess is that for reasons unknown to you, one of the other elemental factions used your electromagnet to wound or otherwise affect a restrained water elemental. There were small signs of a struggle, but it's not clear if the water elemental managed to break free or was dragged away. Either way, you reported the incident to \cDiplomat{\intro}, an Azi diplomat who you have found to be quite capable and trustworthy. Nonetheless, none of the elemental factions have claimed responsibility and at present, the incident remains a disturbing mystery.

Given your research experience, you were a natural choice to be on the team returning to the Conduit site. The science team you are a part of contains two other elemental experts: \cMS{\intro} and \cScientist{\intro}. \cMS{} is an extremely troublesome individual and a terrible collaborator. Based on your investigations and past experiences, you are quite confident that without oversight, \cMS{\they} would ignore any number of safety and ethical concerns if it served \cMS{\their} purpose to do so. You are not really certain what \cMS{\they} is up to at the Conduit, but you suspect it is probably both reckless and dangerous. On the other hand, \cScientist{} is an Azi scientist who you quite enjoy working with. Personable, intelligent, and very focused. Like most Azi, \cScientist{\they} also understands the need for not allowing political pressure to interfere with doing science properly and safely.

Officially, on this expedition the three of you report directly to the president, \cLeader{\intro}. Although it is not an official capacity, in the past you have occasionally acted as a sort of science advisor, bringing scientific matters that are politically sensitive to \cLeader{}'s attention. You are not sure how receptive \cLeader{\they} will be to your plans for the elementals, but you also hope to bring \cLeader{\them} on board, if you can. Also present at the conference is \cDema{\intro}, \cLeader{}'s 2nd in command and a most unpleasant politician. \cDema{\They} is always pushing for more aggressive and dangerous research, and you fear that if \cDema{\they} had \cDema{\their} way, there would be no checks on the types of experiments that would be carried out in the name of military progress. Fortunately, \cDema{\they} has little influence over what types of research actually gets done, and if you have anything to say on the matter, it will stay that way.

Considering the dangers involved, you are extremely concerned that elementals are taking such interest in the site and are determined to make sure that both elementals and humans realize just how serious things are. But more than anything, you are immensely nervous: you have been testing your electromagnet device for many, many years and have been preparing for exactly this day. In a few hours, if things go as you have been planned, tomorrow is going to be a much, much better day for humans.

%You don't really know what to think of the elementals, but it could be exciting to have closer conversations with them; given their physical prowess and mental enslavement abilities, most humans including yourself rarely have the opportunity to interact with elementals closely. 

%does GD have a mempacket regarding rogue/loyalist, who she saw trashing her lab?

\begin{itemz}[Goals]
  \item Restore your family's good name by completing and activating your electromagnet to send all the elementals back through the Conduit.
  \item Find others who realize your plan is the best course of action and convince them to help you. %this is its own goal because getting ``popular support'' for your plan is important, ideally she doesn't want it to just come out of the blue.
  %\item If you can't send the elementals back, instead try to seal the Conduit to prevent a future catastrophe.
  \item Figure out why the elementals are dying. Discuss this problem with the human diplomats to see how the elementals might react to the news.
  \item Find out what the earth elementals did at the Conduit ten years ago.
  \item Find out what happened in your lab three months ago.
  \item Investigate all other scientists to make sure they are conforming to ethical standards. Bring all ethical violations to the attention of the leading government officials.
\end{itemz}

\begin{contacts}
%These are longer descriptions than a contact list should be -- I'm working on incorporating this text into the main body.
  \contact{\cLeader{}} The elected leader of the majority of humanity.
  %Reasonably charismatic, and respectful enough. More importantly, \cLeader{\they} doesn't try to directly interfere with scientific research or push it faster than it is safe to do so.
	\contact{\cDema{}} An unpleasant politician.
	\contact{\cMS{}} A Cit scientist who specializes in understanding the mechanisms by which elementals can exert mental control over both their own species and humans. \cMS{\They} is always a vocal supporter of \cDema{}'s views on scientific research.
	\contact{\cScientist{}} An Azi scientist who specializes in elemental chemistry. You have had good experiences working together in the past.
  \contact{\cAvatar{}} The human who you first met in your great grandfather's lab ten years ago. Now a prominent diplomat.
\end{contacts}

\end{document}
