\documentclass[char]{guildcamp1}
\begin{document}
\name{\cGroomB{}}

It took a long time, clambering your way up to the top. Growing up, your family had little to call their own but faith in Virtuism and patriotism, but they clung to those things like the flesh on a peach pit, and by golly, it was just enough. You remember the itchy, hand-me-down sweaters and the soda-cracker lunches with a mixture of nostalgia and embarrassment. But you worked hard in school, choosing to turn your back to the drugs and the gangs, and eventually qualified for the North Summit Military Academy, the most prestigious in the country.

You graduated with flying colors, and became an Engineer of the Army. Your advances in the safety training for Air Force cadets gave you a good reputation, and your business savvy helped to balance the military’s budget.

It was while working for the Army that you met \cScientist{}, a woman of such fierce passion for life that you could even overlook her atheism. She was a contracted military scientist and you were an officer-in training, and the day she looked you in the eyes and called you Lindy-loo, you were sure you were in too deep.

Was it wrong, to feel that way about someone who had abandoned the Virtuous Teachings? You weren’t sure, but after holding yourself in reserve for so many years, perhaps it was healthy to let your heart have its say for once.

So, your heart had its say. Again and again, it had its say, and it was clear that she felt the same way. You loved her for years, and considered making her your wife. You didn’t particularly want to have children, but though your religious practice had dampened as you brought \cScientist{}‘s life into your own, you still felt guilty that your relationship was spiritually unconfirmed. You sometimes tried to bring it up, but \cScientist{} always shot you down. She was utterly disenchanted towards the Virtuism and all it entailed, including traditional marriage. “We’re together, love,” she’d say. “How would marriage change anything except make it more complicated?”

You stayed with her through two wars, keeping you both busy at your desks, drafting budget estimates and programming self-navigating ships. It was during this second war that the military began having difficulties with funds. It had overextended itself, nearly bankrupting the country, and you began receiving more and more desperate requests for funding.

It seemed that the only way to fix the problem was to dip into the private sector, and you found many buyers interested military technology, delivered covertly. It was only partly legal, what you were doing, but in the current political climate, it seemed that it was the only way to keep the war effort afloat.

You never told \cScientist{}. You were putting yourself at risk, and it wasn’t worth endangering her career as well. But she was so observant, she eventually found your records, and confronted you about it. You were calm, and kept a level head as always, but she was belligerent, and you began to lash out.

That’s when she dropped the bomb: She was pregnant.

You didn’t believe it. You thought perhaps she attempting to blackmail you, lie to you, convince you to give up the under-the-table deals now that your futures were incorrigibly entwined. You blamed her. You were always safe, she must have done it on purpose, must be resenting his successful career, must be trying to prove some kind of point.

She slept on the couch for the night, then walked out of the apartment and out of your life. She never asked for paternity payment. You sometimes wonder what happened to her, and if she really bore your child. The thought fills you with regret, but you’ve gotten good at avoiding thinking about it.

Years later, your heart had healed, and one day you walked into a coffee shop and met \cBride{}. \cBride{} was nearly half your age, and she wasn’t wealthy, but her faith was strong. She reminded you of yourself, at a younger age. But she had such confidence! She held herself with poise, and always gave out an air of mystery. You were hooked, and soon intoxicated. You felt like a young man again, and six months into your relationship, you proposed. To your amazement, she said yes.

Meanwhile, your military tech business was booming. You were supplementing the army’s funds just enough to keep them quiet, and scraping some cream off the top for yourself. Sweaters and soda crackers were a thing of the past. Now you wore name brand suits, and dined on caviar! And now, Li Timpeh, a political party from an unstable country, was looking to buy a new military AI Drone, and they were offering serious, hard cash. What they wanted it for was none of your business.

Unfortunately, the only time the foreigners were going to be in the country was during the wedding, so you had to bring the AI prototype with you, and keep it at the Hotel Virtuoso, where you are to be married. But you aren’t worried. You are the only one with a key, and no one suspects a thing. You haven't seen your contact yet though. If Nava doesn't turn up, you just might find a different seller. If anyone caught you with the technology you would have a hard time explaining yourself. It has to be passed off to someone-for the right price of course.

You’re not entirely sure what happened next. There you were, about to marry a beautiful young woman, not to mention about to seal one of the biggest transactions of your career.  Your tux fit like a glove, the paperwork was signed, and you felt 15 years younger. Everything was perfect.

You were just going in to check on the prototypes. Your key was in the door, you were about to open it, when, very suddenly, you heard an alarm ringing in your ears, and everything went black. The next thing you knew, you were lying in a cold metal box, the alarm still blaring.

You sat up, but everything was wrong. You were too short, your arms the wrong length. You looked at your hands, and they were not your hands.

You turned your head, and a horrible, half-metal, half-plastic man was sitting up next to you, and it screamed at you in the voice of your hired pastor, \cPastor{}. You leapt out of the coffin-like box, scattering the dust that had settled on your limbs. All about you were panels with buttons, like the cockpit of an airplane. Were you dreaming? Was this a nightmare?

The room had no door and no window. You were trapped, and you sat in your metal box next to the moaning robot for some time, before you realized that you had to do something.

You stood up and went to the wall. There, you pushed some of the buttons, desperate to find a way out, and the screens lit up with lines of some code you didn’t know. You tried to recall your schooling from decades ago, and type in some lines, but the system was all different. 

Eventually, the screen went blank, and the alarm stopped. A voice said, quite clearly:

\emph{EMERGENCY SHUT-DOWN INITIATED. FOUR HOURS OF BATTERY LIFE REMAINING.}

Then, everything went black.

When you opened you eyes, you were in the hallway outside of where you were keeping the Drone blueprints. What happened? Did you faint? You quickly left for the bar to get something to calm your nerves. Over a gin on the rocks you resolve to figure out what happened. That place was scary and foreboding, but as a technology expert for the millitary, you are itching to return there and learn all you can about it. Not that your fiance would understand, she adheres to the tennants of Virtuism even more strictly than you do, and cringes every time you mention the millitary technology you work with day to day.

This is supposed to be the happiest day of your life, and something has gone horribly wrong.

\begin{itemz}[Goals]
  \item Get married to \cBride{}, according to the ceremony of your shared religion. You love her, she loves you, and you want your special day to go as smoothly as possible.
  \item Sell the millitary AI drone to  someone. Peferably your contact from Li Timpeh, but if they don't show...
  \item Find out what the heck is going on, and get back into that room full of consoles and buttons.
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cBride{}} This is your fiancée. You love her dearly.
  \contact{\cScientist{}} Your old flame. You wonder what happened to her?
  \contact{\cPastor{}} The pastor you hired to minister the wedding. A well-respected and holy man. You have no idea why you would dream about a robot with his voice.
  \item Nava: Your contact from Li Timpeh. He should be showing up at some point.
\end{contacts}

\begin{itemz}[Notes]
  \item For this character, please dress in blue jeans and a white collared shirt.
  \item The Groom's bank account \# is 20-89-59
\end{itemz}


\end{document}
