\documentclass[char]{guildcamp1}
\begin{document}
\name{\cKid{}}

You are seven years old, and just started school. Boring. You'd rather be outside playing ball, or running around, or better yet, finding dinosaurs, or traveling to outer space. At least you still get plenty of time to color, one of your favorite things to do. Your room at home is covered in drawings of space ships. Your really favorite thing to do is spend time with mom, \cScientist{}. She's really busy with her work though, so you don't get to hang out very much. Mostly you spend time with your nanny, who is fun too, you guess. When you get to spend time with mom, going out for ice cream or something, it's always great. It's nice to get away from all those noisy computers.

You've been feeling kind of lonely lately. You don't get along very well with anyone at school. They all make fun of you for how you dress. They are all very preppy and afraid to get mud on their expensive clothes.  Also, no one understands how smart your mom is. Your mom has been worried about a lot of things too. Her work has been kind of stalling, and she spends an awful lot of time at the doctor's. She gets sad and cries at night. You wish she wouldn't because it's scary. You are really worried that something is wrong. Since you rarely see her anymore, when she told you that the two of you were going to a hotel together, it made you very happy.

Today is going to be especially great. You are on vacation with your mom at this fancy hotel, and you are going to meet your dad! You got off school, and get to spend time with mom too. Your nanny is nice and all, but you love your mom. And just last month your mom started telling you all about your dad. A dad. A real dad. All yours. How exciting! His name is apparently \cGroomA{}. You have never met your dad, in fact you didn't even know you had one until mom told you. You've grown up seeing other kids with their dads and seeing people playing with their dads on TV, and you've always wanted to have a dad too. So when your mom told you that she's going to take you to meet your dad, you got really excited.

But today isn't going the way you thought it would at all. You arrived at the hotel, and mom had to run off immediately, muttering something about some \cRival{\human} named \cRival{}. Mom really doesn't like him. He must be bad.

You've been running around by yourself, which is not very much fun, and even worse, you just found out that your dad is getting married to SOMEONE ELSE! This is horrible. This is not what you were thinking at all. You thought that meeting your dad meant that he'd get back together with your mom and be like a real dad to you, like the dads you've seen on TV. Maybe if you stole that wedding ring that the horrible woman your dad is about to marry has, you could ruin the wedding. Then surely your dad would see that he really should get back together with mom instead.

At least one good thing has happened though. As you were wandering around, you found a teddy bear sitting all alone on a bench.  He looked so lonely and in need of a hug, so you picked it up. Whoever abandoned the teddy bear must have been very mean, it was probably an adult. They don't seem to care about stuffed animals at all. It's like they don't see that they have feelings too. You wont let any grown up take the teddy bear because you are sure they will just mistreat him again. You found the teddy, which makes it rightfully yours. No one is going to take him away from you.

All these grown ups are running around, busy with things. It's kind of funny to watch them run around like that. It's the perfect situation to use your special talent. It's super special and also a big secret because people yell at you when they find out, especially your mom. You are really small and sneaky, and you can steal almost anything if you really try. 


%%Your name is \cKid{}. You are seven years old. Your mom is \cScientist{}. She's a pretty great mom, even though she's always working and sometimes doesn't have enough time to spend with you when you want her to. 

%%You were raised by your mom and a nanny, and you never met your dad. You've grown up seeing other kids with their dads and seeing people playing with their dads on TV, and you've always wanted to have a dad too. So when your mom told you that she's going to take you to meet your dad, you got really excited! But when the two of you got to the hotel where she said your dad would be, it turns out that your dad is getting married to SOMEONE ELSE! This is horrible. This is not what you were thinking at all. You thought that meeting your dad meant that he'd get back together with your mom and be like a real dad to you, like the dads you've seen on TV. So you want to try to make that happen. 

%%Your mom has been worried about something lately, but you don't know what it is. She gets sad and cries at night. You wish she wouldn't because it's scary.

%%You do have one special talent, though. It's super special and also a big secret because people yell at you when they find out. You are really small and sneaky, and you can steal anything. 

\begin{itemz}[Goals]
  \item Keep your teddy bear safe.
  \item Play with Dad.
  \item Get Dad back together with Mom! If you steal the wedding ring away from your dad's new fiance, then he won't marry her and will get back with your mom instead, and you'll have a real dad.
  \item Figure out what is wrong with Mom.
  \item If you find out who \cRival{} is, go annoy him! He's mean to Mom!
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cScientist{}} Your mom. You love her so much!
  \contact{\cGroomA{\MYname}} Your dad. You've never met him but you love him too!
  \contact{\cRival{} Your mom doesn't like him! They're \emph{ENEMIES.}
\end{contacts}


\end{document}
