\documentclass[char]{elementals}
\begin{document}
\name{\cLeader{}}

You are President \cLeader{\intro}, the elected leader of the meta-government formed to replace the New United Nations when it was officially disbanded at the end of the 22nd century. You have your hordes of detractors and a steady base of supporters, although you have to keep reminding people who blame you for every ill they experience that seeing as you possess no veto or legislative powers, you have considerably less influence over matters than they think. Most of your day-to-day activities involve keeping faction A from engaging in physical altercations with faction B because they refuse to censure faction C who doesn't agree with their viewpoints on issue D. That said, you are still the elected representative of a good fraction of the human population, and when the need arose for a single individual to represent humans at the gathering today, you're it.

Your general approach to governance is mediation. When two forces oppose each other, you try your best to defuse the situation by whatever means possible. Although it's tricky, thus far you've managed to apply this philosophy even when the elementals are concerned. Whenever elementals wreak havoc -- and they do, all the time -- there is always a call for all out war with whatever faction of elementals caused the problem (or all elementals at once, because why not?). Your military advisors give you almost daily reminders that this would be a Very Bad Idea, and up until now you have done a good job of pacifying people. That said, you have also never really managed to extract any significant concessions or even apologies from the elementals involved: destruction of property or even murder seem like practically alien concepts to them. Still this has gotten quite a bit better over the past 50 years or so; improvements in agriculture, for example, have made modern farming quite a bit more resistant to a pack of fire elementals deciding that they want to bathe in the burning remains of a few thousand acres of farmland.

Years of political engagements have taught you the wisdom of doing your research \emph{before} you come to a meeting like this. There are seven other humans with you today, most of whom you already know. \cRomeo{\intro} is your bodyguard, an Azi soldier who you generally get along with. \cDema{\intro} is the only other member of your executive branch present. He is a talented speaker who is good at playing up the emotions on crowds; although your relationship is complicated, in general \cDema{\they} serves as a good foil to your more conciliatory negotiation style. Also accompanying you are \cAvatar{\intro}, the head diplomat in charge of negotiating a peace treaty with the elementals, and \cAvatar{\their} Azi assistant \cDiplomat{\intro}, also a talented negotiator.

There is also a sizable contingent of scientists attending. Officially all three report to you, although in practice you've found scientists tend to pay little attention to the chain of command. The most infamous of the scientists is \cGD{\intro}, the great granddaughter of Konrad Strauss, the scientist who got us into this mess 100 years ago. She's apparently made quite a name for herself in the scientific community, and specializes in researching the Conduit and the elemental plane. Also present is \cMS{\intro}, a more eccentric scientist whose focus is on the elemental's mental powers. Finally, there is \cScientist{\intro}, an Azi scientist who your report indicates is (as expected of an Azi) a stable and capable individual who studies the chemical processes that underlie the elementals. Your reports indicate that there are fairly tense social interactions between the three scientists, and that \cMS{} has been accused of safety procedure violations in the past by \cScientist{}. Still, all three are present because even after 100 years no one fully understands exactly what makes elementals tick, and these are the three people best situated to learn more. In particular, the opportunity to study one of the elemental leaders in close proximity has almost never presented itself before. You're just going to have to keep an eye on these three to make sure they don't get incinerated or cause an inter-species war. You also suspect the scientists have their own research agendas and you are going to have to find out what exactly they are.

%does leader have some ``resist enslavement'' tech from MS?

\begin{itemz}[Goals]
  \item Maintain peace between humans and the elementals at all costs.
  \item Keep all the humans attending the gathering alive.
  \item Work with \cAvatar{} and \cDiplomat{} to negotiate a peace treaty with one or more of the elemental factions.
  
\end{itemz}

\begin{contacts}
  \contact{\cLeader{}} The elected leader of the majority of humanity.
	\contact{\cDiplomat{}} An Azi diplomat and your friend and confidant.
	\contact{\cMS{}} A scientist who you have previously exposed for safety violations. Specializes in understanding the mechanisms by which elementals can exert mental control over both their own species and humans.
	\contact{\cGD{}} The great granddaughter of Konrad Strauss. A good collaborator, both friendly and capable. Specializes in the elemental plane and the Conduit itself.
  \contact{\cAvatar{}} \cDiplomat{}'s boss. A bit eccentric, and also known for talking to \cAvatar{\themself}.
\end{contacts}

\end{document}
