\documentclass[char]{elementals}
\begin{document}
\name{\cLoyal{}}

You are \cLoyal{\intro}, a high-ranking earth elemental standing in for your King, \cEarthKing{}.

You were one of the first earth elementals to separate from your King, and are immensely proud of this fact.  It gives you the right to command nearly all the earth elementals, and the important responsibility of providing counsel to the King and taking his orders directly.  Of course, \cEarthKing{\they} being much older and wiser than you, you generally defer to \cEarthKing{\their} judgment.  And on the rare occasions that you don't defer, \cEarthKing{\they} enslaves you and makes you obey.  Nonetheless, it's a great honor to be so close to the King.

Infuriatingly, you don't actually know your exact rank among the earth elementals.  You are within the second tier of power, and are certainly one of the oldest within that rank, but you've never managed to establish whether you outrank \cRogue{\intro} or whether \cRogue{\they} outranks you.  And due to \cRogue{}'s callous disdain for the hierarchy and the King's inexplicable soft spot for the clown, you haven't been able to get a straight answer as to which of you separated first.  You've tried fighting \cRogue{}, enslaving \cRogue{\them}, and giving \cRogue{\them} orders, and every time the outcome seems to be that you're stronger, but \cRogue{\they} always has this stupid grin afterwards that makes you wonder whether \cRogue{\they} isn't just messing with you.  You really do hate \cRogue{\them} for it, but somehow \cRogue{\they} has managed to stay in the good graces of the King, so you have to at least be polite.  Even if \cRogue{\they} does get away with the most ridiculous displays of disobedience without even a suggestion that the King might enslave \cRogue{\them} for it.

Since \cEarthKing{} is not attending and \cRogue{}, if \cRogue{\they} even outranks you, doesn't do these sorts of things, you are at this gathering to represent your faction and monitor what any others might be trying to do with the Conduit.  However, the other factions do not know that your King is ill.  While all the elementals have been weakening since their arrival in this plane, a fact which no doubt every faction has noticed by now, the King has been getting worse faster than anyone else.  At first, you thought it must be because \cEarthKing{} wasn't originally from this plane, but \cRogue{}, after disappearing for months without so much as asking for permission, reported that the other faction leaders were not worsening.  \cRogue{\They} insisted that this was all a plot by the air elementals, but you've sent out the junior elementals and confirmed that no air elementals have even come near the King's palace.  Besides, \cEarthKing{} has told you that \cEarthKing{\they}'s been weakened before, back on the elemental plane, and that \cEarthKing{\they} was cured by seeking out a ``quintessence elemental,'' one of the peacekeepers back on that plane which maintained the balance between the factions.  This elemental gave \cEarthKing{\them} a white healing substance.  

\cEarthKing{} sent you to the Conduit meeting with the secret purpose of obtaining this substance.  \cEarthKing{\They} suggests bringing a quintessence elemental through the Conduit.  This would also serve the purpose of restoring the balance of power between earth and air on this plane, though once \cEarthKing{} returns to full strength you hold out hope that, without quintessence elementals around, you might be able to overpower air someday.  After all, you've held them off during \cEarthKing{}'s illness.  And if it turns out that this mysterious substance can also reverse the weakening of the lesser elementals, it might be a distinct advantage for your faction.

You know that the human scientists have been studying both the Conduit and elemental biochemistry, and that some will be attending the gathering at the Conduit.  You hope to talk to them and determine whether they know anything about the healing substance or how to bring a specific type of elemental through the Conduit.  You tried once before, ten years ago, along with \cMinion{} and some other earth elementals, but your attempt failed and you destroyed most of the borrowed lab equipment in the  process.  You hope that by asking a human for help, you might be more successful this time.

\begin{itemz}[Goals]
	\item Obtain the healing substance produced by quintessence elementals. This will likely require summoning Quintessence elementals through either a \emph{momentary opening} or \emph{terminal opening} of the Conduit.
	\item Restore the power of the earth faction, and if possible weaken the air faction.
	\item Represent \cEarthKing{} well, and avoid letting the other factions find out that he is sick.
	\item Where you are able, enforce the hierarchy among elementals.  You believe in it strongly, and are deeply disturbed by elementals who don't respect it.  If possible, find out where you stand relative to \cRogue{} and make sure \cMinion{} stays in line.
\end{itemz}
 
\begin{contacts}
	\contact{\cRogue{}}  A second-tier elemental who has broken with the hierarchy.
	\contact{\cMinion{}}  A low-ranking earth elemental who was sent with you.
  \contact{\cAvatar{}}  A human diplomat who has visited \cEarthKing{}'s court.
\end{contacts} 

\end{document}
