\documentclass[char]{elementals}
\begin{document}
\name{\cMiniEarth{}}

You are \cMiniEarth{\intro}, a low-ranking earth elemental who was dragged along to this meeting just so that \cLoyal{\intro} could have another minion to lord over.

You're pretty much at the bottom of the heap, as far as earth elementals go.  Sure, there are other elementals that are around the same rank, \cMinion{\intro} included, but you pretty much just have to take orders from everyone without getting the opportunity to give any.  Sometimes you almost wish you were a different element -- they at least can move up through the hierarchy.  As an earth elemental, your rank is determined by the time of your creation, and with King \cEarthKing{}'s power weakening it's not likely that there will be any more junior earth elementals for you to boss around.  Earth is your home, though.  You have a deep connection with dirt, are fascinated by earthquakes, and generally feel at home among your fellow earth elementals.  You even respect that the older elementals are generally wiser, and entitled to their positions at the top.  You just feel it's about time you got your turn there.

While you respect your superiors in general, you have your doubts about \cLoyal{}.  For one thing, \cLoyal{\they} doesn't have to answer to anyone but \cEarthKing{}, and the King has been so weak recently that \cLoyal{} is practically in charge.  Also, even though you would honor the hierarchy and obey orders anyway, \cLoyal{\they} is just so obsessive about it, constantly reminding you that you're at the bottom and \cLoyal{\they}'s at the top.  It really grates on your nerves, but you know that even if you wanted to disobey you'd just get enslaved and end up following orders anyways, so you generally behave yourself.  \cLoyal{} can't stop you making faces behind \cLoyal{\their} back, though, and complaining to your fellow low-ranking earthlings.  \cMinion{} doesn't seem as bothered by \cLoyal{} as you are -- \cMinion{\they} just obeys orders and then goes back to playing in the dirt.  \cMinion{\They} listens politely when you complain, though, just like \cMinion{\they} listens politely to \cLoyal{}'s tirades about duty to your element and your superiors.

Much to your surprise, after \cLoyal{} ordered you and \cMinion{} to accompany him to the Elemental Council, \cRogue{\intro} joined your group.  You've seen \cRogue{\them} around a few times before, and know not only that \cRogue{\they}'s similar in power to \cLoyal{}, but also that \cLoyal{} despises \cRogue{\them}.  \cRogue{} seems to exist outside the hierarchy, as much as that's possible in the rigid social structure of Earth.  \cRogue{\They} clearly has \cEarthKing{}'s trust, but you've never seen \cRogue{\them} either enslave another elemental or be enslaved \cRogue{\themself}.  \cRogue{} rarely appears in the Earth court, and you're not entirely sure whether \cRogue{\they} leaves on missions for the King or just on \cRogue{\their} own whim.  \cEarthKing{} certainly didn't mention that \cRogue{} would be joining your delegation, and \cLoyal{} seemed as surprised as you were, so you suspect \cRogue{} isn't even here on official orders.  All of this makes \cRogue{} terribly intriguing to you, and it certainly helps that \cLoyal{} despises \cRogue{\them}.  You're curious about this non-hierarchical way of living, and eager to learn more about what exactly \cRogue{} does with \cRogue{\their} time.

\begin{itemz}[Goals]
	\item  Do what \cLoyal{} says when necessary, because \cLoyal{\they} is your superior and because in the end it's usually what's best for Earth as a whole.
	\item  At the same time, avoid doing what \cLoyal{} says whenever possible, because you want to and because you resent \cLoyal{\them}.
	\item  Learn more about \cRogue{} and what \cRogue{\they} is doing here.
  \item  Find a way to heal your King, both because he's your King and because you're sick of being at the bottom of the pecking order.
	\item  Make life difficult for the other elemental factions and especially for Air.  Sworn enemies, after all.
\end{itemz}

\begin{contacts}
  \contact{\cLoyal{\intro}} A high-ranking earth elemental, here to represent the Earth King.  \cLoyal{\They} ordered you to attend as well.
	\contact{\cMinion{\intro}} Another low-ranking earth elemental, also here to serve \cLoyal{}.  \cMinion{} is a friendly elemental who doesn't have \cLoyal{}'s obsession with hierarchy, but doesn't seem to mind subservience the way you do.
	\contact{\cRogue{\intro}} Another high-ranking earth elemental, who as far as you know was not sent to the meeting by the Earth King.
\end{contacts} 

\end{document}
