\documentclass[char]{guildcamp1}
\begin{document}
\name{\cProgrammer{}}

Humanity is a dying race. We prospered for a time, but it turned out that our sun and Earth could support us for less time than we had hoped. Unfortunately, interstellar distances are vast and despite combining humanity's best minds, no easy solution was found: it was not possible to store enough energy to support a ship of awakened colonists, and cryogenic freezing was too volatile and power-hungry to last through the vast amounts of time required to reach another planet.

The human race did not take this news well and was not willing to so gracefully exit the galactic stage. If our biological forms were not suited to handle the ravages of interstellar travel, we would replace them with something else that could. Although the technology existed to transfer a human consciousness into a robotic body, it was decided that too much of our heritage would be lost if we existed only as robots on a barren spaceship. Instead, the decision was made to preserve humanity in a virtual environment. This is where you come in.

Your name is \cProgrammer{\intro} and you were born in Pasadena, 12596 CE. You were widely hailed as one of the greatest minds of the century. When the decision was made that humanity would be preserved in virtual form, humanity turned to you. Programming and the mind-machine transfer are your specialties, and over the course of several decades you and a team of thousands of others built the most comprehensive computer system ever constructed. It was eventually installed on the ship \emph{New Eden}, itself the pinnacle of human engineering. Ultimately, the majority of humanity had their consciousness imprinted onto the system, and as the great simulation began, its host ship was launched to drift amongst the stars. You watched the great ship take off from the dying Earth. Shortly after not even the longest-range sensors on Earth could pick up the ship's signal, you happily passed away at an old age, your life's work completed.

Philosophers, politicians, and scientists debated for quite some time what nature the virtual world should take. Should it be a true post-scarcity utopia, free from trouble and death, with infinite resources for all? Should the new humanity start at 126th-century technology or something primitive like the Dark Ages of the 30th century? Ultimately,  it was decided that something critical to our existence would be lost if the world was free from adversity, and the world was constructed to be as close to ours as possible; no ``free and unlimited energy'' would be available, and the new humanity would start at the beginning of something approximating the Roman Empire. Importantly, a conscious decision was made to avoid passing down the knowledge of humanity's origin so that future generations would not feel their existence was in any way fake or a cheap imitation of the real thing. You were a great opponent of the Utopians (those who pushed for an adversity-free world) and one of the founders of the New Beginning movement, which wanted to keep the fact that the world was a simulation from those inhabiting it. You are certain that although a perfect utopia sounds nice in theory, it would ultimately be unsustainable and inevitably result in the destruction of the simulation.

A myriad of blinking lights flash on a 2D heads-up display superimposed across your vision. You take a moment to get your bearings, and find yourself in what you believe to be something approximating a hotel room from between 20th to 22nd century humanity. You then take a moment to reflect on the fact that you are thinking at all. The last thing you remember is doing a backup upload of your consciousness...which would mean you are mostly likely inside your own simulation, and something catastrophic has happened, initiating one of the many fail-safes. That would mean those blinking lights are the debug console. You decide to pay a bit more attention to them.

There are two big warning lights blinking. The most serious is that the simulation is running on the emergency battery. It has only \emph{four hours} of energy left, and that's only with running a very, very small subset of the simulation space. The vast majority of the simulation is currently inactive. You're not really sure what caused the low battery, but you think it would have to be someone outside the simulation messing with it. New Eden has three robot bodies that are designed to fit human minds, but no one from the simulation should have any idea how to escape the simulation and upload their consciousness into them, and the debug lights show you that all three robot bodies are currently inactive.

The second warning light shows you that there are two other entities currently connected to the simulation. Based on the light color and blinking frequency, they do not appear to be human minds. This is most likely what caused you to awaken --- the simulation's monitoring system woke you up so you could decide on the appropriate response to the newly connected entities. The ship is also indicating a proximity alert, which could indicate another nearby ship, planet, or asteroid. Unfortunately, because battery power is so low, only the most basic level diagnostic analysis is running. You cannot access your full debug suite, which prevents you from modifying the simulation directly, accessing the ship's sensor logs, or even exiting the simulation to investigate using the robotic bodies.

You return to taking in your surroundings. Upon inspecting a mirror you find you look exactly like you remember yourself, but when you try to reach out to touch the mirror your hand passes straight through it. This appears to be a persistent problem --- \emph{you are ethereal and cannot physically interact with any objects or people in the simulation unless told otherwise.} This doesn't shock you too much; it's standard protocol for debug-mode. Makes it a lot easier to navigate around, although you're again frustrated by the low-power situation as the nice ``teleport to destination'' function is currently inaccessible.

You don't know what your surroundings are like, but you have a reasonable idea about what to expect. The monitoring system for the simulation will have incarnated you and chosen this specific subsection of reality for a reason. That likely means that it thinks there is some way out of the simulation nearby. The most likely way you can think of is throwing a recursive exception: when the host computer detects a simulation-within-a-simulation of a certain immersive complexity, under some circumstances the mind is instead ejected to one of the New Eden robots to avoid an unsustainable recursion.

There will likely be some corruption of the local environment. This is not too unexpected given the sudden low-power situation, but you imagine the local inhabitants will find it terrifying. These anomalies are very dangerous and the mind-states of people who interact with them will start to lose cohesion --- if their mind-states deteriorate too much, they will be excised from the simulation entirely and will cease to exist. One of the reasons you have been awakened is to prevent this from happening.

Most importantly, the simulation periodically creates a fail-safe to preserve the current world state so that, should something catastrophic happen, the world can be restored from the backup copy. This ``save state'' is likely embodied somewhere in the world. You won't be able to immediately recognize it, but you know it should be able to resist any environmental corruption or anomalies that may appear. You can use your debug console to determine the current mental state of anyone you interact with, and you suspect that someone with very little corruption is likely in possession of the save-state.

Should you manage to find a way outside the system, the save-state should be able to transfer outside the system as well. You can then use it to restore the rest of the simulation. As far as you know, those currently within the reduced part of the simulation will be preserved. Unfortunately, because you don't have a solid body at present, you won't be able to directly interact with the save-state: someone else will have to carry it outside the simulation for you.

You were not the only programmer of the simulation, and this copy of your persona is from a few months before New Eden launched. There may or may not be other fail-safes in place to restore the simulation that you are not aware of.

Things aren't looking too great, but you were one of the greatest minds of your generation. You can get this situation under control if you put your mind to it. If you play your cards just right, you might even be able to fix things without revealing the nature of reality to most of the local inhabitants.

This is a summary of the mechanical consequences of being ethereal:
\begin{enumerate}
\item Your body passes through everything you touch or interact with unless explicitly told otherwise.
\item You can search through rooms or other areas to scout or help other players, but you cannot actually pick up the items you find.
\item You can freely move through solid obstacles such as locked doors, unless told otherwise. \(However, you cannot pass through the walls of game space\)
\end{enumerate}

\begin{itemz}[Goals]
  \item Preserve the simulation at all costs. If anyone tries to alter the simulation from its original trajectory, stop them.
  \item Find the save-state, find a way outside the simulation back into New Eden, and reset the simulation using the save-state.
  \item Prevent any humans from dying due to corruption from any anomalies.
  \item Find out who the mysterious minds are that are connected to the simulation. If they are benevolent, you would love to learn more about them outside the simulation, but entreat them to leave the simulation in peace. If they threaten the simulation or humanity, stop them. You do not know what form they might take within the simulation.
  \item The New Beginning movement is very important to you. Prevent as many people as possible from learning about the true nature of the simulation. One or two people may be dismissed as insane, but if too many learn of it, once the simulation is restored the truth might become widespread and your life's work might degenerate into anarchy or self-destruction.
\end{itemz}

\starttag{mems}

  \memfold{if you see an item whose number starts with ``77''}{These people seem to have made quite respectable progress on the mind-machine interface front. With a little help, their work could be just what you need to get out of the simulation. With a \bf{completed head-mounted display} and a \bf{completed mental amplifier}, you might be able to jury-rig up something to get your consciousness uploaded into one of the \emph{New Eden} robots. One problem is that you will need a lensing device of some kind: specifically, a ruby or sapphire gemstone. Open your $\Delta$ packet now.}

  \memfold{If you see item \#148 and stand near it for one minute}{This is not good. It appears to be a save-state created by one of those damnable Utopians. You would guess that they hid it in one of the subsystems, just waiting for such a low-power emergency. You wouldn't be surprised if they engineered this whole disaster in the first place. They probably have tried to find allies in the simulation, so you will have to be on your guard. If you can get this Utopian save-state back to the ship, you are fairly confident you can destroy it.}

\endtag

%mem-packet idea: If you hear bade #pastor/groom mention the spaceship open this packet. ``You are going to kill Alexandra for implementing the ``awaken humans on proximitiy detection'' protocol. That's the only way simulation humans could be drawn outside the simulation. You told her that it was a terrible idea precisely because of a situation exactly like this one. If you survive this, you are seriously contemptating resurrecting her consciousness for a bit just so you can tell her 'I told you so'.''

%he is effectively the founder of Virtuism. Perhaps religious people recognize him. There might be pictures of him in his starting hotel room that look just like him (think portraits of Jesus), and the very religious might almost worship him.

%the Utopian could be a powerful movement that had a planted personality that activates within the Scientist.

\end{document}


%%Ethereal ability psychlim
