\documentclass[char]{elementals}
\begin{document}
\name{\cPyro{}}

You are \cPyro{\intro}.  You are a powerful member of a powerful race of Fire Elementals.  You are one of the strongest 2nd-tier elementals on this plane, and defer to your Queen, \cQueen{\intro}.  You used to have \cQueen{\their} ear when it came to important state decisions, but \cQueen{\they} is generally less inclined to exercise Fire's full potential than you are, and sometimes loses patience with your quick temper.  \cQueen{\they} must keep up appearances and show diplomacy when working with other elementals or humans, while you have no such reservations.  During your youth, this allowed you to rise through the ranks of 2nd-tier Fire Elementals, but you still must work for \cQueen{}'s respect.  About three decades ago, you got into a nasty scuffle with a particularly rude 3rd-tier Water Elemental.  You were easily victorious, as well you should have been, but other Water Elementals attempted to avenge him by flooding one of \cQueen{}'s volcano palaces.  You have been trying to earn back \cQueen{\their} favor ever since.  This is made more difficult by the fact that the two of you don't see eye-to-eye on the necessity of courteous diplomacy.  While other elementals, particularly those that rank highly, can be formidable foes, you can hardly understand why \cQueen{} bothers with the weakling species that occupy this plane.

While you have heard a great deal about the elemental plane, you have never been there yourself.  You came into being after the incident that somehow brought a number of powerful elementals, including \cQueen{} into the human world.  While you sometimes wish you could see the plane on which you were meant to exist, you have no real desire to leave the delightfully flammable human world.  Here, you can release your power fully, and spread fire in a way that would likely be repressed by stronger members of other elements were you on the elemental plane.  Here, you can be one of the strongest Fire Elementals.  Here, you can prove that Fire is the strongest.  And here, you can be sure of your ability to protect your little sister, \cJuliet{\intro}.

Although it is a quaint moniker, and human familial relationships make little sense to you, you do believe the term ``sister'' does seem to best describe how you feel about \cJuliet{}.  \cJuliet{\They} was spawned on the human plane just after you were, and you spent your first day of existence burning down a forest to provide enough fire to protect \cJuliet{\them} from a sudden rainstorm, which you secretly suspect was an attempt by Water Elementals to neutralize you and your newly-spawned siblings.  You and \cJuliet{} were separated from the others by the downpour, and you believe you were the only ones to have survived. \cJuliet{\they} is not as strong or as high-ranking as you, and you fear if Water, or even Earth or Air, tries to gain more control over the human plane, \cJuliet{\they} would be one of the first Fire Elementals to fall. For this reason, when you found out \cQueen{} was looking for someone to infiltrate the human ranks and spy on them, you were quick to recommend \cJuliet{}.  You knew that securing \cJuliet{\them} in the Queen's favor would give her more protection, and even provisionally increase \cJuliet{\their} power, as well as improve your own standing with \cQueen{}.  However, you now worry that perhaps you were too hasty.  \cJuliet{} began as the intermediary between \cQueen{} and the Air King, and now all the Air Elementals are blaming \cJuliet{\them} for a disaster you are almost certain was caused by an Air Elemental.  While you thrive on destruction and don't really understand why causing some human vehicles to crash is such a big deal (hey, accidents happen!), you think that \cJuliet{} taking the blame will undo all of the work with humans \cJuliet{\they} was able to do, and would likely lower both of you in \cQueen{}'s court.

While many humans are little more than easily flammable playthings, or perhaps potential slaves, there are a select few who are much more useful.  In particular, \cMS{\intro} has made a discovery that you think could be quite useful.  Elementals are capable of enslaving humans, of course, but when \cMS{} suggested \cMS{they} might be able to enslave Elementals, you were intrigued.  If you could gain the power to control Earth, Air, and Water Elementals as easily as their own kings or queens, you would be able to take over this entire puny realm for your own fiery glory.  From what \cMS{} has told you, \cMS{\they} was able to capture a low-ranking earth elemental, and used some sort of ``tape,'' you think \cMS{they} called it, to cause another human to enslave the earth elemental.  What you wouldn't give to be able to use this ``tape'' and gain the ability to enslave other elementals yourself!  If you shared this technology with \cQueen{} as well, you would doubtless earn her respect, and \cQueen{they} would be able to control even more other Elementals!  On the other hand, you are suitably wary of this technology.  The last thing you need is the embarrassment of being enslaved yourself, and by a human, no less!  So you while you continue to work with \cMS{}, you remain cautious of \cMS{\their} motives.

And that is what brought you here, to this meeting of humans and Elementals.  While most are here to talk of peace, you know that many will also attempt to gain power for their own faction, as is the usual fare at Elemental Councils.  You are here to support your Queen, but more importantly, you are here to maintain Fire's authority on this plane.  \cMS{} is here, and you hope to be able to gain some of \cMS{their} enslaving technology, and use it on some of the Earth or Air Elementals who are also present.  In addition, you know that this old building contains a conduit, through which the first Elementals came to the human world 100 years ago.  You know little more about the conduit itself, but you do know if the gateway to the elemental plane were opened again, either you and those Elementals that were here could return to the Elemental plane, or more Elementals could  come through to this side, many of which would be much more powerful than you or even \cQueen{}.  While you could not bear the thought of having to submit to some high-ranked Water, Air, or Earth spirit, you think you should be a way to only bring through more Fire Elementals.  You would be lower in the hierarchy, yes, but more powerful Fire Elementals would also dominate over those of other factions.  

\begin{itemz}[Goals]
  \item Acquire the enslavement technology from \cMS{} and use it to control Earth, Air, and Water elementals, and share it with \cQueen{}
  \item Learn more about the conduit and find a way to allow more Fire Elementals into the human world.
  \item Stay on \cQueen{}'s good side
  \item Prove that \cJuliet{} was not responsible for the airplane incident 
  \item Keep \cJuliet{} safe from harm.
\end{itemz}

\begin{contacts}
  \contact{\cQueen{}}- The most powerful Fire Elemental on this plane, and your superior.
  \contact{\cJuliet{}}- A low=ranking Fire Elemental who you are very protective of.
  \contact{\cMS{}}- A human scientist who may know how to enslave elementals.
\end{contacts}

\end{document}
