\documentclass[char]{guildcamp1}
\begin{document}
\name{\cRival{}}


Success is sweet.  You are one of the world's leading expert in brain computer interaction.  You made millions of dollars founding your own company.  

Your professional career took off in graduate school when you discovered a way of measuring the activity of individual neurons in a human brain.  A few years earlier, physicists had developed superconducting magnets that were only one centimeter in diameter, and you realized that by creating a cylindrical array of these magnets you could focus them on individual neurons.  After a few years of work you created a device that could detect a person's surface thoughts. With this person could think ``I want to send an email to Bob that says the following: . . .,'' and would it detect this and take the required action automatically.  After graduate school, you founded a start-up called {\em ``Vision''} with this technology and earned hundreds of  millions dollars.  You love the power this money gives you.  You often carry a million dollars of stocks around with you, just to remind yourself of your wealth, and to trade if you find someone who has something you really want.

In your spare time, you have become involved in politics.  The current state of affairs pains you greatly.  You are deeply involved in the sciences and see the great potential they have to improve lives. You have frequented a few of the more radical political blogs, and post in a couple of forums run by utopian activists. You, and they, believe that technology can effectively change the limited nature of resources, destroying all need for war and strife and opening the human mind to an earthly paradise you call 'Utopia.' You're not sure how to get there, but it's been your goal for years.

As part of this goal, you've done some research into psychoactive substances, trying to create the perfect pleasure chemical, something harmless and nonaddictive, yet euphoric. Your research has been unsuccessful so far, but you think that this new strain of Anaphmonine, which goes by the street name 'Bite,' might get close. You are a bit paranoid that your dabbling into illegal substances will get you in trouble, so usually keep your samples on you. You don't actually take Bite, but you know that it has less potent effects if injected rather than ingested. (Bite will cause hallucinations for 5 minutes if eaten, but only 2 minutes if injected with a syringe and water).

You have continued working on your brain-computer interface in a huge lab at your company, and you have reached a new milestone.  You can now build a device that can scan all the neurons and all the connections between them in a living human brain.  You have brought the parts to build this machine for a conference tomorrow, and you're sure your work deserves the International Medal of Science, the highest honor a scientist in any field can receive.  This is it, a chance to prove to everyone just how intelligent and trustworthy you are.

The only obstacle between you and the award is your longtime rival, Dr.~\cScientist{\intro}.  Your rivalry with \cScientist{} began in high school at the International Science Fair.  %Note: this is intentionally different from scientist's account.  They both remember the other doing the first bad thing.

You needed to win. That was the important thing. You needed the boost to start your career. Your ideas, your goals, and your plans for Utopia were too valuable to the world to leave to chance. So you hacked into the system and tried to fail your biggest competitor. \cScientist{} caught you, and expelled you. \emph{Damn!} You tried to explain that you were doing it for a good cause, but your pleas fell on deaf ears.

In the future, you were more careful, and quickly rose to the top of your class. You were a rising star. So what if you did it by copying the unfinished research of senior scientists from big corporations? Those pigs were just stomping on the poor anyway. There was only one other 'mission' that someone managed to collect evidence of.  Your old friend \cBride{} spied on you and caught you altering paper acceptances in a prominent journal, but luckily she wouldn't betray you.  You would hate for any of your illegal activities to get out and damage your reputation.

In terms of research quality, you and \cScientist{} are about evenly matched, but you know that to have a platform for your politics, you need to be the \emph{best} and the most acclaimed. And if you can't pull ahead, then \cScientist{} needs to drop behind. Your latest achievement on this front was personal in nature. A few months back you were looking for dirt on \cScientist{} and hacked into \cScientist{\Their} doctor's computer. You discovered that \cScientist{\They{}} have a terminal disease. You forwarded the news to several prominent bloggers, hoping that \cScientist{}'s co-publishers would abandon working with her if they found out.

Today your plan to knock \cScientist{} out of the running for the International Medal is simple.  With some simple hacking you managed to obtain a copy of the paper \cScientist{\they} is submitting tomorrow.  You have created a copy of this paper which looks similar but commits clear plagiarism of another scientist's work.  You'll get hold of \cScientist{\their} folder which contains \cScientist{\their} paper and swap the real and faked paper.  You can't wait to see the press when they find out tomorrow.

You have thought about what to do next with your brain-computer interface technology, and realize it would be very powerful if combined with an advanced artificial intelligence.  Perhaps you could scan a human brain and then run a simulation of it inside a computer.  This would require a very advanced artificial intelligence, but your rival \cScientist{} has been working on just such a technology.  Of course \cScientist{\they} would never give it to you if you asked, and \cScientist{\their} security is too good for you to steal it directly.  

Ah well. In the mean time, you've heard whispers that there is some major millitary technology being stored at the hotel. The security is laughable, and it is a golden opportunity to learn what the millitary is up to. You are no pacifist, but knowledge is power. There is what is supposed to be a high security door at this hotel, and you plan to find a way inside it and take the blueprints or whatever is behind that door.


\begin{itemz}[Goals]
\item Complete production on your Head Mounted Display for the International Medal of Science Award Ceremony tomorrow.
\item Steal the blueprint from behind the high security door.
\item Hang onto your stocks or trade them for something sufficiently valuable. You need the money for when you create Utopia.
\item Frame \cScientist{} for plagiarism.
\end{itemz}

%TODO make sure relevant items and mechanic exist for plagiarism plot.  Should the foler/paper be physrepd?
% TODO Rival has an item of stocks
% TODO make sure Rival has drugs/meth
% TODO: get widget or give widget to Scientist
% TODO: make science more sketchy


%Your pronoun is \cRival{\they}.

%%%%%
%% List contacts, using \contact{<char macro>}
%\begin{contacts}
%  \contact{} 
%\end{contacts}
\begin{contacts}
  \contact{\cScientist{}} A renowned Senior Scientist in your field. She uses her intelligence to maintain the status quo and sell out to the Man. She's also on your case. Her career needs destroying, and you're the one to do it.
  \contac{\cBride{}}} Your old friend from college. How convenient that her wedding is happening at the some hotel as your conference.
\end{contacts}

\end{document}
