\documentclass[char]{elementals}
\begin{document}
\name{\cRomeo{}}

You are \cRomeo{\intro}, bodyguard to \cLeader{\intro}, the President of the humans.

You are an Alpha Azi, you are among the elite, genetically modified to have genius-level intelligence, psychologically designed to be self-directed and capable of independent thought within the constraints of your programming.  That is to say, \cLeader{} can give you a broad directive, and you can interpret and enact it without getting step-by-step instructions.  In your childhood, you received training in the Barracks with the other Azi selected to be soldiers or security guards: the Alphas, who are generally partnered with a Cit of equal intelligence to serve as personal bodyguards; the Betas, who are methodical and diligent and do well heading security forces, as long as they report to a Cit or an Alpha Azi; the Gammas, who have less initiative and require detailed instructions; and so on.

After you completed all your training, you were assigned to \cLeader{}, the scion of a family that has been prominent in human society since the first Opening that brought elementals to earth a hundred years ago.  \cLeader{\Their} forebears played an important role in rallying humans during those dark times, when the elementals ravaged the cities and wantonly incinerated, smothered, or drowned any living creature in their path.  Over the years, as humans adapted to coexistence with the elementals, \cLeader{}'s family was instrumental in initiating diplomatic relations with them.  As a result, when Cits re-established the birth labs and began producing Azi again, the son of the \cLeader{\formal} family was among the first to receive an Alpha Azi companion, namely you.

As soon as you finished your Barracks training, you were called to your training supervisor's office to receive your formal Contract binding you to \cLeader{}.  \cLeader{\They} is your Supervisor, the one in whom you have complete trust, to whom you turn when you experience any psychological conflict.  Azi are very logical, while Cits are bafflingly emotional - dealing with them can be very confusing, and yet, it is unavoidable in your role as bodyguard.  \cLeader{} is the one who resolves all difficulties.  This is in your Contract.  The two of you have been together since you were both youths, before \cLeader{\they} began his ascent to power, and you are like family.  You are absolutely loyal to \cLeader{\them}.

As \cLeader{}'s bodyguard, your primary responsibility is to protect \cLeader{\them}.  This task involves forestalling assassination attempts from both humans and elementals who disagree with \cLeader{\their} political views, meaning you investigate everyone with whom \cLeader{\they} comes into contact, including \cLeader{\their} second-in-command, the smooth-tongued Secretary of State \cDema{\intro}.  More broadly, you interpret this ``protection'' directive to encompass \cLeader{}'s emotional state.  To this end, you support \cLeader{\them} in his goals.  Currently the human-elemental peace treaty is very important to \cLeader{\them}, so you do your best to collect information about key players that might be helpful.

One elemental you meet regularly is King \cKing{\intro} of the Air faction, who has expressed interest in an alliance with humans.  The Air elementals are the most friendly of the four factions, but you remain wary of them on principle.  Another elemental you see often is \cJuliet{\intro}, a Fire elemental who acts as an intermediary between the Fire Queen, \cQueen{\intro}, and King \cKing{}.  Even though Fire elementals in general aren't particularly friendly towards humans and all too frequently incinerate humans by accident or through neglect, \cJuliet{} seems different.  The more you interacted with \cJuliet{\them}, the more you grew to appreciate \cJuliet{\their} company.  \cJuliet{\They} is intelligent and trustworthy (or so you thought), and at some point you examined your feelings and concluded that you love \cJuliet{\them}.  Luckily \cLeader{} has been supportive of your relationship, mostly because \cLeader{\they} cares about you and wants you to be happy.  You've also received encouragement from one of the diplomats, an Azi named \cDiplomat{\intro}, which you appreciate, but you remain suspicious of anyone who is not your Supervisor.  Besides, unlike \cLeader{}, \cDiplomat{\they} has an ulterior motive for being helpful: \cDiplomat{}'s goal is to achieve a human-elemental treaty.

Even with \cLeader{} and \cDiplomat{}'s help, though, finding opportunities to meet \cJuliet{} in private has been challenging.  Negotiating all the cultural and \emph{species} differences has also been tricky.   But you've been making things work...up until recently, when two airplanes were knocked out of the sky by an elemental, killing hundreds of humans.  King \cKing{} has told \cLeader{} that \cJuliet{} did it.  \cJuliet{\They} denies it, but not strenuously enough, in your opinion.  You are determined to find out the truth.  You love \cJuliet{\them}, but murder is unacceptable.  You cannot tolerate any more human deaths at the hands of elementals.  If \cJuliet{\they} is guilty, you will have no choice but to break up with her and report her crime to your Supervisor.  You hate the thought of doing so (it feels like betrayal, somehow), but it is the only action that is consistent with logic and with your programming.

But if \cJuliet{} is innocent, you hope to find a way to stay with \cJuliet{\them} forever.  You know that \cJuliet{\they} will be at this meeting, and you are determined to have a private conversation with her to find out the truth.  Unfortunately, that means leaving \cLeader{}'s side, which you are hesitant to do unless you can ensure \cLeader{\their} safety.  Luckily for you, though, the scientist Galina Schwartz, whose Azi assistant \cScientist{\intro} is also attending the meeting, has sent you an experimental belt that may offer some protection against elemental attacks.  It is not fully functional yet, but perhaps you can get it to work.  That would be one way to ensure \cLeader{}'s safety while you seek out \cJuliet{}.  One way or another, the future of your relationship will be decided at this meeting!




\begin{itemz}[Goals]
  \item Protect \cLeader{\full}!  \cLeader{\They} has many enemies, both elemental and human, and it is your duty to keep \cLeader{\them} safe.
  \item Look after \cScientist{\full}.  It's the least you can do for Galina Schwartz, who has done you a favor by sending you the experimental belt.
  \item Help \cLeader{} get the human-elemental peace treaty signed by finding out information about key players.
  \item Keep any elementals from finding out about your relationship with \cJuliet{}.
  \item Find a way to stay with \cJuliet{} forever without leaving President \cLeader{} unprotected.
  \item Find out what \cJuliet{} had to do with that airplane, if anything.
  \item Keep an eye on Secretary of State \cDema{\full}.  \cDema{\Their} family was prominent in the Extinguishers group, \cDema{\their} parents were executed for their crimes, and 
  \cDema{\they} \cDema{\themself} was once a member.
\end{itemz}

\begin{contacts}
  \contact{\cLeader{}} President of the humans and your Supervisor.  You are absolutely loyal to \cLeader{\them}.
  \contact{\cAvatar{}} Head diplomat, whose life goal is to negotiate a human-elemental peace treaty.
  \contact{\cDiplomat{}} An Azi diplomat who encourages your relationship with \cJuliet{} for political reasons.
  \contact{\cScientist{}} An Azi scientist, whom you've promised to look after at the meeting.
  \contact{\cDema{}} Secretary of state of the humans.  You're keeping an eye on \cDema{\them}, just in case \cDema{\they} gets over-ambitious.
  \contact{\cJuliet{}} A Fire elemental who acts as an intermediary between the Fire Queen and Air King.  Also the love of your life.
  \contact{\cKing{}} King of the Air elementals who may sign a peace treaty with humans.
\end{contacts}






\end{document}
