%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[notebook]{guildcamp1}
\begin{document}

%\item 
%\item 

\startnotebook{\nAlienAgression{}}

\begin{page}{pre}
This notebook is not transferable. You may open it to the first page at the start of the game.
\end{page}

\begin{page}{first}

You are both frustrated and fascinated with the apparent limitations of these human bodies.  Test how much one body varies from the next by having a jumping contest with someone. See who can jump higher. When you complete this step, you may turn to \nbref{second}.

\end{page}

\begin{page}{second}

Well that was enlightening. Raise your $\Omega$ score by 1.  The humans around you appear to be engaged in a religious ritual of some sort. Does it have anything to do with exerting rights over property or territory? Inverview two people for five minutes each on how humans stake their claim on a place or object. When you are done, you may turn to \nbref{third}.

\end{page}

\begin{page}{third}

How strange. So this religion doesn't seem to have much to do with territory. It seems like humans aren't naturally very aggressive. It's time to provoke one. Insult a human verbally - try to initiate what is called an `argument' and observe the response. When you are done, you may turn to \nbref{fourth}.

\end{page}

\begin{page}{fourth}

Perhaps there is hope for the human race.  Raise your $\Omega$ score by 1. It appears they can be persuaded to become agressive with the proper stimulus. But a verbal attack won't help you in your war. It is time to determine a human's effectiveness in combat.  Initiate combat with a  human and sucessfully knock them out. Observe their response, and that of any witnesses or someone who finds the unconscious human. When you have learned how humans respond to physical aggression, turn to \nbref{fifth}.

\end{page}

\begin{page}{fifth}

Humanity certainly has the potential to be an valuable ally, once you teach them the basics of making interstellar engines.
Gain 5 $\Omega$, but not past your maximum value. This knowledge quest, besides being very enlightening, seems to have duplicated some of the much-needed maintenance on your physical body. Tear up your ``Mental degradation'' ability.

\end{page}

\endnotebook

\end{document}
