%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[notebook]{elementals}
\begin{document}

%\item 
%\item 

\startnotebook{\nEnslavementResearch{}}

\begin{page}{first}

You have plenty of psionic data feeds from observing the elemental enslavement process first-hand, but for some reason the elemental biochemistry seems to have shifted now that they are so close to the Conduit. You will need to gather some more up-to-date experimental data. Find your trusty \emph{tricorder}, a \emph{photodiode}, and a \emph{coffee mug}. With these in your hands (remember two of these items are 1-hand bulky), you need to watch two different factions of elementals attempt to enslave a human. In each case, the victim must be successfully enslaved, and cannot be yourself.

Once you have data on two humans being enslaved by elementals from different factions, turn to \nbref{second}.

\end{page}

\begin{page}{second}

Your blasted rod is having thermal problems again; you should never have tested it on a fire elemental, it melts the circuitry. Find a large body of water and dunk the rod in it for two minutes.

When you complete this step, you may turn to \nbref{third}.

\end{page}

\begin{page}{third}

Finally...now the rod is ready for another test. Unfortunately, the rod is very weak -- even if you can find a willing participant, it will have no effect on them unless their psionic capabilities are below the rod's capabilities. Use your tricorder to examine the TODO-ELEMENTAL-POWER-STAT stat for elementals; the rod can only work on elementals with a TODO-ELEMENTAL-POWER-STAT value less than or equal to 3.

Once you find an appropriate victim (willing or not) have them strapped into one of the chairs in your laboratory and activate the rod as an Enslave B ability TODO-ENSLAVE-MECHANIC.

When you complete this step, you may turn to \nbref{fourth}.

\end{page}

\begin{page}{fourth}

\emph{You may now use the rod to enslave elementals with Enslave B, but the rod takes a while to recharge and may only be activated every 20 minutes}

The rod is working well, but despite your best efforts it has never been able to work beyond the weakest elementals. Fortunately you have the special tape you designed to train Azi, although you will need to update it in light of the elemental's mutating biology in the presence of the Conduit. Towards this end, use your tricorder while you observe two different elementals attempt to enslave an Azi.

When you complete this step, you may turn to \nbref{five}.

\end{page}

\begin{page}{five}

The data is disappointing at best. Based on these observations, making the tape work on more powerful elementals is not going to be easy. First, you will need \emph{elemental essence}, a core component of

When you complete this step, you may turn to \nbref{six}.

\end{page}

\begin{page}{six}

Spend five minutes in your lab to complete your \emph{Azi education tape}. Now it is again ready to re-train Azi to enslave elementals.

Once you have working tape, you need to actually find Azi to retape. They must sit in one of the chairs in your lab, and do not have to be willing, as long as they are restrained. Ideally, you would like to convince the political leadership (probably with the help of \cDema{}) to gain control.

When you complete this step, you may turn to \nbref{six}.

\end{page}

\endnotebook

\end{document}
