\documentclass[notebook]{elementals} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nLearnAboutHumans{}}

\begin{page}{first}
You have observed humans for a long time, but have only recently begun talking to a few of the scientists and politicians.  You think it would be useful to use this meeting as an opportunity to learn more about humans.  At game start, you may  turn to \nbref{second}.
\end{page}

\begin{page}{second}
You know that \cJuliet{} also frequently interacts with humans.  You wonder if she has discovered anything about them you haven't.  Spend five minutes talking to \cJuliet{\them} about what she has observed about human behaviour and society.  When you have done this, turn to \nbref{third}.
\end {page}

\begin{page}{third}
 That is interesting.  You have heard \cDiplomat{} mention the terms "Azi" and "Cit" before, but you are not entirely sure what they mean- you think there might be different kinds of humans?  Spend at least five minutes talking to \cDiplomat{} about this distinction, and have \cDiplomat{\them} help you create a list of all humans present and whether they are Azis or Cits.  After you have done this, turn to \nbref{fourth}.
\end{page}

\begin{page}{fourth}
That was enlightening, but as \cDiplomat{} is an Azi, you suspect asking a Cit about the two types of humans might reveal a very different attitude.  Hmm... according to your list, \cGD{\intro} is a Cit, and \cScientist{\intro} is an Azi.  This might be a good opportunity to introduce yourself and your research.  Spend two minutes talking to each of three more humans, one Azi and two Cit, about human society.  When you have finished these conversations, turn to \nbref{fifth}
\end{page}

\begin{page}{fifth}
 That certainly did give you some interesting insights into human society and behaviors, but you still wonder about their physiology.  Elementals are about to sustain their power and energy for very long periods of time, but humans seem to need to ingest items in order to renew their energy.  You aren't entirely sure what humans eat, though.  You know they power their science equipment with various items found in the lab.  Go to one of the laboratories and select two items at random, and offer each item to a different human and see if they will eat it.
 turn to \nbref{sixth}.
\end{page}


\begin{page}{sixth}
 Well, that didn't work.  It seems that there are only certain kinds of items that humans can ingest as food.  Perhaps you can find some food items in the kitchen?  Locate the kitchen and find three food items, and convince three different humans to eat them.  Ask the humans if eating the food has helped them gain energy.  Once you have sucessfully energized three humans, turn to \nbref {seventh}.
\end{page}

\begin{page}{seventh}
You would like to be able to further study human physiology in the future.  Obtain a syringe and a vial, and draw a blood sample from one willing human.  Ask \cGD{} if you can use the mass spectrometer in \cGD{\their} lab to analyze it.  Once you have used the mass spectrometer, turn to \nbref {final} to see what you learned from the machine.
\end{page}

\begin{page}{final}
Human blood seems to serve a similar purpose as your own elemental essence.  This is useful, although a little strange. Why do elementals have blood and essence? Oh well, You have learned lots of amazing things about humans today, and even helped them get energized. Open your K packet now.
\end{page}

\endnotebook

\end{document}