\documentclass[blue]{elementals}
\begin{document}
\name{\bKnowQ{}}

You are one of the few elementals on this planet who once lived on the elemental planes. You do not know the cosmology that relates your home plane to this hot piece of rock, water, and air, but while things on this alien planet are very different than your birthplace, after 100 years life you have finally started to adapt.

Just like on the elemental plane, the four elements have been in a state of near-constant warfare since arriving. You have astutely realized that these battles are in some ways different here. Oddly, you have noticed that they are substantially more destructive. Low and even mid-ranking elementals often sustain serious injury that take months to heal. In rare occasions, elementals have actually died. These deaths rock the entire hierarchy. The amount of fighting has consequently declined substantially as the factions try to work out why the consequences of fighting for dominance on this plane are so extreme.

The only thing that is missing from this plane, that exists on the elemental plane, is the Quintessence. The Quintessence is best described as a fifth element. Rather than wielding one of the four cardinal elements of fire, water, earth and air, the Quintessence claims to be all about maintaining the balance between the elements. It is not entirely clear how they do this, but they do. No elemental faction has ever managed to gain the upper hand against the others, no matter how it tried. Whenever any elemental faction has seemed to make progress, the Quintessence, despite being few in number, have managed to restore order and balance very rapidly. However, upon arriving on this planet you have rapidly come to realize that while the Quintessence balance, they also control, suppress, and diminish. Freed from their influence, you have thrived in ways you never before believed possible. You have no desire to return to their control and this personal freedom is far more valuable to you than any fluctuations in the destructive power of elementals battles on this planet.

You feel unsettled on this plane some times. The feeling is becoming more prominent and more frequent. You have begun to wonder in the deepest recesses of your mind whether the Quintessence actually served some purpose other than subverting you and your kind. Because of this uncertainty, the elemental factions have shifted their focus away from outright destruction of the other elements to exerting control over them similar to how the Quintessence controlled the elements on the elemental plane.

\end{document}
