\documentclass[blue]{guildcamp1}
\begin{document}
\name{\bAlienRace{}}

\section*{The Xenid Race}

%\emph{(This document summarizes some of the important points about the alien race. Most of the critical information is on your character sheet, but this may be useful for roleplaying purposes or should other players ask.)}

\subsection*{Biology}

Xenids reproduce sexually but do not have a concept of gender and do not resemble human males or females --- like many plants, all Xenids have both reproductive mechanisms. Xenids give birth to live young and raise them in ``extended family'' groups. Xenids have conscious control over many systems in their bodies, such as emotions, memory, and pain, and they consequently do not suffer from human problems such as painful childbirth. Xenids do not have emotions in the same way humans do. To Xenids, emotions are not reflexive responses to external stimuli, but are consciously decided upon to achieve a certain effect. They might choose to release a chemical similar to adrenaline if they perceive a high-stress situation is happening, or they might induce chemical changes similar to human anger if they want to appear and act more intimidating in a confrontation. Some Xenids choose to rarely use these emotional states and remain cool and logical, while others find these states extremely beneficial and preemptively active them, preferring to always be in the state they find most appropriate for each situation.

Most Xenid enhancements came about through directed genetic re-engineering of the species, but this was a very long time ago and most consider their predecessors to be a totally different species, similar to how many humans perceive early primates. All Xenids are quite intelligent although not necessarily moreso than exceptional humans. Although Xenids have encountered many other races, because of their aversion to interacting with others, even the more scholarly Xenids often forget that many species do not know how to re-engineer themselves. They are often surprised to learn that other species still suffer from all manner of biological problems (unwanted pregnancies, painful childbirth, and so on).

\subsection*{Contact}

This is a special organization within the Xenid hierarchy in charge of all non-warfare interaction with other species. For the two-person scouting missions like the one you are involved with, both members are considered equal rank and neither has direct authority over the other. It is almost unheard of for there to be physical conflict between the partners, and any interpersonal conflict should be conducted out of the view of others --- the Xenid race tries to present itself to others as having a unified consensus. Contact has a set of first-contact principles to be followed when interacting with new species for the first time:

\begin{enumerate}
\item Avoid physically harming others unless attacked.
\item \textbf{Negotiate fairly. Do not renege on a deal made in good faith. There is a famous incident a century ago, where failure to comply with this principle led to a two-decade war.}
\item Think carefully before divulging specifics about Xenids.
\item Do not interfere with local political or religious beliefs.
\item You can participate in rituals and ceremonies if asked to do so, but only after asserting that you fully understand the specifics being asked of you.
\end{enumerate}
 
\subsection*{The Xenid Empire and the Idrian War}

The Xenids have large populations in approximately 50 star systems, with an additional 50 border star systems with small military or scientific outposts. The Idrian race is much smaller (spanning 11 stars) but their technology, especially their AIs, are more sophisticated. Although the Xenids have won several confrontations, their victories have usually only come about because of superior numbers, and their losses have also been considerably higher than the Idrians. Idrians rely almost entirely upon machines to wage their wars and members of the species are almost never seen. The cause of the war was a minor conflict known as ``The Idrian Incident'' where an Idrian robotic scouting squad wandered into a Xenid encampment and started carting away heavy metals. The Xenids responded by destroying the robots and the situation escalated into the current war; it turns out the Idrians consider their robot AIs to be full citizens. Unfortunately, you and the Idrians both thrive best in argon-rich atmospheres, which is a relatively rare atmosphere type and likely one reason your species are still in conflict. There are currently no active diplomatic channels between the two races.

The human ship you have just encountered is approximately ten light years away from one of your border star systems (although it happens to be on the opposite side of the Idrian conflict's front). It would take your scout ship approximately one month to return to the nearest Xenid outpost.

\end{document}