\documentclass[blue]{elementals}
\begin{document}
\name{\bKnowQ{}}

You are one of the few elementals on the human plane who know something about the elemental plane, either because you came from it yourself or because you have learned about it from one of the elementals who did.  You do not know the cosmology that relates the elemental plane to this hot piece of rock, water, and air, but while this alien planet is very different from your ultimate place of origin, most elementals on Earth have adapted well.

Just like on the elemental plane, the four elemental factions have been in a state of near-constant warfare since arriving.  You have astutely realized that these battles are in some ways different here.  In particularly, they are substantially more destructive.  Low and even mid-ranking elementals often sustain serious injury that take months to heal.  In rare occasions, elementals have actually died.  These deaths rock the entire hierarchy.  The amount of fighting has consequently declined substantially as the factions try to work out why the consequences of fighting for dominance on this plane are so extreme.

The only thing that is missing from this plane, which exists on the elemental plane, is the Quintessence.  The Quintessence is best described as a fifth element.  In appearance, Quintessence elementals are white glowing balls or streaks of light, in varying sizes.  Rather than wielding one of the four cardinal elements of fire, water, earth and air, the Quintessence elementals claim to be all about maintaining the ``balance'' between the elements.  It is not entirely clear how they do this, but they do.  No elemental faction has ever managed to gain the upper hand against the others on the elemental plane, no matter how hard it tried.  Whenever any elemental faction seemed to make progress, the Quintessence, despite being few in number, managed to restore order and balance very rapidly.  Their work towards balance is aided by their ability to control other elementals of any type, thereby stopping any fights in progress.  They can also provide a white substance useful for helping elementals heal after the battles were over.

However, while the Quintessence balance, they also control, suppress, and diminish.  Most elementals of the other four types are happy and thriving without the influence of Quintessence.  Losing that freedom is not desirable.  Most elementals probably consider that freedom to be far more valuable than any fluctuations in the destructive power of the elementals' battles on this planet.

Nonetheless, there is a certain feeling that bothers you sometimes.  A sense that something is missing here, related to the absence of the Quintessence.

\end{document}
