\documentclass[blue]{guildcamp1}
\begin{document}
\name{\bVirtuism{}}

As a practitioner of Virtuism, you are familiar with its basic tenets. They are listed below, as they appear in a contemporary work by \cPastor{\MYname{}}.

\begin{itemize}
  \item \cGod{\MYname{}} is great, and can do many things for you. He will do nothing for you however, if you do not strive to help yourself first. When you have done all you can, \cGod{\MYname{}} will do the rest.
  
  \item \cGod{\MYname{}} has given us all the power to affect change. We should never squander that power. 
  
  \item All are expected to look for the signs of the doomsday, and be prepared to do their part to prevent it. 
  
  \item Generosity is crucial to the maintenance of our community of devotees. We must not fixate on worldly possessions, or selfish uses of our time. However, one must never look to the needs of others without first meeting his or her own needs.
  
  \item Worshipers of technology are the enemy of \cGod{\MYname{}}. Atheists worship technology and seek to subvert our devotion to \cGod{\MYname{}} for their own, selfish ends. Use technology if you must, but do not bow to it, and do not allow it to control you.
  
  \item The nuclear family is incredibly important, particularly for the raising of children. You should not marry anyone who has not embraced Virtuism. It is sinful to have intimate relations outside of marriage, and even more so to raise children outside of the holy bond of matrimony
  
  \item Above all, Virtuism strives for clarity of self. Reflect often upon yourself to help you to understand \cGod{\MYname{}}'s plan for you. Never doubt yourself, or what you know to be true through this self reflection.
\end{itemize}

Further, you are familiar with the history of Virtuism:

(\emph Virtuism is an extremely old religion,as old as the world itself. Some say that \cGod{\MYname{}}} even walked this world for a time, thousands of years ago, before he ascended. He has been dead for a very long time, but some people believe that he will return at the end of days. Virtuism warns ardently against being fooled by false Gods. There is substantial literature explaining the existance and manerisms of demons who are puported to appear in the guise of wise prophets from Virtuism's past. It is considered up to all members of Virtuism to recognize and reject these demons.

Virtuism has been through several schools of thought on the state of suffering of it's people. These have included periods of time where there was much agitation for creating a Utopian society, and pacifism was widely embraced. Currently, most of Virtuism rejects pacifism but counsels caution in conflict, particularly when technology is involved. 

Virtuism has always had an uneasy relationship with technology. Some early texts indicate that at one time, Virtuism embraced technology, but when scientists and engineers turned their back on the Tenets of Virtuism, the church rejected them and their new machines. For many years, Virutism has shifted between outright opposition, which led to several bloody riots at leading research universities, and ambivalence, with many practitioners of Virtuism openly supporting technology companies. Modern Virtuism acknowledges that many technologies are critical to our day to day lives, but counsels that we should never be ruled by it.


\end{document}