\documentclass[blue]{elementals}
\begin{document}
\name{\bHumanHistory{}}

The year is currently 2650 CE. Humanity has gone through a long and messy history since the 21st century, the relevant parts of which are detailed below. 

{\bf Azis and Cits:}
In the 24th century, an inter-continental war broke out. During this period, humans developed an array of technologies, by far the most important of which was ``artificial zygote insemination'', which is a combination of intensive genetic engineering and psychological conditioning that result in the birth of Azi, a highly talented and specialized form of human. Through years of extensive psycho-sensory training, these humans can be trained as experts in just about anything. Azi make wonderful soldiers, mechanics and scientists, and during their upbringing each is conditioned with specially-prepared visual-auditory stimuli called ``tape''. During their training period, they are conditioned to respond mostly to the orders of a specific human handler. They will do most things asked of them by their supervisor as long as it does not conflict with their basic taping.

Azi have come to play a prominent role in human society, but having a class of humans that are extremely good at what they are trained to do, and unlikely to question most orders, is of course a temptation for some Cits (``citizens'', or non-Azi humans). There are a few dark souls who might wish to usurp Azi for their own ends. Every now and then, stories surface of Azi who have been re-taped too quickly.  Taping is a process designed to take weeks or months. There is no safe way to re-tape an Azi in a shorter span of time. It can be done, but at a terrible price. The Azi is rarely able to recover, and may be non-functional for the rest of his or her life.  The legal consequences for re-taping an Azi too rapidly are extreme.

{\bf Elementals:}
One hundred years ago, the world was changed forever when \cGrandfather{\full}, in a foolish attempt to make more powerful Azi soldiers, somehow managed to build a connection between Earth and the elemental planes known as the Conduit. Through the Conduit came four hugely powerful elementals --- one each of fire, water, earth and air. What ensued was a period of utter chaos as the elementals wreaked havoc across the world. Although they have since spawned many more minions, the four original elementals still reign supreme over their factions.

%While not everyone accuses \cGrandfather{} of having caused this disaster on purpose, all looked to him to fix it. He quickly started work again, and those close to him claim that he was even making progress. But one night, less than a month after the original disaster, a group of Azi broke into \cGrandfather{\their} lab, destroyed all of \cGrandfather{\their} research, and killed \cGrandfather{\them}. The police investigation that followed determined that the Azi that perpetrated the crime had been brutally re-taped. The psychologists determined that the re-taping process could not have taken more than a few hours. Unfortunately for the investigation, while most the Azi were apprehended within a few days, they were all deemed completely insane, and most committed suicide within a week despite being under close surveillance. Whoever was the mastermind behind this crime was never brought to justice.

Literally hundreds of thousands of people have died since the elementals were created. It is not clear that the elementals have even noticed. Humanity has long sought a way to fight back, but with limited success. Despite years of research by scientists such as Galina Schwartz\footnote{Not in game} and her Azi partner \cScientist{\full}, the unorthodox \cMS{\full}, and \cGrandfather{\full}'s granddaughter \cGD{}, humans still have all too few ways to resist elementals.  It doesn't matter whether the elemental is fire, water, earth or air - humans die when they get too close. For the strongest elementals, ``close'' could be within 100 meters. Some of the weakest elementals do not passively destroy things, but can do so easily if annoyed. One particularly disturbing phenomenon involving elementals is that of mind control.  They can apparently compel humans to do things against their will. To compound the problem, the phenomenon often leaves the human with amnesia, and so their actions can only be pieced together from the accounts of bystanders.

A small, militant faction called the Extinguishers took it upon themselves to battle the elementals.  Led by gifted military leaders, such as members of the \cDema{\formal} family, they used ingenuity and contraband technology to lure a few of the weakest elementals to their deaths.  However, no human, however cunning, can stand against the stronger elementals, and so, within the last 10 years or so, a new movement emerged among the humans. Its proponents argued that humanity should seek not to fight the elementals but to ally with them, and viewed the Extinguishers as a terrorist faction that must be eliminated if humans and elementals were ever to make peace.

A growing number of humans believe that peace is in fact the answer. The diplomat \cDiplomat{\full} is testing the idea that if elementals could be made to see the value of humans, they would not destroy, and maybe even actively protect humans.  So far \cDiplomat{} is still alive, so perhaps it has some merit. It all relies on the continued goodwill of the elementals however, and that makes many people understandably nervous. President \cLeader{\full}, the leader of the \cNewUN{\full}, and the high ranking diplomat, \cAvatar{\full}, championed the cause, which culminated with the defeat and trial of the Extinguishers' leaders. Even a scion of the \cDema{\formal} family has declared support for a human-elemental alliance: \cDema{}, who is now Secretary of State. The Air King, \cKing{}, seems to be willing to entertain the possibility of peace, and \cLeader{} and \cAvatar{} are moving forward with the process. Some people, including \cLeader{}'s Azi bodyguard \cRomeo{\full} (whose job it is to be suspicious), are wary of \cKing{}'s sudden good will; others say not to look a gift horse in the mouth. Regardless, \cLeader{} has secured an invitation to an elemental council tonight. It is the first time humans will be able to interact with elementals in some meaningful way. The world waits with bated breath for a positive outcome.

\begin{members}
  \member{\cLeader{}} President of the \cNewUN{\full}, whose goal is to formalize a human-elemental treaty.
  \member{\cDema{}} Secretary of State, a former member of a militant organization who now supports the \cNewUN{\full}.
  \member{\cAvatar{}} A high-ranking diplomat who champions a human-elemental treaty.
  \member{\cDiplomat{}} An Azi diplomat who also supports a human-elemental treaty.
  \member{\cGD{}} \cGrandfather{\full}'s granddaughter, a talented scientist in \cGD{\their} own right. 
  \member{\cScientist{}} An Azi scientist who strongly believes in ethical research practices.
  \member{\cMS{}} A brilliant scientist who is not afraid to bend the rules.
  \member{\cRomeo{}} An Azi soldier, who is the President's bodyguard.
\end{members}


%%what else does everyone know?

\end{document}
