\documentclass[blue]{elementals}
\begin{document}
\name{\bElemental{}}

Being an elemental on the human plane is strange for you. There are many concepts that humans have that just so \emph{alien}. Time passes here. No, more than that --- time passes and it \emph{matters}. Humans age and die, something that never happens to elementals. And humans have such a strong sense of property. Everything is ``me'' and ``mine''.  They get so very upset if you happen to wander through a field and flood it, or the wind from your passing destroys a small town. They seem to think it is somehow your responsibility to replace it. And do they whine and complain when a human ends up dead! It certainly isn't your fault that they are combustible. How the species survives without the ability to reform their substance is quite beyond you.

{\bf History:}
Everyone knows the history of elementals on this human plane. One hundred years ago, a human somehow managed to open the Conduit and pull through 4 mid-level elementals, one of each of the cardinal elements Fire, Water, Earth and Air. These elementals, Fire Queen \cQueen{}, Earth King \cEarthKing{}, Air King \cKing{}, and Water Queen \cWaterQueen{},  quickly expanded over the earth by aliquoting their power into minions. As on the elemental plane, there is no love lost between the factions and infighting reigns supreme. Each faction is always trying to one-up the others and gain mastery over the whole world.

{\bf The Conduit:}
The Conduit is the weakest point between the human and elemental plane. Once every 10 years or so, the planes come into close proximity with each other, and it is therefore particularly easy to open the Conduit between the planes. That time is now. The planes will be most aligned right at midnight, and they won't be so closely aligned again for another 100 years. The last time the Conduit was opened was 100 years ago when the first elementals were brought over. If a way to open the Conduit can be found, elementals are capable of calling over more of their kind through. Before midnight, the connection cannot be sustained for any length of time and only a \emph{momentary opening} is possible during which only the weakest of elementals can come through. These are useful servants, to be sure, but little more than that. But as midnight approaches, the connection to the elemental plane can be sustained for an extended period of time allowing a \emph{terminal opening} of the Conduit.  During this time, elementals of substantial power that are capable of truly affecting the balance of power on Earth can traverse the connection.

{\bf The Suppressor Field:}
As a general rule, elementals do not like to be near the Conduit because it has a damper field of some kind. For reasons unclear, even the strongest elementals on this plane cannot wield their powers with impunity within the field. Powers are so dampened, in fact, that an elemental and a human might be nearly equally matched in fighting prowess.

\emph{The suppressor field extends over all of game space.}

{\bf The Hierarchy:}
One of the most important aspects of elemental culture is the hierarchy. Lower rank elementals must defer to higher rank elementals of their faction. The King or Queen is the highest ranking element of the faction on this plane at primal tier. Most factions have three or four tiers under the King or Queen.  Since the suppressor field dampens all elemental power, it will be harder than usual to determine the rank of an elemental. Although it is rarely necessary, an elemental of higher rank can compel a lower ranking elemental of the same element to do some task.

The hierarchy is more than just a social formality, though. Since all lower ranking elements are spawned from the Kings and Queens, their abilities and power are tied to that of their leader. If the leader of an elemental faction were to die, the faction would be crippled.

%%{\bf Enslaving Humans:}
%%Elementals also have the ability to compel humans to some extent. This is not common practice because it is rare that elementals find some use for humans. Enslavement is a long and tedious process and doesn't last for very long; it is rarely worth the trouble. It does potentially have its uses however, particularly to tip the balance between elemental factions.

{\bf Elemental Essence:}
All elementals have elemental essence. Normally essence is just part of who you are, but under certain circumstances it can be removed. Essence, like blood, will regenerate given time, but it takes several days.

{\bf Reading and Writing:}
Elementals cannot read or write in English unless the character knows otherwise. Usually elementals would just enslave a convenient human to write down anything that they needed to have written down.

{\bf The Elemental Council:}
Once every 5 years, the elements hold a council. For one night only, the factions put aside their squabbling and come together to discuss issues that affect them all. Normally the council is held on an island in the middle of the Pacific Ocean, as far away from humans as possible, but since the two planes are so close together tonight, the Conduit has been selected as the location, despite the suppressor field.  Representatives from the Fire, Earth, and Air factions will all be in attendance; Water has elected not to come.  However, for the first time ever, humans will be present.  \cKing{} is considering an alliance with them and has invited them to send representatives to the Elemental Council.

\begin{members}
  \member{\cQueen{}} Queen of the Fire elementals, who has publicly proclaimed that \cQueen{\they} intend to open the Conduit to bring over more elementals of all factions.
  \member{\cPyro{}} Second tier Fire elemental, who is impetuous and militant.
  \member{\cJuliet{}} Second tier Fire elemental, intermediary between \cQueen{} and \cKing{}.
  \member{\cLoyal{}} Second tier Earth elemental, a strong believer in following the rules.
  \member{\cRogue{}} Second tier Earth elemental, a believer in the use of unorthodox ways to achieve goals.
  \member{\cMinion{}} Third tier Earth elemental, \cLoyal{}'s underling.
  \member{\cMiniEarth{}} Third tier Earth elemental, also \cLoyal{}'s underling.
  \member{\cKing{}} King of the Air elementals, who of the elementals has the closest ties to humans.
  \member{\cNaturalist{}} Second tier Air elemental, a scientist who is fascinated by humans.
  %\member{\cMiniAir{}} Third tier Air elemental, brought along by \cKing{} on a whim.
  %\member{\cMiniWater{}} Third tier Water elemental, here as an unofficial observer.
\end{members}

\end{document}
