%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[notebook]{guildcamp1}
\begin{document}

%\item 
%\item 

\startnotebook{\nAlienQuestions{}}

\begin{page}{pre}
This notebook is not transferable. You may open it to the first page at the start of the game.
\end{page}

\begin{page}{first}

You are mostly aware of the details of procreation, but the tutorial provided no idea as to how humans actually go about finding a mate.
Acquire two perspectives on this topic from two different humans. When you complete this step, you may turn to \nbref{second}.

\end{page}

\begin{page}{second}

Well that was enlightening. Raise your $\Omega$ score by 1. The humans around you appear to be engaged in a religious ritual related to
finding a compatiable partner. What purpose does a wedding serve? Interview two people participating in the wedding on
this topic for at least 2 minutes. When you are done, you may turn to \nbref{third}.

\end{page}

\begin{page}{third}

The wedding is interesting, but it seems to be a small part of a broader religion, and there appear to be multiple religions within the society.
Given the existence of multiple religions, how does a human determine which one is correct? Gather at least two different perspectives on this subject.
When you are done, you may turn to \nbref{fourth}.

\end{page}

\begin{page}{fourth}

Your sister loves studying religious rituals, if you manage to get out of here this will make for some great dinnertime conversations.
Raise your $\Omega$ score by 1. The cultural basics out of the way, Now the really tough question: 
Why is the technology level inside the simulation so primitive compared to the host ship? As far as you can tell, both were constructed by humans.
When you have the answer to this question, turn to the next page.

\end{page}

\begin{page}{fifth}

Humanity certainly has the potential to be a dominant species in the galaxy, once you teach them the basics of making interstellar engines.
Gain 5 $\Omega$, but not past your maximum value.

%A vision forms in your head of what you recognize as a ``teddy bear''. You are fairly convinced that this is the precious backup copy of the world you have been searching for.
\end{page}

\endnotebook

\end{document}
