%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[notebook]{guildcamp1}
\begin{document}

\startnotebook{\nBrainDamage{}}

\begin{page}{pre}
This notebook is not transferable. You may open it thirty minutes into the game.
\end{page}

\begin{page}{first}

In observing these humans you have noticed a small number of them holding hands. You do not believe this process is directly involved in transferring genetic material, but it still seems to serve some important purpose. To find out exactly what purpose, you suppose you will just have to experiment. Hold hands with two different humans for at least five seconds. When you complete this step, you may turn to \nbref{second}.

\end{page}

\begin{page}{second}

That sensation was very odd but also strangely \ldots pleasant. Raise your $\Omega$ score by 1. Xenids have something similar to emotions as well but there are definitely some important differences. You decide to explore more human emotions. You pick one at random: embarrassment. You are not sure how to induce this emotion, but the tutorial you went through on the ship provided a video suggestion. Spin in circles with your arms extended for at least five seconds while another human observes you. When you are done, you may turn to \nbref{third}.

\end{page}

\begin{page}{third}

That was very embarrassing! This emotion has none of the pleasant properties of the previous one. You will have to select emotions to explore more carefully. You pick ``peacefulness'' next. Go meditate quietly on the universe in a room by yourself for one minute. You may not talk to anyone and need to avoid any significant distractions. Then you must have a two minute discussion regarding the topic of your meditation with a human. When you are done, you may turn to \nbref{fourth}.

\end{page}

\begin{page}{fourth}

That was much better! Although you found your mind wandering and starting to ponder frustratingly unanswerable questions such as ``why do I exist?'', ``what is the meaning of life?'', ``what is the difference between a physical brain and a simulated consciousness?'', and ``perhaps my real body is also inside a simulation the way this one is?''. You will have to try this ``meditation'' back in your real body sometime. In fact, you can feel your real physical body responding positively to this meditative practice --- raise your $\Omega$ score by 1. The next emotion you intend to explore is ``spirituality'', which seems to be quite uniquely human. You need to receive a blessing from a religious figure or participate in a religious ceremony. When you do so, turn to turn to \nbref{fifth}.

\end{page}

\begin{page}{fifth}

That was very enlightening! You have never experienced anything quite like it. Raise your $\Omega$ score by 1. This emotional process seems to have duplicated some of the much-needed maintenance on your physical body. Tear up your ``Mental degradation'' ability.

\end{page}

\endnotebook

\end{document}
