%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[notebook]{elementals}
\begin{document}

%\item 
%\item 

\startnotebook{\nEnslavementResearch{}}

\begin{page}{first}

You have plenty of psionic data feeds from observing the elemental enslavement process first-hand, but for some reason the elemental biochemistry seems to have shifted now that they are so close to the Conduit. You will need to gather	 some more up-to-date experimental data. Find your trusty \emph{tricorder}, a \emph{photodiode}, and a \emph{coffee mug}. With these in your hands (remember two of these items are 1-hand bulky), you need to watch two different factions of elementals attempt to enslave a human. In each case, the victim must be successfully enslaved, and cannot be yourself.

Once you have data on two humans being enslaved by elementals from different factions, turn to \nbref{second}.

\end{page}

\begin{page}{second}

Your blasted \emph{control rod} is having thermal problems again. You should never have tested it on a fire elemental; it melts the circuitry. Find a large body of water and dunk the rod in it for two minutes.

When you complete this step, you may turn to \nbref{third}.

\end{page}

\begin{page}{third}

Finally...the rod is ready for another test. Unfortunately, the rod is very weak --- even if you can find a willing elemental participant, it will have no effect on an elemental unless its psionic capabilities are below the rod's power threshold. Your tricorder can examine the $\beta$ stat for elementals. The rod can only work on elementals with a $\beta$ value less than or equal to 1.

Once you find an appropriate victim (willing or not), have the elemental strapped into one of the chairs in your laboratory and activate the rod as an ``Enslave 5'' ability (follow the mechanics delineated on ``The Elemental Enslavement Mechanic'' greensheet).

When you complete this step, you may turn to \nbref{fourth}.

\end{page}

\begin{page}{fourth}

\emph{You may now use the rod to enslave elementals with ``Enslave 5'', but the rod takes a while to recharge and may only be activated every 20 minutes.}

The rod is working well, but despite your best efforts it has never been able to work beyond the weakest elementals. Fortunately you have the special tape you designed to train Azi, although you will need to update it in light of the elemental's mutating biology in the presence of the Conduit. Towards this end, use your tricorder while you observe two different elementals attempt to enslave an Azi (the attempts do not have to succeed).

When you complete this step, you may turn to \nbref{five}.

\end{page}

\begin{page}{five}

There is something eerily incomplete about the data you've been gathering. It appears as if there is already some control mechanism built into all elementals -- someone has carefully designed a mechanism that allows them to establish an overriding connection straight to their psionic core. You have never seen this control pathway used on Earth, so you can only assume it comes from the elemental planes, but studying it is not going to be easy.

First, you will need \emph{elemental essence}, a core component of all elementals. You might be able to find it naturally, but you also know how to extract it directly from an elemental. Seat an elemental in one of the chairs in your lab, then spend one minute poking the elemental with whatever you have at hand. At the end of this period, the elemental must give you one elemental essence, if it has any left. When you have an elemental essence, you may turn to \nbref{six}.

\end{page}

\begin{page}{six}

Now comes the tricky part. To study this mysterious ``master race'' that constructed the elemental's control pathway, you will need to participate in a \emph{momentary opening} of the Conduit. You must put your \emph{elemental essence} on the cart, then study the Conduit and the essence throughout the momentary opening. This experiment will destroy the essence.

When the opening is completed, you may turn to \nbref{seven}.

\end{page}

\begin{page}{seven}

Excellent...you are severely impressed by the subtlety and thoroughness by which the elementals are effectively enslaved on a global scale. The elementals on Earth are very fortunate that none of these mysterious slave-masters are about, as they are apparently quite common on the elemental planes.

You now know exactly how to modify your tape to exploit this new pathway -- and with these modifications, you think there is a chance you will be able to control even the most powerful of elementals, with enough Azi. Spend three minutes in your lab to complete your \emph{Azi education tape}. Now it is again ready to re-train Azi to enslave elementals.

Once you have working tape, you need to actually find Azi to retape. Ideally, you would like to convince the political leadership (probably with the help of \cDema{}) to support this retaping as clearly necessary for human survival, but you will do it without any support if need be. To retape an Azi, they must first sit in one of the chairs in your lab, and do not have to be willing, as long as they are restrained. Then expose them to the tape for three minutes (you can train multiple at once). After this period, tell them to open their ``Z packet''. You are now their supervisor and for the most part, they should obey your orders.

When you have successfully retrained an Azi, you may turn to \nbref{eight}.

\end{page}

\begin{page}{eight}

\emph{You may continue to retape Azi.}

Now you just need to test out your newly-empowered Azi on real elementals. Ues your Azi minions as you see fit. You are confident that possibly with two, definitely with three, Azi working together, they could control even \cQueen{} or \cKing{}. All other elementals should be controllable with only a single Azi.

It's about time someone took charge of this chaotic situation.

\end{page}

\endnotebook

\end{document}
