%%%%%
%%
%% Research Notebooks live in this directory.  This file doubles as a
%% latex'able example notebook.
%%
%% Notebook macros (in ../Lists/notebook-LIST.tex, presumably) each
%% have a file that lives here.  The argument to \startnotebook{...}
%% probably should be the macro for the given whitesheet.  However,
%% you can also just use \name{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%%%%

\documentclass[notebook]{guildcamp1}
\begin{document}

\startnotebook{\nPlayWithDad{}}

\begin{page}{pre}
This notebook is not transferable and explains how to play with dad. You may open it immediately upon start of game.
\end{page}

\begin{page}{first}

You are so excited about meeting your dad and getting to play with him. But first you need a toy. Find a {\bf ball}, then play catch with \cGroomA{} for 3 minutes. Role play accordingly.  Once you're finished playing catch, you may turn to \nbref{second}.

\end{page}

\begin{page}{second}

That was fun. Dad is so much better at catch than mom. It's so nice that he's spending time with you. Maybe you should get him a gift? Find a cookie and give it to dad.  Once you've given dad a cookie, you may turn to \nbref{third}.

\end{page}

\begin{page}{third}

Playing ball isn't the only thing you'd like to do with your dad.  You love to color in school, so why not spend some time drawing with dad?  Acquire a set of {\bf crayons} and then color with \cGroomA{} for 5 minutes. Role play accordingly. When you are done, you may turn to \nbref{fourth}.

\end{page}

\begin{page}{fourth}

Playing with dad is great. He's so much fun. But always being around adults is boring. Slip off and go check out the construction site all alone. The adults seem to think it might be dangerous, so it must be fun.

When you've investigated the construction site for 2 minutes, you may turn to \nbref{fifth}.

\end{page}

\begin{page}{fifth}

Enough of being on your own, lets find dad again. It is definitely time to play your all time favorite game ever, tic-tac-toe.  Find your dad and play with him until you have  each won 3 games.  Better not tell him though or he might lose to you on purpose! Afterwards, you may turn to \nbref{sixth}.

\end{page}

\begin{page}{sixth}

Yay for playing thinking games like that. But you are restless again. I wonder if dad is into playing sports and running around? Play tag with dad and two other adults for 2 minutes. Once you are done you do so, turn to \nbref{seventh}.

\end{page}

\begin{page}{seventh}

Hanging out with dad is so much fun. If only he weren't going to marry that other lady. He really ought to get back together with mom. Spend 5 minutes in conversation with \cGroomA{} and try to convince him not to marry that lady and get back together with mom instead. Once you've tried to convince him, turn to \nbref{eighth}

\end{page}

\begin{page}{eighth}

Congratulations, you have successfully played with dad! You are so excited that you just can't keep it to yourself. Tell everyone you see for the next 2 minutes (you only need to tell someone once) that you had such a great time playing with your dad!

\end{page}

\endnotebook

\end{document}
