%%%%%
%%
%% This file sets up the Abil datatype and creates Abil macros.  These
%% are for abilities that characters may have.
%%
%%%%%

\DECLARESUBTYPE{Abil}{Element}
\PRESETS{Abil}{
  \F\MYtext	%% text of ability, read by user
  \F\MYeffect	%% effect text of ability, read by recipient(s)
  }


%%%%%
%% \ability{<name>}{<text>}{<effect>}
%%
%% \ability is a wrapper around \INSTANCE, useful for 1-shot abilities,
%% etc.
\newinstance{Abil}{\ability[3]}{
  \s\MYname{#1}\s\MYtext{#2}\s\MYeffect{#3}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\NEW{Abil}{\aTest}{
%  \s\MYname	{Test Ability}
%  \s\MYtext	{You are a test.}
%  \s\MYeffect	{This is a Test.}
%}
%
%\NEW{Abil}{\aSpecial}{
%  \s\MYname	{Special Powers}
%  \s\MYtext	{You have special powers, as detailed in your \gTest{}
%		greensheet.}
%  \s\MYeffect	{I have special powers!}
%  \s\MYgreens	{\gTest{}}
%  \suite
%  }

\NEW{Abil}{\aFiremansCarry}{
  \s\MYname	{Fireman's Carry}
  \s\MYtext	{You can carry a body as if it were two-hands bulky.}
  \s\MYeffect	{I can carry this body well.}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


  
%% Basic DarkWater-style Martial Attack abilities


%% Everyone has these 3
\NEW{Abil}{\aAssist}{
  \s\MYname	{Assist}
  \s\MYtext	{You can assist someone else's attack.  You must be
		within ZoC of both the attacker and target.  Within two
		seconds of an attack, direct this at the attacker,
		saying ``\MYname'' and your CR.}
  \s\MYeffect	{I assist your attack.}
  }

\NEW{Abil}{\aKnockOut}{
  \s\MYname	{Knock Out}
  \s\MYtext	{You can knock someone out as an attack. Say ``\MYname'' and your CR.}
  \s\MYeffect	{I knock you out.}
  }

\NEW{Abil}{\aWound}{
  \s\MYname	{Wound}
  \s\MYtext	{You can wound someone as an attack. Say ``\MYname'' and
		your CR.}
  \s\MYeffect	{I wound you.}
  }


%% the \basecombat macro can be prepended to the Char abils list
%% (in char-LIST.tex)
\def\basecombat{\aKnockOut{}\aWound{}\aAssist{}}

%% only some people have these
\NEW{Abil}{\aDisarm}{
  \s\MYname	{Disarm}
  \s\MYtext	{You can disarm someone of one item as an attack.  Say
		``\MYname'' and your CR.  Point at the item you want to
		disarm them of.  If the attack works, they must drop that item.}
  \s\MYeffect	{I disarm that item.}
  }

\NEW{Abil}{\aRestrain}{
  \s\MYname	{Restrain}
  \s\MYtext	{You can restrain someone as an attack.  Say ``\MYname''
		and your CR.  You may freely drag, attack, or (if you have
		a weapon) killing-blow them.  To be free to do anything else, or if
		your health state changes, you must incant ``release'' and let them
		go.}
  \s\MYeffect	{I restrain you.  You are restrained until I incant
		``release.''}
  }
\NEW{Abil}{\aThrow}{
  \s\MYname	{Throw}
  \s\MYtext	{You can throw someone as an attack.  Say ``\MYname'' and
		your CR.  Point in the direction you want to throw them.}
  \s\MYeffect	{I throw you.  Go in the direction I point ten full steps
		or until you hit a wall or similar.}
  }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Abil}{\aWorkConduit}{
  \s\MYname	{Work the Conduit Machine}
  \s\MYtext	{I know how to work this machine to open the conduit.}
  \s\MYeffect	{This ability allows you to work the Conduit Machine. You may flip over the greensheet ``\gConduitCover{}'' and read/interact with the sheet entitled ``\gConduit{}''' which is underneath it.
  
This information is transferable. You may freely tell other characters how to work the machine and they will gain this ability as well. This information is also extractable. You may be compelled under enslavement to reveal it. If you tell someone how to use the machine, direct them to acquire a copy of this ability from the $\Omega$ Packet in -013.}
}

\NEW{Abil}{\aMadness}{
  \s\MYname	{Psychlim: Maniacal Planner}
  \s\MYtext	{I just thought of the most marvelous idea, but regrettably you are not smart enough to comprehend it.}
  \s\MYeffect	{You periodically think of insidiously clever ways to accomplish whatever you are currently planning to do, and audibly laugh, giggle, or cackle for no apparent reason. This is very likely to happen in the middle of conversations with others, especially when they start to bore you (which they always do) and your mind wanders to more important intellectual matters.}
}

\NEW{Abil}{\aAziLimits}{
  \s\MYname	{Psychlim: My Supervisor Knows Best}
  \s\MYtext	{If I feel conflicted, my supervisor has all the answers.}
  \s\MYeffect	{Your tape training has conditioned you to understand that your supervisor has all the answers.  If you feel conflicted about anything, you should consult him or her, and your supervisor will resolve your difficulties.  As such, you will obey your supervisor's commands unless they conflict irreconcilably with your basic persona.}
}

\NEW{Abil}{\aAvatarPsychlim}{
  \s\MYname	{Psychlim: Let's Chat}
  \s\MYtext	{Vitality and Patrick sometimes find it easier to just talk about it.}
  \s\MYeffect	{If think you are alone, take the opportunity for \cAvatar{} and Vitality to have a chat, since just talking is easier for \cAvatar{}.  If \cAvatar{} says or does something Vitality objects to, or Vitality wants \cAvatar{} to do something \cAvatar{\they} finds objectionable, \cAvatar{} will ``talk to himself'' regardless of the presence of others.  Volume should be proportional to the intensity of the disagreement.}
}

\NEW{Abil}{\aRaidLab}{
  \s\MYname	{Raid a Laboratory}
  \s\MYtext	{I am conducting an exhaustive search of this laboratory.}
  \s\MYeffect	{You can only use this ability in conjunction with a scientist. You and the supporting scientist must search around the entire lab space for four minutes. This action is very obvious and can be interrupted by others. At the end of this time, you may interact with the ``lab space'' sign for that lab, to get a summary of the research the scientist is conducting.}
}

%%Ele enslavement relevant abilities:
\NEW{Abil}{\aFireEnslave}{
  \s\MYname	{Enslavement (Fire)}
  \s\MYtext	{I attempt to enslave you.}
  \s\MYeffect	{This ability allows you attempt to enslave fire elementals and humans. This action has a 15 minute cool-down whether it works or not. Refer to the \gEnslave{} greensheet for details.}
  \s\MYgreens	{}
}

\NEW{Abil}{\aEarthEnslave}{
  \s\MYname	{Enslavement (Earth)}
  \s\MYtext	{I attempt to enslave you.}
  \s\MYeffect	{This ability allows you attempt to enslave earth elementals and humans. This action has a 15 minute cool-down whether it works or not. Refer to the \gEnslave{} greensheet for details.}
  \s\MYgreens	{}
}

\NEW{Abil}{\aAirEnslave}{
  \s\MYname	{Enslavement (Air)}
  \s\MYtext	{I attempt to enslave you.}
  \s\MYeffect	{This ability allows you attempt to enslave air elementals and humans. This action has a 15 minute cool-down whether it works or not. Refer to the \gEnslave{} greensheet for details.}
  \s\MYgreens	{}
}

\NEW{Abil}{\aQEnslave}{
  \s\MYname	{Enslavement (Quintessence)}
  \s\MYtext	{I attempt to enslave you.}
  \s\MYeffect	{This ability allows you attempt to enslave any elemental faction, but not humans. {\bf For the purpose of this ability you have an effective CR of 6.} This action has a 15 minute cool-down whether it works or not. Refer to the \gEnslave{} greensheet for details.}
  \s\MYgreens	{}
}


\NEW{Abil}{\aAziEnslave}{%%Grandmother has CR 15
  \s\MYname	{Enslavement (Azi)}
  \s\MYtext	{I attempt to enslave you.}
  \s\MYeffect	{This ability allows you attempt to enslave any elemental faction, but not humans. {\bf For the purpose of this ability you have an effective CR of 6.} This ability also allows you to assist/be assisted when enslaving a target (ie: 2 players using this ability have an effective CR of 12). This action has a 15 minute cool-down whether it works or not. Refer to the \gEnslave{} greensheet for details.}
  \s\MYgreens	{}
}

%%Azi can resist enslavement
\NEW{Abil}{\aResistEnslave}{
  \s\MYname	{Resist Enslavement}
  \s\MYtext	{I resist your attempt to enslave me.}
  \s\MYeffect	{This ability allows you resist enslavement by elementals who use the any ``Enslavement(type)'' ability on you. If you choose to, you can resist enslavement via this ability. You do not have to do so.
  }
}

%%Conduit sealing/unsealing abilities
\NEW{Abil}{\aDrawBlood}{
  \s\MYname	{Draw Blood}
  \s\MYtext	{I am drawing blood from you. You suffer a CR loss for 3 minutes.}
  \s\MYeffect	{You can draw blood from a target player. Refer to associated greensheet for details.)
  }
}

\NEW{Abil}{\aUnsealConduit}{
  \s\MYname	{Remove seal}
  \s\MYtext	{I know how to remove this seal.}
  \s\MYeffect	{You know how to clean off this seal. (You may interact with ``\sSealedLocationSheet{}'' via this ability. Refer to the associated greensheet for details.}
  \s\MYgreens	{\gUnsealConduit{}}
}

\NEW{Abil}{\aCollaborate}{
  \s\MYname	{Collaborate}
  \s\MYtext	{I can collaborate with scientists.}
  \s\MYeffect	{You have been watching humans for a long time and have great powers of observation and deduction. You can therefore collaborate with scientists. You are considered a scientist for mechanics that require a scientist.}
}

\NEW{Abil}{\aMakeWhite}{
  \s\MYname	{Synthesize \iWhiteQ{}}
  \s\MYtext	{I can synthesize \iWhiteQ{}.}
  \s\MYeffect	{You have figured out how to synthesize \iWhiteQ{}. If you would like to do so, find a quiet location conducive to meditating (the place where the water elementals would have met may work), destroy one \iQEssence{}, and take one \iWhite{} from that location. {\bf You may use this ability this once every 30 minutes.}}
}

\NEW{Abil}{\aLearnSong}{
  \s\MYname	{Teach Me a Song}
  \s\MYtext	{I am listening intently to your song.}
  \s\MYeffect	{You love songs! You can pick them up just by hearing them once. If you convince someone to sing a song, or happen to be nearby as they are doing so, you can learn it as long as you interact for at least a minute. If there is an ability associated with the song, you can get the corresponding ability card from a GM.}
}

\NEW{Abil}{\aModifierSummonFire}{
  \s\MYname	{Conduit Modifier: Fire's Song}
  \s\MYtext	{I am singing a song that attracts fire elementals. Flames surround me.}
  \s\MYeffect	{This ability can only be used to modify the Conduit as it is being opened. You must place this ability on the ``Conduit modifiers'' sheet at the start of the opening and remain within 2 ZOC of the cart throughout the entire process. Your song attracts fire elementals from the elemental plane towards the opening on the other side of the Conduit. There can be multiple instances of this modifier on the Conduit to increase the strength of the song.}
}

\NEW{Abil}{\aModifierSummonAir}{
  \s\MYname	{Conduit Modifier: Air's Song}
  \s\MYtext	{I am singing a song that attracts air elementals. A small thunderstorm surrounds me.}
  \s\MYeffect	{This ability can only be used to modify the Conduit as it is being opened. You must place this ability on the ``Conduit modifiers'' sheet at the start of the opening and remain within 2 ZOC of the cart throughout the entire process. Your song attracts air elementals from the elemental plane towards the opening on the other side of the Conduit. There can be multiple instances of this modifier on the Conduit to increase the strength of the song.}
}

\NEW{Abil}{\aModifierSummonEarth}{
  \s\MYname	{Conduit Modifier: Earth's Song}
  \s\MYtext	{I am singing a song that attracts earth elementals. The earth vibrates around me.}
  \s\MYeffect	{This ability can only be used to modify the Conduit as it is being opened. You must place this ability on the ``Conduit modifiers'' sheet at the start of the opening and remain within 2 ZOC of the cart throughout the entire process. Your song attracts earth elementals from the elemental plane towards the opening on the other side of the Conduit. There can be multiple instances of this modifier on the Conduit to increase the strength of the song.}
}

\NEW{Abil}{\aModifierSummonWater}{
  \s\MYname	{Conduit Modifier: Water's Song}
  \s\MYtext	{I am singing a song that attracts water elementals. The earth vibrates around me.}
  \s\MYeffect	{This ability can only be used to modify the Conduit as it is being opened. You must place this ability on the ``Conduit modifiers'' sheet at the start of the opening and remain within 2 ZOC of the cart throughout the entire process. Your song attracts water elementals from the elemental plane towards the opening on the other side of the Conduit. There can be multiple instances of this modifier on the Conduit to increase the strength of the song.}
}

\NEW{Abil}{\aModifierSummonQuintessence}{
  \s\MYname	{Conduit Modifier: Quintessence Song}
  \s\MYtext	{I am singing a song that attracts quintessence elementals. Small white wisps of light flicker into existence around me.}
  \s\MYeffect	{This ability can only be used to modify the Conduit as it is being opened. You must place this ability on the ``Conduit modifiers'' sheet at the start of the opening and remain within 2 ZOC of the cart throughout the entire process. Your song attracts quintessence elementals from the elemental plane towards the opening on the other side of the Conduit. There can be multiple instances of this modifier on the Conduit to increase the strength of the song.}
}

\NEW{Abil}{\aModifierElectromagnet}{
  \s\MYname	{Conduit Modifier: Electromagnet}
  \s\MYtext	{I am hooking up my device to the Conduit.}
  \s\MYeffect	{This ability accompanies the Electromagnet. If you lose control of the Electromagnet, leave this ability with it. You can use this ability even if you don't know what the Electromagnet does. This ability can only be used to modify the Conduit as it is being opened. You must place this ability on the ``Conduit modifiers'' sheet at the start of the opening and remain within 2 ZOC of the cart throughout the entire process. Make sure a GM is present before starting to open the Conduit.}
}

\NEW{Abil}{\aModifierChannelWhite}{
  \s\MYname	{Conduit Modifier: Channel Elementium}
  \s\MYtext	{I am making significant modifications to the machine that controls the Conduit opening.}
  \s\MYeffect	{This ability can only be used to modify the Conduit as it is being opened. You must place this ability on the ``Conduit modifiers'' sheet at the start of the opening and remain within 2 ZOC of the cart throughout the entire process. Make sure a GM is present before starting to open the Conduit. Your modifications should cause Elementium to be transferred through the Conduit in very large quantities.}
}


\NEW{Abil}{\aFirstAid}{
  \s\MYname	{First Aid}
  \s\MYtext	{I know first Aid.}
  \s\MYeffect	{This ability can be used to stop someone from bleeding out and dying from a wound. Take 2 minutes to minister to the person. Roleplay accordingly. This action stops the target's bleed out counter. If first aid is successfully administered, at end of the bleed out counter (a total of 7 minutes with first aid), target wakes up as if they had only been knocked out.}
}

\NEW{Abil}{\aDominate}{
  \s\MYname	{Dominate Elemental}
  \s\MYtext	{I command you to do my bidding.}
  \s\MYeffect	{This ability allows you order an elemental of any faction as if they were enslaved to you. This action can only be used on one target at a time and cannot be resisted by elementals (it does nothing when used on humans). Refer to the \gEnslave{} greensheet for details.}
  \s\MYgreens	{}
}

%Abilities for elemental lords.

\NEW{Abil}{\aAirTeleport}{
  \s\MYname	{Howling Gale}
  \s\MYtext	{I vanish in a thunderous blast of air.}
  \s\MYeffect	{Once per hour, you may go Not Here for up to five minutes, and return to game in any area you could normally access. You may use Tempest immediately, if available, in response to any ability that would otherwise kill or incapacitate you.}
%Belongs to Mistral
}

\NEW{Abil}{\aFireWall}{
  \s\MYname	{Conflagration}
  \s\MYtext	{I become a roiling pillar of living flame, losing all semblance of human form. A scalding burst of explosive force erupts from me, knocking you unconscious.}
  \s\MYeffect	{Once per hour, you may knock unconscious all characters (including allied Elementals) within 4 Zones of Control in a massive pyroclasm. You may not selectively target this ability. Using this power exhausts even your considerable elemental might, and you must go Not Here for five minutes immediately afterwards. You return to game at the Lava Pool in the \pKitchen{}.}
%Belongs to Caldera (and Gehenna, if she appears).
%A way of dealing nonlethally with potential scary Good Guy Mobs?
%Mistral’s Tempest ability can be used in response to this.
%This is, I think, the most easily broken of the three. My worry is having Fire Queen tell her minions “I’m going to use this. Wait outside and kill all the unconscious people once I’m gone.” How to remedy? Suggestions?
}

\NEW{Abil}{\aHeatThings}{
  \s\MYname	{Heat}
  \s\MYtext	{I can use my body heat to warm things!}
  \s\MYeffect	{As a Fire elemental, your body temperature is still significantly above room temperature.  You can give your skin a little boost of power to warm it further.  Now you can heat things!}
%Belongs to all Fire elementals.
}

\NEW{Abil}{\aBecomeFiery}{
  \s\MYname	{Fiery Appearance}
  \s\MYtext	{Little tongues of flame are roiling all over my body!}
  \s\MYeffect	{When you feel a strong emotion, be it positive or negative, you lose control of your fiery essence, and little tongues of flame begin dancing all over your skin.  They won't hurt people around you...but they do look very intimidating.}
%Belongs to all Fire elementals.
}

\NEW{Abil}{\aPhysicalContact}{
  \s\MYname	{Touch}
  \s\MYtext	{I can have physical contact with those who are not Fire elementals.}
  \s\MYeffect	{Sure, you have a fiery nature, but it's all about mind over matter, isn't it?  If you focus, you can control your emotions and body temperature enough to have physical contact with people who are not Fire elementals.}
%Belongs to all Fire elementals.
%Especially important to Juliet.
}


\NEW{Abil}{\aEarthTrap}{
  \s\MYname	{Granite Vault}
  \s\MYtext	{Massive shards of stone jut up through the floor and entomb you for 5 minutes.}
  \s\MYeffect	{Once per hour, you may automatically trap a single target within your Zone of Control in a tomb of rubble. For five minutes, they cannot move or interact with others in any way - they are essentially Not Here, but remain immobile.}
%Belongs to Shale
%Mistral’s Tempest ability can be used in response to this.
}

\NEW{Abil}{\aEarthSpeaker}{
  \s\MYname	{Living Earth}
  \s\MYtext	{I can communicate with lifeless stone and metal.}
  \s\MYeffect	{You may open any item packet made solely of stone without meeting the normal conditions for doing so. Observers see the stone literally flow to obey your requests.}
%Belongs to all Earth elementals.
%Works on Malachite (to extract ore) and Stones from the riverbed (to open the geodes).
}


\NEW{Abil}{\aGlowInDark}{
  \s\MYname     {Glow in the Dark}
  \s\MYtext     {I glow with a bright white light}
  \s\MYeffect   {You may glow brightly at will.  This will illuminate darkened rooms and is also obvious to anyone in the area.}
}

\NEW{Abil}{\aWaterSneaky}{
  \s\MYname	{Hydroform}
  \s\MYtext	{I can merge my form with a sufficiently large body of water to hide.}
  \s\MYeffect	{Whenever you're out of combat, you may go Not Here in any room with a substantial amount of water in it. You may also enter Hydroform in a room without a body of water, becoming a puddle on the floor (place the "Puddle" item in the room while you're Not Here and retrieve it once you return). You may continue to observe and listen to anything that occurs while you're in Hydroform as if you were still in game. You may not leave the room while in Hydroform, unless your puddle is moved, in which case you must follow it. Any observers present when you enter or leave Hydroform notice you changing form. You may not stay in Hydroform for more than fifteen minutes at a time, and you may not reenter it for five minutes afterward.}
%Belongs to Tide
}

\NEW{Abil}{\aPickLocks}{
  \s\MYname	{Lock Picking}
  \s\MYtext	{I can pick locks}
  \s\MYeffect	{You can freely pass any locked door. Anyone accompanying you may also pass freely.}
%Belongs to Tide
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


