 %%%%
%%
%% This file sets up the Sign and Label datatypes and creates Sign and
%% Label macros.
%%
%% Signs generally represent interesting parts of game area, usually
%% as things posted on walls.  Labels represent other things, often on
%% or inside envelopes, that are part of complex mechanics.
%%
%% The default value for \MYloc will inherit location from the Place
%% or Sign most immediately up the ownership tree.  Override this by
%% setting \MYloc to anything (even blank).
%%
%% Sign is for full-sized signs that would cover most of a large
%% manila envelope; SignMedium is for signs sized to half-sized manila
%% envelopes; SignSmall is for signs sized for small manila envelopes
%% (the same size as item cards).  Label, LabelMedium, and LabelSmall
%% are analagous, but they don't have a \takedownby note at the
%% bottom.  You can always use a sign or label without an envelope or
%% with a differently-sized envelope.  Choose which based on
%% visibility and content.
%%
%% SignTiny is for signs you want to be hard to find; it is small and
%% does not have a \takedownby note.  SignDot is for a very small
%% "dot" which only has a title.
%%
%% SignStrip produces a strip of paper (without a \takedownby note)
%% with labels on the outside that show on both sides if you fold it
%% in half.  These are a convenient alternative to sub-envelopes. They
%% can also be used for "s-packets" taped to walls (see
%% Extras/README-s-packets).
%%
%% LabelCover produces a label similar to the cover to a research
%% notebook.  LabelPage, likewise, produces a page.
%%
%% EOG is for full-sized end-of-game signs.
%%
%%%%%

\DECLARESUBTYPE{Sign}{Element}
\PRESETS{Sign}{
  \FD\MYloc	{\mylocation} %% real-space location
  \FD\MYtext	{} %% text of sign
  }
\POSTSETS{Sign}{
  \edef\mylocation{\MYloc}
  \protected@edef\@ownerstring{%
    \MYname%
    \ifx\mylocation\empty\else\ (\mylocation)\fi%
    }
  }
\def\mylocation{}

\def\loc#1{\rs\MYloc{#1}}

\DECLARESUBTYPE{SignMedium}{Sign}
\DECLARESUBTYPE{SignSmall}{Sign}
\DECLARESUBTYPE{SignTiny}{Sign}
\DECLARESUBTYPE{SignDot}{Sign}
\PRESETS{SignDot}{\s\MYtext{}}

\DECLARESUBTYPE{Label}{Sign}
\PRESETS{Label}{\s\MYloc{}}
\DECLARESUBTYPE{LabelMedium}{Label}
\DECLARESUBTYPE{LabelSmall}{Label}

\DECLARESUBTYPE{SignStrip}{Sign}
\DECLARESUBTYPE{LabelCover}{Label}
\DECLARESUBTYPE{LabelPage}{Label}

\DECLARESUBTYPE{EOG}{Sign}
\PRESETS{EOG}{%
  \s\MYname	{End Of Game}
  \s\MYtext	{{\bf\Huge You may not pass through here.}}
  }


%%%%%
%% \signbig[<location>]{<name>}{<text>}
%% \eog[<location>]
%%
%% \signmdeium[<location>]{<name>}{<text>}
%% \signsmall[<location>]{<name>}{<text>}
%% \signtiny[<location>]{<name>}{<text>}
%% \signdot[<location>]{<name>}
%%
%% \labelbig{<name>}{<text>}
%% \labelmedium{<name>}{<text>}
%% \labelsmall{<name>}{<text>}
%%
%% \signstrip[<location>]{<name>}{<text>}
%% \labelcover{<name>}{<text>}
%% \labelpage{<name>}{<text>}
\newinstance{Sign}{\signbig[3][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}\s\MYtext{#3}}
\newinstance{EOG}{\eog[1][\mylocation]}{\s\MYloc{#1}}

\newinstance{SignMedium}{\signmedium[3][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}\s\MYtext{#3}}
\newinstance{SignSmall}{\signsmall[3][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}\s\MYtext{#3}}
\newinstance{SignTiny}{\signtiny[3][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}\s\MYtext{#3}}
\newinstance{SignDot}{\signdot[2][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}}

\newinstance{Label}{\labelbig[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{LabelMedium}{\labelmedium[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{LabelSmall}{\labelsmall[2]}{
  \s\MYname{#1}\s\MYtext{#2}}

\newinstance{SignStrip}{\signstrip[3][\mylocation]}{
  \s\MYloc{#1}\s\MYname{#2}\s\MYtext{#3}}
\newinstance{LabelCover}{\labelcover[2]}{
  \s\MYname{#1}\s\MYtext{#2}}
\newinstance{LabelPage}{\labelpage[2]}{
  \s\MYname{#1}\s\MYtext{#2}}


%%%%%
%% \sEOG{}
%% use \sEOg[\loc{<location>}]{} for EOG sign at a specific place
\NEW{EOG}{\sEOG}{
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NEW{Sign}{\sTest}{
  \s\MYname	{A Room}
  \s\MYloc	{10-250}
  \s\MYtext	{A lecture hall with large, sliding blackboards.}
  }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% The hotel rooms
\NEW{Sign}{\sHotelRooms}{
  \s\MYname	{Hotel Room Access}
  \s\MYloc	{- 004}
  \s\MYtext	{There are three ways to gain entrance to a hotel room:

{\bf 1. } Possess the appropriate room key.

{\bf 2. } You may hit the door with a {\bf CR of 5} or greater.

{\bf 3. } Hack your way in. The lock has a difficulty level of {\bf 1} unless the room belongs to \cScientist{\MYname{}}, in which case the lock has a difficulty level of {\bf 2}.

Once you have completed one of the above requirements, you may stand with your hand on the room sign for 30 seconds to enter the room. You may then freely stash items that are stashable, and take items that are in the room.}
  }

\NEW{Sign}{\sBrideRoom}{
  \s\MYname	{A Hotel Room}
  \s\MYloc	{- 004}
  \s\MYtext	{The nameplaque says {\bf \cBride{\MYname{}}}. 
  
  
  If you have the room key with item {\bf \# 100}, you may enter the room.}
  \s\MYitems {\iBible{}}
  }
  
\NEW{Sign}{\sGroomRoom}{
  \s\MYname	{A Hotel Room}
  \s\MYloc	{- 004}
  \s\MYtext	{The name plaque says {\bf \cGroomA{\MYname{}}}. 
  
  If you have the room key with item {\bf \# 101}, you may enter the room.}
  \s\MYitems {\iBible{}\imac{}\iDogtags{}}
  } 
  
\NEW{Sign}{\sScientistRoom}{
  \s\MYname	{A Hotel Room}
  \s\MYloc	{- 004}
  \s\MYtext	{The name plaque says {\bf \cScientist{\MYname{}}}. Below it is another name plaque that says {\bf \cKid{\MYname{}}}. 
  
  If you have the room key with item {\bf \# 102 or 103}, you may enter the room.}
  \s\MYitems {\iBible{}\iBall{}\iPaper{}}
  }
  
\NEW{Sign}{\sRivalRoom}{
  \s\MYname	{A Hotel Room}
  \s\MYloc	{- 004}
  \s\MYtext	{The name plaque says {\bf \cRival{\MYname{}}}.  
  
  If you have the room key with item {\bf \# 104}, you may enter the room.}
  \s\MYitems {\iBible{}\iWidget{}}
  }
  
\NEW{Sign}{\sPastorRoom}{
  \s\MYname	{A Hotel Room}
  \s\MYloc	{- 004}
  \s\MYtext	{The name plaque says {\bf \cPastor{\MYname{}}}.  
  
  If you have the room key with item {\bf \# 105}, you may enter the room.
  }
  \s\MYitems {\iBible{}\isyringe{}}
  }
  
\NEW{SignTiny}{\sI}{
  \s\MYname	{I}
  \s\MYloc	{- 004}
  }
  
\NEW{Sign}{\sActiveRoom}{
  \s\MYname	{A Hotel Room}
  \s\MYloc	{- 004}
  \s\MYtext	{The name plaque says {\bf \cActive{\MYname{}}}.  
  
  If you have the room key with item {\bf \# 106}, you may enter the room.}
  \s\MYitems {\iBible{}}
  }
  
\NEW{Sign}{\sLiTempeh}{
  \s\MYname	{A Hotel Room}
  \s\MYloc	{- 004}
  \s\MYtext	{The name plaque says {\bf Nava}.  
  
  If you have the room key with item {\bf \# 107}, you may enter the room.}
  \s\MYitems {\iBible{}\multi{5}{\iDrug{}}}
  }
 
%% The Kitchen
\NEW{Sign}{\sMortarAndPestle}{
  \s\MYname	{A Mortar and Pestle}
  \s\MYloc	{- 002}
  \s\MYtext	{A Mortar and Pestle are lying on the counter.}  
  \s\MYitems {\iPoisonedWine{}}
  }
  
\NEW{SignTiny}{\sR}{
  \s\MYname	{R}
  \s\MYloc	{- 002}
  }
  
\NEW{Sign}{\sCookieJar}{
  \s\MYname	{A Big Cookie Jar}
  \s\MYloc	{- 002}
  \s\MYtext	{There is a cookie jar on the counter.
  
  If you would like a cookie, put both hands on this sign for 30 seconds. You may then take a cookie. The cookie jar is essentially infinite. If it is empty, tell a GM.}  
  \s\MYitems {\multi{10}{\iCookie{}}}
  }
  
\NEW{Sign}{\sRefrigerator}{
  \s\MYname	{Refrigerator}
  \s\MYloc	{- 002}
  \s\MYtext	{A big, industrial sized refrigerator. 
  
  If you would like to search the refrigerator, place both hands on this sign for 30 seconds. Note: The items available here are effectively infinate in quantity. If this envelope is ever empty, tell a GM.}
  \s\MYitems {\multi{5}{\iMagnet{}}} 
  }

\NEW{Sign}{\sKitchenSink}{
  \s\MYname	{The Kitchen Sink}
  \s\MYloc	{- 002}
  \s\MYtext	{A big, stainless steel sink. A good place to wash your hands. 
  
  If you would like to search the sink, place both hands on this sign for 30 seconds. Note: The items available here are effectively infinite in quantity. If this envelope is ever empty, tell a GM.}
  \s\MYitems {\multi{5}{\iSteelWool{}} \multi{5}{\iWashcloth{}}}
  }
  
\NEW{Sign}{\sKitchenCabinet}{
  \s\MYname	{A Kitchen Cabinet}
  \s\MYloc	{- 002}
  \s\MYtext	{Full of all kinds of useful cooking implements. 
  
  If you would like to search the cabinet, place both hands on this sign for 30 seconds. }
  \s\MYitems {\multi{3}{\iPastaStrainer{}} \multi{3}{\iKnife{}}\iMedicine{}} 
  }
  
%% The Bar

\NEW{Sign}{\sBarCounter}{
  \s\MYname	{The Bar}
  \s\MYloc	{- 002}
  \s\MYtext	{Normally there would be a bartender here, mixing drinks. 
  
  If you would like to search behind the counter, place both hands on this sign for 30 seconds. You may then take 1 item from the counter. The items here are essencially infinite in quantity. If the envelop is empty, tell a GM.
}
  \s\MYitems {\multi{20}{\iWine{}}\multi{10}{\iVial{}}\iPocketWatch{}} 
  }
  
\NEW{SignTiny}{\sT}{
  \s\MYname	{T}
  \s\MYloc	{- 002}
  }
  
\NEW{Sign}{\sTV}{
  \s\MYname	{An old-fashioned television}
  \s\MYloc	{- 002}
  \s\MYtext	{Oh, the TV is playing. Yet the switch seems to indicate that it’s turned off…? If you watch it for a moment, it’s clear that the same two ads are playing, over and over.

Buy Nibbles n’ Kits dog food! Buy Peach Laundry Detergent! Buy Nibbles n’ Kits dog food! Buy Peach Laundry Detergent! Buy Nibbles n’ Kits dog food! Buy Peach Laundry Detergent! Buy Nibbles n’ Kits dog food! Buy Peach Laundry Detergent! Buy Nibbles n’ Kits dog food! Buy Peach Laundry Detergent! Buy Nibbles n’ Kits dog food! Buy Peach Laundry Detergent!
  
 This television may be opened up if you spend one minute doing so. If so, remove an item below. }
  \s\MYitems {\iSolenoid{}}
  }
  %% THIS IS A GLITCH ITEM and it needs a star sticker

%%The construction site
\NEW{Sign}{\sToolbox}{
  \s\MYname	{A Toolbox}
  \s\MYloc	{Hall off of - 002}
  \s\MYtext	{A big metal toolbox.
  
  If you would like to search the toolbox, place a hand on this sign for 1 minute. You may then take 1 item of your choosing from the toolbox.}
  \s\MYitems {\multi{3}{\iSolderingIron{}}\iWidget{} }
  }
  
\NEW{Sign}{\sPileOfWood}{
  \s\MYname	{A Pile of Wood}
  \s\MYloc	{Hall off of - 002}
  \s\MYtext	{An assorted collection of wooden planks and boards. 
  
  If you would like to search the pile, place a hand on this sign for 1 minute. You may then take 1 item of your choosing from the pile.
}
  \s\MYitems {\multi{3}{\iTwoByFour{}}\multi{3}{\iRope{}}\iBinoculars{}}
  }
  
\NEW{SignTiny}{\sA}{
  \s\MYname	{A}
  \s\MYloc	{Hall off of - 002}
  }

\NEW{Sign}{\sWater}{
  \s\MYname	{A Block of Water}
  \s\MYloc	{Blocking hall off of - 002}
  \s\MYtext	{\bf{It is possible to squeeze past if you\'re careful.}

There appears to be a floating aquarium in the middle of this hallway, blocking most of the passage. But on closer inspection, this aquarium lacks glass. It is simply a cube of water, held in the shape of a cube by god-knows-what, with some very confused fishes swimming around haphazardly inside.

If you have a net-like device and make a CR 2 attack, you can catch a fish. Open the packet below.}
  \s\MYitems {\multi{4}{iFish{}} }
  }
%% THIS IS A GLITCH ITEM and it needs a star sticker
%% Also, accompany this with an outline in masking tape on the ground
  
%% The Lobby of the Hotel
\NEW{Sign}{\sReception}{
  \s\MYname	{The Reception desk}
  \s\MYloc	{Main Hallway}
  \s\MYtext	{Normally there would be someone staffing the desk.}
  }
  
\NEW{Sign}{\sPortrait}{
  \s\MYname	{A Portrait of a tastefully dressed gentleman \#444}
  \s\MYloc	{Main Hallway}
  \s\MYtext	{A beautiful rendering of the image of the God of Virtuism.}
  }

\NEW{Sign}{\sFlowers}{
  \s\MYname	{A Vase of Flowers}
  \s\MYloc	{Main Hallway}
  \s\MYtext	{What a lovely flower arrangement! These would look quite nice at the wedding. If you get close, you can hear a strange static noise coming from the vase. What could be making that sound? It’s grating.
  
  If you would like to take a flower, stand with both hands on the sign for 30 seconds then take a flower.
  }
  \s\MYitems {\multi{15}{\iFlowers{} }}
  }
  
  %% THIS IS A GLITCH ITEM and it needs a star sticker

%%REALITY
\NEW{Sign}{\sHallwayBlocked}{
  \s\MYname	{YOU MAY NOT PASS THIS SIGN UNLESS YOU KNOW OTHERWISE.
  
  If you know otherwise, you may pass into this room, but you {\bf MUST} interact with the sign on the table directly inside the door before taking any action in this room.}
  \s\MYloc	{-015}
  \s\MYtext	{\#9999}
  }

\NEW{Sign}{\sPossessABody}{
  \s\MYname	{How to Possess A Body}
  \s\MYloc	{-015}
  \s\MYtext	{Since you are normally just a simulation, you must posess a body in order to exist in the real world. Below are a set of three robot bodies you may posess. Pick up one of the index cards labeled ``Robot'' and carry it with you at all times while you are in reality.  If there are no notecards on the table, there are no bodies available and you must return to the simulation immediately.
  
  There is a time limit for how long you can stay in reality. You can stay for a maxium of \bf{5 minutes.} You may choose to leave before the time is up.
  
  Unless you know otherwise, you may not possess an alien body.
  
  If you wish to destroy one of the alien bodies, you may do so once you have posessed a body of your own. If you choose to do so, you must inform a GM before you begin. The action takes 5 minutes and is interruptable. Pick up the notecard and do nothing else for 5 minutes. If anyone asks what you are doing, explain that you are attempting to destroy the body.  If you succeed in killing the body, tear up one of the notecards marked ``Alien''.
  
  {\bf NOTE: All bodies have CR 0. This supercedes your CR.}}
  }

\NEW{Sign}{\sAlienShip}{
  \s\MYname	{Alien Ship}
  \s\MYloc	{-015}
  \s\MYtext	{There is an airlock here that leads to an alien ship docked alongside this one. If you wish to take the alien ship and leave this one you may do so, however doing so constitutes leaving the game and you will not be allowed to return.
  
  In order to take the alien ship, you must first gain access to it. 
  
  If you have the {\bf number combination}, you may simply lay hands on this sign for 3 minutes. Then take down this sign and inform a GM that you have left game. This is an interuptable action.
  
  If you do not have the {\bf number combination} you may hack into the lock. The lock has a difficulty level of 3.}
  }

\NEW{Sign}{\sReturnToSim}{
  \s\MYname	{How to return to simulation}
  \s\MYloc	{-015}
  \s\MYtext	{If at any time you wish to return to the simulation, simply replace the index card representing your body where you found it, set your badge to ``I'm not here'' and return to where you used the dream machine (deck of cards). Then set your badge back.}
  }

\NEW{Sign}{\sSimStateExplained}{
  \s\MYname	{The Simulation State Readout}
  \s\MYloc	{-015}
  \s\MYtext	{The signs below indicate the state of the simulation.  If either one does not read {\bf ``Broken''}, then the simulation has been altered from the broken state. If one of the signs reads otherwise, then the state of the simulation is such.
  
  If you would like to alter the state of the simulation, follow the instructions on one of the signs below.}
  }

\NEW{Sign}{\sBrokenSim}{
  \s\MYname	{Item {\bf \#126}}
  \s\MYloc	{-015}
  \s\MYtext	{The Simulation is {\bf Broken}
  
  The simulation has experienced a fatal error. At 11:00 pm, the simulation will be terminated. All data will be lost. REPEAT: All data will be lost.
  
  If you have item {\bf \#126}, and you place it in the blue square below (remove anything already in the blue square), replace this sign with the one under it. If the sign to the right does not indicate that the simulation is {\bf broken}, swap the signs so it does.}
  }

\NEW{Sign}{\sBrokenSimTwo}{
  \s\MYname	{Item {\bf \#148}}
  \s\MYloc	{-015}
  \s\MYtext	{The Simulation is {\bf Broken}
  
  The simulation has experienced a fatal error. At 11:00 pm, the simulation will be terminated. All data will be lost. REPEAT: All data will be lost.
  
  If you have item {\bf \#148}, and you place it in the blue square below (remove anything already in the blue square), replace this sign with the one under it. If the sign to the left does not indicate that the simulation is {\bf broken}, swap the signs so it does.}
  }
  
\NEW{Sign}{\sFixedSim}{
  \s\MYname	{The {\bf Save State} is present}
  \s\MYloc	{-015}
  \s\MYtext	{The fatal errors have been corrected. At 11:00 pm, the simuation will revert to the save state.  All anomolies will be removed.}
  }

\NEW{Sign}{\sUtopianSim}{
  \s\MYname	{The {\bf Utopia State} is present}
  \s\MYloc	{-015}
  \s\MYtext	{The simulation has been modified to reflect a utopian state. At 11:00 pm, the changes will take effect.}
  }       

\NEW{Sign}{\sConsole}{
  \s\MYname	{A free-standing console.}
  \s\MYloc	{-015}
  \s\MYtext	{This console is set a little away from the others. It doesn't appear to do anything special.}
  } 

%%The Gift Shop
\NEW{Sign}{\sGiftShop}{
  \s\MYname	{The Gift Shop}
  \s\MYloc	{-030}
  \s\MYtext	{This is the gift shop for the hotel. It is small and mostly full of cheap junk.}
  \s\MYitems {}
  }

\NEW{Sign}{\sGiftShopDisplay}{
  \s\MYname	{A Display in the Gift Shop}
  \s\MYloc	{-030}
  \s\MYtext	{There are many things on display. 
  
  If you would like to take one, place your hand on the sign for 1 minute, then you may take an item of your choice.}
  \s\MYitems {\iCrayons{}\iCrayons{}\iHairbrush{}\iHairbrush{}\multi{4}{\iShoePolish{}}\iTape{}\iTape{}}
  }
  
\NEW{Sign}{\sGiftShopStuffies}{
  \s\MYname	{A display of stuffed animals}
  \s\MYloc	{-030}
  \s\MYtext	{There are a whole host of stuffed animals on display here. 
  
  If you would like to search the pile of stuffed animals, place your hand on the sign for 1 minute, then you may take an item if one is available.}
  \s\MYitems {\iGiraffe{}\iDog{}\iCat{}\iBird{}\iDinosaur{}\iMonkey{}}%%A GM will put the item into the envelope when the utopia state appears in game
  }
  
\NEW{Sign}{\sGiftShopWindow}{
  \s\MYname	{A clothing display.}
  \s\MYloc	{-030}
  \s\MYtext	{This trendy boutique is selling some chic skirts and suits! Look, matching purses and wallets!

Wait a minute… what color is the fabric? It’s not one you’ve ever seen before. You’re not sure you can describe it.}
  \s\MYitems {\iClothes{}}
  }
 %% THIS IS A GLITCH ITEM and it needs a star sticker

  
%% The High Security Door
\NEW{Sign}{\sHighSecurityDoorLocked}{
  \s\MYname	{A High Security Door}
  \s\MYloc	{Near -013}
  \s\MYtext	{This steel door looks important. It has a keyhole instead of a card reader. 
  
  If you have item {\bf \# 125} you may open the door. Replace this sign with the one under it (put this sign under that one). You may then take any item from this room that you wish to take.}
  \s\MYitems {}
  }

\NEW{Sign}{\sHighSecurityDoorUnlocked}{
  \s\MYname	{A High Security Door}
  \s\MYloc	{Near -013}
  \s\MYtext	{This steel door looks important. It has been left open. You may close the door. 
  
  If you do so, replace this sign with the one under it (put this sign under that one).}
  \s\MYitems {\iMilitarySecret{}}
  }

%% Broom Closet
\NEW{Sign}{\sBroomCloset}{
  \s\MYname	{A Broom Closet full of junk}
  \s\MYloc	{-032}
  \s\MYtext	{This is a small broom closet. There seems to be a whole bunch of random items in here if you had the patience to find them.}
  \s\MYitems {}
  }
  
\NEW{Sign}{\sPileOfJunk}{
  \s\MYname	{A Pile of Junk}
  \s\MYloc	{-032}
  \s\MYtext	{There is a pile of junk here. 
  
  If you would like search the pile of junk for a useful item, spend 3 minutes searching this room. You may then take one item randomly.}
  \s\MYitems {\iWidget{}\multi{4}{\iwire{}}\iBible{}\multi{3}{\isyringe{}}\multi{3}{\iRope{}}}
  }
  
%% The ballroom
\NEW{Sign}{\sBallroom}{
  \s\MYname	{The Grand Ballroom}
  \s\MYloc	{-013}
  \s\MYtext	{This is the Grand Ballroom for the hotel. The floors are a rich, grainy red wood.  The walls are covered in gilded wallpaper and the sweeping, the vaulted ceilings are graced by elaborate chandeliers. 
  
  The wedding is scheduled to take place here this evening.
}
  \s\MYitems {\iCellphone{}}
  }

\NEW{SignTiny}{\sB}{
  \s\MYname	{B}
  \s\MYloc	{- 013}
  }
 
  %% Spa
\NEW{Sign}{\sSpa}{
  \s\MYname	{A Spa}
  \s\MYloc	{-032}
  \s\MYtext	{This was a fancy Spa, but something's wrong.
  
 Everything in this room seems to be sprouting leaves. Even the plastic and metal furniture is sprouting plastic and metal foliage.

For every 30 seconds spent within 2 ZoC of this sign, lower your $\Omega$ by 1.
}
  \s\MYitems {\iWidget{}}
  }
 %% THIS IS A GLITCH ITEM and it needs a star sticker


%%Windows for flavor text and to make it clear that there is nothing outside.

\NEW{Sign}{\sWindow}{
  \s\MYname	{A Window}
  \s\MYloc	{}
  \s\MYtext	{This window used to look out over the grounds of the hotel, but now when you look out, you see\ldots \emph{nothing}.  It's disconcerting because you don't see darkness, or light, or anything. There is just--nothing. The window won't budge, and you aren't sure you'd want to open it anyway.
  }
  \s\MYitems {}
  }