\documentclass[green]{elementals}
\begin{document}
\name{\gElementalEggs{}}

These tiny elementals you have found correspond to the infantile forms of powerful elementals. They are strong enough that, once grown up, they could significantly disrupt the balance of power in their faction's favor. Unfortunately, elementals age slowly and it will be over a decade before their power starts to manifest. In the meantime, you will have to look after them.

Young elementals require periodic attention to develop properly, especially in their current form when they are just starting to form an independent consciousness. Proper care involves the following steps:
\begin{enumerate}
  \item They must be kept constantly immersed in their element. This typically means keeping them on or near the body of an elemental of their type.
  \item To prevent the elementals from developing into weak, cowardly individuals, they must be toughened up. Their caretaker must physically tax them to encourage their growth. \emph{Bounce the physrep a few times}. This action must be taken at minimum every 10 minutes, but can be performed more frequently. The more often the action, the stronger the resulting elemental.
  \item Occasionally even elemental babies need to sleep. {\bf Once, 30 minutes after receiving the baby elementals, a caretaker must rock the baby elemental to sleep and sing a lullaby.} This action will take 30 seconds. Roleplay accordingly.
\end{enumerate}

Properly cared for, these elementals will prove a valuable asset. On the other hand, if the baby elementals go for too long without being in the presence of their element they may suffer greatly or even die of starvation.

Typically, elementals are very protective of their young and taking or attack them is comparable to attacking a human child.

\end{document}