\documentclass[green]{elementals}
\begin{document}
\name{\gEndGame{}}

%\emph{This sheet summarizes the various ``end of game'' scenarios.}

\section{Elementals get sent home}

If \cGD{\intro} successfully hooks up the electromagnet to a terminal opening, some of the elementals get sent home. How many depends on how many elemental essence \cGD{} used. One essence will only get those in game space, which will have similar effects to the ``an elemental leader dies'' scenario. Three essence gets a much larger radius including the earth king, but the water queen persists and forms an agreement of sorts with the humans (balance is managed because now there's only one serious faction left). Five or more essence sends all the elementals home (the number of essence needed may be adjusted depending on how things play out). The elementals who go back are reminded of their true place within the hierarchy, which (even for the leaders) is low indeed. The elementals born on Earth also learn what it means to be subjugated at the hand of the quintessence. The earth and quintessence elementals are content, but the other factions seethe.

\section{One or more of the elemental leaders die}

The loss of a leader is a serious problem. That elemental faction will rapidly implode and be crushed by the opposing faction. Regardless of alliances, a lot of strife will ensue as the competing faction (for example, water queen taking advantage of fire queen's death) proceeds to wipe out the leaderless faction. Many humans and elementals will die on all sides.

\section{Humanity sign a formal treaty with an elemental faction}

This depends on the treaty wording (and whether their respective leaders decide to betray the alliance). In general, the alliance is respected (especially with earth) and the other factions keep their distance from humanity, acknowledging their place in the hierarchy. Things are considerably more peaceful and humans become more of an observe to the ongoing conflict of the elementals. Sometimes humans are even invited to arbitrate elemental disputes, taking on some of the roles of the quintessence back on the elemental planes. The humans are likely better positioned to deal with any of the scenarios below.

\section{Elementals acquire a large source of Elementium}

If \cScientist{\intro} uses an ability on a terminal opening of the Conduit, a large quantity of Elementium will be brought over in the form of a blizzard of snowflakes that cover the area outside the Conduit. The humans collect this and build an ``Elementium repository'' nearby and dispense it to the elementals, who eventually become addicted to the substance and become diminished in power and aggression (Elementium is useless to elementals unless first processed by humans). For the most part, they retreat to their various domains and stop warring with each other or bothering humans. Small conflicts still persist, but communication between elementals and humans ultimately goes up considerably as humans and elementals find it much easier to get along and interact.

\section{Stasis, the elder quintessence elemental, is summoned}

Stasis alone is sufficient to maintain the balance between the elementals and provide Amaranth indefinitely (he is senior to the elemental leaders by two generations). Under his guidance, the elemental factions are brought to bear and are forced to leave humans alone or face the wrath of Stasis. Peace ensues but the elementals are severely diminished. Many faction leaders greatly resent what they percieve as their subjugation at the hands of Stasis.

\section{Gehenna, the elder fire elemental, is summoned}

Gehenna massively tips the balance of power in Fire's favor. She decides there is no point in maintaining the illusion of balance and kills \cKing{} and \cEarthKing{}, and forces \cWaterQueen{} into hiding deep within the ocean. Fire rampages across all the continents and Gehenna lets the humans live, but occasionally reminds them of her vast power by toasting a city or three. The temperature of the Earth rises and in the ensuing years, Gehenna focuses on boiling \cWaterQueen{} out. If \cScientist{} acquired Elementium, Gehenna still destroys the air and earth factions but is eventually forced to take Elementium and is somewhat pacified, resulting in a tense agreement with humans. If there is no source of Elementium, Gehenna rages for the next fifty years and things are \emph{bad}, but she eventually dies.

\section{Gehenna AND Stasis}

Assuming this is not resolved in-game, Gehenna flees far away but is eventually subjugated by Stasis, but not before Gehenna manages to kill both \cKing{} and \cEarthKing{}. Without their leaders, the earth and air faction eventually diminish to the point of extinction, while Stasis oversees a barely-stable standoff between fire (who has taken over the continents) and water (who never come on shore). Stasis does his best to preserve humans but it does not always go well for them.

\section{Stasis AND Elementium}

With both Stasis and Elementium available, all the elemental factions except for Earth choose to accept Elementium as a comparatively liberating alternative to control by Stasis. Stasis is upset at his lack of control but is convinced by \cAvatar{\intro} that the elementals can be peaceful without being directly enslaved.

\section{No Elementium, no Stasis}

Without a sufficient source of Elementium or Amaranth, the elementals will die out in 50 years. If there are some quintessence elementals left, like Vitality, they are enough to maintain only a handful of elementals each. The number of elementals reduces from thousands to only 5 or so of each faction, and even the great leaders are reduced to the power level of their children. Although the dying of the elementals is filled with dangerous moments, ultimately humanity weather's their demise. Afterwards, the leaders do survive (unless \textbf{all} the quintessence are dead), but elementals are reduced to an idle curiosity living on a large preserve. Some of the leaders beg to be returned to the elemental plane at the next large opening, while others plot in secret to bring more over.

\section{Human Enslavement Technology}

Led by \cMS{\intro}, humanity in secret mass-produces the technology to enslave elementals. The elementals who were aware of the technology underestimate human ingenuity and capacity to spread the technology and are taken by surprise when humanity starts taking hostage any elementals who cause any trouble on their territory, and the elementals are forced to negotiate for the return of their own kind. If \cLeader{\intro} is in power, all the elemental factions quickly realize that humans are now a terrifying force and agree to a global alliance, keeping to their own territory on pain of enslavement. If \cDema{\intro} is in power, then a surprise attack is launched once the technology is mass-produced, taking all the leaders except \cWaterQueen{}. Humanity asserts its authority and all the factions are brought to bear, with \cWaterQueen{} wisely agreeing to retreat to the ocean depths rather than escalate a conflict she is not likely to win. Enslavement technology also greatly protects humans if the elementals die out for lack of Amaranth/Elementium, and even Gehenna can be subjugated.

\section{Coup d'Etat}

If \cDema{\intro} takes power, \cDema{\they} convinces humanity to become dramatically more militant. Impressive anti-elemental technology is developed and a strong territorial divide is established. if \cMS{\intro} is still alive, enslavement tech is developed, as above. \cDema{} either waits for the elementals to die out, tries to enslave them, or assassinate their leaders.

\end{document}
