\documentclass[green]{elementals}
\begin{document}
\name{\gSealingLocations{}}

In the name of maintaining your advantage on this plane you intend to prevent anyone from opening the Conduit tonight.  To do this, you will have to seal the possible conduit locations. This also leads to your ultimate goal of sealing the conduit permenantly. To seal the conduits, you will need to draw a Rune of Sealing across the location in a mixture of human blood and elemental ``blood''.

To seal a conduit location:
\begin{enumerate}
  \item Acquire a vial of human blood. To do this use your ``\aDrawBlood{}'' ability.
  \item Acquire a vial of elemental ``blood'' from any elemental faction (you \emph{may} acquire the blood from yourself). To do this use your ``\aDrawBlood{}'' ability.
  \item Empty the contents of both vials over the location you wish to seal (tear up the item cards)
  \item Spend 2 minutes mixing the blood and essence and shaping the rune of sealing. If anyone asks you what you are doing (ie: ``What do I see?''), explain to them that they see you spreading a dark, sticky substance over this location.
  \item Place a ``\wSealedConduit{}'' whitesheet over the conduit location to indicate that it has been sealed.
  \item Wash your hands at the kitchen sink or in the pond. (spend 30 seconds with both hands on the sign). Until you do so, your hands are covered in a dark, sticky substance that smells strongly. You must hold your hands out in front of yourself (you wouldn't want to get this stuff on you!) and explain to anyone who asks what they see.
\end{enumerate}

Unfortunately, this seal is not permanent until it sets and the mixture will not set for several days. Until then, someone could wash your seal off. You will have to keep an eye on it.

{\large \emph{If 8 possible locations are sealed at the end of game, the Conduit will be sealed permanently and can never be opened again.}}
\end{document}
