\documentclass[green]{elementals}
\begin{document}
\name{\gTreaty{}}

Formalizing a human/elemental treaty is a big step toward eventual peace between humans and elementals. Like all such political documents, there is a formal process for formalizing a treaty.

If you would like to formalize a treaty between humans and an elemental faction, you must follow these steps:
\begin{enumerate}
  \item Obtain verbal confirmation from the current leader of the humans, and the current leader of the elemental faction in question that they agree to a treaty.
  \item Compose an introductory paragraph expressing your desires for the treaty.
  \item Obtain a \emph{written} paragraph from the leader of the humans enumerating the commitments that humans offer. (If necessary, transfer it to the same page with your introduction)
  \item Obtain a \emph{written} paragraph from the leader of the elemental faction enumerating the commitments that the elementals offer. (If necessary, transfer it to the same page with your introduction)
  \item Once both leaders agree to the terms of the treaty, have both leaders sign the treaty.
  \item Obtain the signatures of yourself and 1 other witness. (There should be 4 signatures on the treaty at this point.)
  \item Make a public announcement of the treaty by telling at least 2 other people.
\end{enumerate}

Once the treaty has been signed, you expect both parties to abide by the terms. Make sure everyone understands this before they sign.

\end{document}
%%Machine has 1 number and instructions
%%Each conduit location has 2 pages. covered page has list of numbers that are active at different times
%%Check for prime(?) factors