\documentclass[green]{guildcamp1}
\begin{document}
\name{\gPrepareWedding{}}

As a practitioner of Virtuism, with a role to play in this most sacred ceremony, you have explicit knowledge of how to prepare for the wedding ceremony. The ceremony requires actions on the part of the {\bf bride}, the {\bf groom}, the {\bf pastor}, and one {\bf witness}. You are highly encouraged to recruit as many witnesses as possible for the ceremony, although only one is necessary.

{\bf Keep in mind that Virtuism does not allow weddings to occur after dark.} Sundown is at 11:00 pm tonight.

{\bf Before preparations for the ceremony can begin, everyone interested in participating, including witnesses, should attend a prayer circle 3.5 hours before dark (7:30 pm)} (which translates to 30 minutes after game start). {\bf A prayer circle is simply everyone joining hands for 30 seconds.} Additional witnesses may be added later, assuming the fulfill the {\bf witness} requirements below, but at least one witness must be present at the prayer circle.

If you wish to fulfill the conditions of being the {\bf Bride} or the {\bf Groom} you must complete the following tasks, in any order you choose:
\begin{itemize}
  \item Collect a {\bf flower}. Make sure to bring it to the ceremony!
  \item Spend 3 minutes in conversation with someone about the ceremony. {\it Role play accordingly.}
  \item Spend 5 minutes alone in contemplation of your vows. {\it Simply choose not to interact with anything or anyone since you are contemplating your vows. You may do this anywhere, as long as no one is within 2 ZoC. If someone enters this range you may warn the person and if they immediately retreat, you may continue. Otherwise, you must start over.}
  \item Spend 2 minutes in your {\bf room}, getting ready. {\it Stand with both hands on the sign for your room for your room for 2 minutes while in posession of your room key.}
  \item If you are the {\bf Bride}, get somebody to brush your hair while in the spa. You must acquire a hairbrush to do so. You and your helper must both place a hand on the {\em Spa} sign for 1 minute (you must both do this at the same time).
  \item If you are the {\bf Groom}, get somebody to shine your shoes in the spa. You must acquire shoe polish to do so. You and your helper must both place a hand on the {\em Spa} sign for 1 minute (you must both do this at the same time). Performing this action consumes the shoe polish.
  \item If you are the groom, obtain the lapel pin from the Pastor.
  \item Practice dancing with the bride or groom for at least 5 minutes. {\it Role play accordingly.}
\end{itemize}

If you wish to fulfill the conditions of being the {\bf Pastor} you must complete the following tasks, in any order you choose:
\begin{itemize}
  \item Collect a {\bf flower}. Make sure to bring it to the ceremony!
  \item Spend 2 minutes in conversation with one non-believer, explaining the importance of the wedding ceremony.
  \item Bring enough {\bf glasses} of wine (3 plus any witnesses. Don\'t hesitate to bring extras) from the {\bf Bar} to the {\bf Ballroom}. {\it Glasses have a bulkiness of 1 hand. You may therefore carry up to 2 at a time, if you are carrying nothing else. Since they are fragile, \bf{ you cannot run} whenever you are carrying at least one wine glass. Don\'t spill!
  \item Spend 3 minutes preparing your speech which you will deliver at the beginning of the ceremony.
  \item Speak with the bride and the groom and make sure they are ready to marry and have no lingering doubts, concerns, or anything in their past that might prevent them from being married under the tennants of virtuism.
  \item Give the lapel pin to the Groom.
\end{itemize}

If you wish to fulfill the conditions of being a {\bf Witness} you must complete the following task {\it (note: non-believers can act as witnesses if they have spoken to the pastor):}
\begin{itemize}
  \item Collect a {\bf flower}. Make sure to bring it to the ceremony!
\end{itemize}

\end{document}