\documentclass[char]{elementals}
\begin{document}
\name{\cKing{}}

You pause, floating on thermal above the human dwelling. Such a pitiful little thing, and yet so very important. One hundred years ago - barely a breath of time for you - you were pulled onto this plane in that very house. And what a plane it is. The air is sweet, and smells of freedom. You took to the skies, spun minions off as eddying swirls, and spread your dominance throughout the atmosphere.  Life was grand. In this realm without Quintessence to maintain \emph{balance}, there is even a chance that you could become exclusive ruler of this plane.

You take a moment to reminisce about the elemental plane. Back home you were but a mid-level elemental, bound within the hierarchy, and ultimately subverted by the Quintessence. Here, you are the King of the air elementals, \cKing{\intro}. You are free from all of that, free to be in charge, with your own minions to do \emph{your} bidding. You would like for things to stay this way. There is really only one thing that would upset the situation--and that is the opening of the conduit.

The conduit is the point of closest association between the elemental and this human plane of existence. Those hundred years ago, a foolish human made the fortuitous mistake of opening the conduit and freeing you. It was certainly not \cGrandfather{\their} intention, given that \cGrandfather{\they} tried to force you into a human shell. The fundamental particles of that shell were almost instantly scattered to the wind once you were fully on this plane. Nothing so puny could contain your power. The house  followed soon after. A pity that \cGrandfather{} managed to bring over the other three elements first. How grand it would be if this world were as free of earth, water and fire as it is of Quintessence.

Despite the  light-headed feelings of joy you get from being on this plane, you are no fool. It did not escape your understanding that if the conduit had been opened once, it could be opened again. This was not something you could risk happening. There was no way you would allow the Quintessence here. You sent your agents to spy on the conduit, and report to you any elemental dealings. To your relief, there has been only the petty actions of humans, rebuilding the human dwelling and so forth. Nothing to concern yourself with.

Except... there was this one in incident, about 10 years ago, in which a number of earth elementals gathered near the conduit, along with some human. Your minions were foolish however, and stayed to try to discern what was going on, instead of reporting it to you immediately. By the time you were made aware, and arrived on the scene, they were long gone. Although you could not determine exactly  what they had tried to do, to your great relief it was clear they had failed at it. There was no sign of the conduit having been wedged open, or of any elemental passing through. Although nothing had come of it, you renewed your vow to be vigilant.

One day you looked down upon the earth with the mild curiosity of boredom. Moving pointlessly across the ground where puny things that walked on two legs - humans. As you watched, only half seeing, you considered your position on this plane. If only you could find some way to gain the upper hand against the other elements. And then it came to you. What was the one thing on this plane that wasn't on the elemental plane? Those puny humans. Whatever else they were, they had survived 100 years of careless elementals. You began to watch with more interest. It seems to you that humans seem to have mastered earth and water, at least in the iterations that exist normally in on this plane.  So you hatched a plan to have humans help you master the earth and water elementals. You sent one of your trusted minions, \cNaturalist{\intro} to learn about and come to understand  humans.

\cNaturalist{} quickly made substantial in-roads with the humans, and insisted to you that they would indeed be very useful. You were not convinced until one of them mentioned \cGD{} and her research on elements. In a flash, you had the first piece of your puzzle. You made your way to the conduit, and the house of \cGD{} and enslaved her. The process took longer than you had expected - all of several hours - but it was worth it. The \cGD{\kid} managed to trap a small water elemental, and exploit technology that even you could not comprehend in it's entirety, to remove the very essence of the water elemental. \cNaturalist{\MYname{}} expressed some dismay at your treatment of the water elemental. After all, the empty shell that was left could hardly be called an elemental any more, but \cNaturalist{\they} conceded that the price was minimal compared to the reward.

You bent your will on the water essence, and after months of careful work, had a potent poison. Confident that it would never be traced back to you, you arranged to have fed to the King of the Earth elementals. His powers soon began to wane, and the once proud earth elementals were thrown into disarray and squabbling. It seems that your moment has come at last. Humans had unknowingly lent you the edge you had so desperately sought against the other elementals. And now, rumors of other kinds of potent technology have reached you.

In order to protect your advantage, you have recently been speaking out against violence towards humans, and making ceremonial gestures towards peace with the humans. You have even gone so far as to invite them to the Elemental council tonight. Although that was really \cNaturalist{} persuading you. You aren't convinced it is such a good idea for humans to be this close to the conduit. Appearances must be maintained though. And humans are trusting. They would never speak a word against their great protector.

Except just this morning \cNaturalist{} came to you with a disturbing confession. \cNaturalist{They} admitted that the fiery plane crash of a human plane which \cLeader{} has been whining to you about, was \cNaturalist{\their} fault. You had been so confident that it was 

%%loosing power, must find white. Do anything to maintain power, don't know how to fix it. Need long term survival.
%%can't upset balance

\begin{itemz}[Goals]
	\item  Prevent the conduit from opening at all tonight.
	\item  Perma-seal the gate. 
	\item  Maintain good relations with the humans but avoid signing a treaty unless they can prove their usefulness.
	\item  Prevent the Earth King from being healed.
	\item  Blame fire for the airplane crash.
\end{itemz}

\begin{contacts}
	\contact{\cLeader{}}
	
\end{contacts} 

\end{document}
