\documentclass[char]{guildcamp1}
\begin{document}

\name{\cBride{}}
\bigquote{``Her power has been made to derive from her sexuality. It has always been preferable to attribute a woman's success to her beauty rather than to her brains, to reduce her to the sum of her sex life.''}{--Stacy Schiff}

You look out of the window in your hotel room, only to find{\ldots} Nothing. There is nothing there. No sky, no clouds, no beautifully manicured garden. Not even the other tower of the Hotel Virtuoso. You stare for a heartbeat, then dive for your Testament. Flipping frantically through the pages, you find {\em The Prophesy}. Your heart beats faster and faster as you read the familiar words again. There is no mistaking that the time talked about in the prophesy is now. You try to catch your breath as you spin around and stare at the wedding dress hanging in your closet. It's you. You are the one talked about in the prophesy. Destined to save the world.

A bitter laughter wells up inside you. How could you be destined to save the world? You don't feel like anything special; your father made sure of that when he left you and your mother. You were just eight years old when he absconded with your mother's fortune. Your mother was heartbroken, and had taken to shooting Anaphmonine to dull the pain. She died from an overdose when you were just 14. You never forgave her, and bitterly resent anyone who does drugs of any kind, but particularly `Bite' (the street name for Anaphmonine).

You snap out of your painful reminiscing. You are not a sob story. You are strong. Independent. Beautiful. Oh yes, you are so beautiful. After your mother abandoned you, just like your father before her, you turned to Virtuism for comfort. What you found there brought you great clarity. You embraced the tenets wholeheartedly, particularly the ones about being self reliant and true to yourself.

In college you met \cRival{}, with whom you became fast friends. \cRival{\They} was a nice \cRival{\kid}, though not very religious. \cRival{\They} didn't seem to understand Virtuism the way you did. It explained so much of the world to you. \cRival{\Them} refusal to follow Virtuism closely led \cRival{} astray a couple of times and you had to rescue \cRival{\them}. In particular, \cRival{\they} got \cRival{\themself} mixed up with a \cRivalEx{\kid} who eschewed Virtuism in all it's manifestations. \cRivalEx{\They} made your friend miserable. When \cRivalEx{\they} started hitting on you as well, you saw a golden opportunity to teach \cRivalEx{\them} a lesson. A few dates and a dramatic break-up in front of half of the sophomore class left \cRivalEx{\their} world shattered, and you drunk with power.

After that, it was like a drug. Leading men on, taking whatever you could from them, and leaving them broken--it was fun. Your conscience never bothered you. The men you targeted deserved to be exploited. They didn't practice Virtuism, or they were hypocrites about it. They lied, stole, cheated-everything your father had done. You ruined reputations, extorted money, and climbed the social ladder yourself. Through it all, you justified it as staying true to yourself. You really were a wealthy girl. You just lacked a fortune at the moment.  

You of course donated some small portion of your money to the church, which quickly gained you power and connections within Virtuism as well. It was not until a few years later that you met \cPastor{}, one of the most prominent pastors of Virtuism. \cPastor{\They} even wrote your favorite edition of the Tennants of Virtuism, a modern commentary on the {\it Testament of Virtuism}. \cPastor{\They} have always been at the forefront of religious theory, and you have always admired \cPastor{\them}. \cPastor{\them} ability to resist your feminine charms, which you tried just for the hell of it, only increased your esteem for \cPastor{}. 

After college, you stayed in touch with \cRival{} as \cRival{\they} quickly rose to prominence in the sciences. It made you sad to see your friend falling away from Virtuism. Whispers began to reach you that \cRival{} might be employing rather unsavory methods to succeed so quickly. You hired some outside help to set up a camera in your friend's apartment. You couldn't believe what you found when you reviewed the tapes. There was \cRival{} was on tape hacking into Journal of the National Academy of Science website and rigging it so their paper would be published as the headline story, and slating someone named \cScientist{}'s article for rejection. When you confronted \cRival{\them} about it, \cRival{\they} tried to brush it off. When you made it clear that you had proof, \cRival{} became distressed and begged you to keep it quiet.  What else could you do? You agreed to keep what you had found to yourself for the time being. You have since thought it over however, and are not so sure you are willing to keep \cRival{}'s secret any more.

Up to now, you have lived the life of a rising star. You were the queen bee in a busy hive of social networking. But one night, one of your lovers went too far. \cGroomA{} proposed to you. \cGroomA{\They} was nice enough, though rather older than you. Spending time with \cGroomA{\them} was oh so boring, but \cGroomA{\they} was oh so wealthy. At least \cGroomA{\they} was  a practicer of Virtuism so you always had something to talk about. You thought his proposal over, and were about to say no, when \cGroomA{\they} produced a gorgeous, and very expensive, ruby wedding ring. You couldn't resist the temptation of money, and said ``yes''.

And now, here you are. Just a month later, about to get married. But you aren't about to give up the lifestyle you have worked so hard to earn back your whole life. The freedom, the money, the power. No, you intend to poison your \cGroomA{\spouse} during the wedding ceremony, and inherit all of \cGroomA{\their} money. Then you can return to your life of freedom and glamour.  The only piece you are missing is \cGroomA{\their} bank account number. 

The fact that the world seems to be ending is not such a big deal. {\em The Prophesy} explains that a wedding ceremony will save the world, and a wedding is exactly what you are determined to see happens tonight.

\begin{itemz}[Goals]
  \item Ensure that the wedding ceremony occurs at all costs.
  \item Persuade your husband to give up his bank account number to you.
  \item Poison your husband, preferably during the wedding ceremony.
  \item Get a hold of \cRival{}'s stocks, possibly in exchange for your continued silence.
  \item Find your next lover/victim.
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cGroomA{}} Your very wealthy husband to be. 
  \contact{\cRival{}} Your old college friend, now a prominant scientist.
  \contact{\cPastor{}} The pastor who will be performing your wedding. You respect him highly.
  \end{contacts}


\end{document}

