\documentclass[char]{elementals}
\begin{document}
\name{\cJuliet{}}

You are \cJuliet{\intro}, a low-ranking Fire elemental here to serve your Queen.

You are also in love.  That's what it has to be, for you to take such risks to see \cRomeo{\intro} as often as you can.  After all, \cRomeo{\they} is a human soldier (bodyguard to the human President, no less!), and you're the Fire elemental sent to spy on the humans.  If any of your fellow elementals found out that you're in a \emph{relationship} with a \emph{human}...well, you'd rather not think about what would happen.  At best, an unbreakable command from Queen \cQueen{\intro} never to see \cRomeo{} again.  At worst, \cRomeo{\they} would be incinerated for daring to think \cRomeo{\themself} worthy of an elemental's love.  Not being very high up in the Fire hierarchy, you'd be powerless to prevent the execution.  Actually, the only reason you are provisionally a second tier elemental is that the Queen needed an agent to observe the humans and find out just what military technology they have been developing, and your brother \cPyro{\intro} recommended you.  What an honor it was, how happy you were, meeting the Queen and receiving this temporary promotion!  You swore to \cQueen{\them} and to \cPyro{} that you would not let them down, and at first everything seemed to go well.

To have an excuse to meet humans, you began acting as an intermediary between Queen \cQueen{} and the King of the Air elementals, \cKing{\intro}, who of the four elemental factions has the closest ties to humans.  In this diplomatic capacity, you were introduced to President \cLeader{\intro}, leader of the remaining humans, who seems rather desperate to form some peace treaty, \emph{any} peace treaty, with any elemental faction to keep \cLeader{\their} people alive.  Queen \cQueen{} isn't particuarly interested in a permanent alliance with humans, especially since \cQueen{\they} is secretly planning to open the Conduit and bring over more Fire elementals from the elemental plane, but it's useful to dangle the possibility of a treaty in front of \cLeader{}.  

In the beginning, you thought that humans were such simple, boring creatures.  Flatter them a little, slip them a tiny nugget of useless information about elementals, imply that you trust them and would prefer to deal with \emph{them} alone, and all of a sudden they thought you were their best elemental buddy who would keep the other marauding elementals from squashing or incinerating them.  Where was the fun in manipulating such gullible fools?

But the more you associated with humans, the more you realized that they were actually wily creatures, no less deceitful and scheming than any elemental.  They all had different personalities, once you got to know them.  After a while, they even started to look different from one another!  President \cLeader{}, far from the political naif you originally thought \cLeader{\them}, is certainly a worthy opponent.  Every time you try to find out what types of military technology the humans are developing and whether any of it is directed against elementals, \cLeader{\they} drops vague hints about \cLeader{\their} scientists conducting critical research and being on the verge of breakthroughs that would benefit humans and elementals alike.  \cLeader{\They}'d be \emph{happy} to share the results with \cLeader{\their} friends, of course.  And then \cLeader{\they}'d start expounding on the benefits of a human-elemental alliance.

Of course, you expanded your circle of human contacts to see if you could pry information out of someone else.  And that was when you became acquainted with \cRomeo{}.  As \cLeader{}'s head of security, \cRomeo{\they} presented a logical target since \cRomeo{\they} has access to the President's rooms and documents.  By this time, you knew enough about human society to understand the Cit/Azi distinction.  It is clear that \cRomeo{\they} was programmed to protect \cLeader{}'s interests and that \cRomeo{\they} also shares \cRomeo{\their} Supervisor's commitment to preserving the human race.  Given this incorruptibility, the usual appeals to greed or ambition wouldn't work, so you decided to befriend \cRomeo{\them} instead...and that's when things went wrong, because to your utter shock you found yourself falling love with \cRomeo{\them}.  The two of you have even been discussing marriage recently!  

Now you find yourself caught between your love and your duty.  \cRomeo{} would be furious if \cRomeo{\they} knew about \cQueen{}'s plan to bring over more Fire elementals (especially since the ones here already aren't always careful about what they burn), but you happen to support that plan. You genuinely believe that there is too much chaos in this world, and that if only Fire could be allowed to rule, it could impose the proper hierarchy and bring peace.  And yet, if your Queen succeeds in opening the Conduit and summoning an army of Fire elementals, if all-out warfare ensues between the elemental factions and the humans get caught in the middle and decimated, \cRomeo{} will be \emph{furious} at you.  You know that his programming forbids him to condone such loss of human life, and he will have no choice but to break up with you.  That would be absolutely devastating.  You don't even want to think about life without him.  As it is, your relationship is already tense because there was an unfortunate incident involving an elemental destroying a couple of planes and the Air faction is blaming you for it.  You know you didn't do it, but \cRomeo{} suspects you're lying to \cRomeo{\them}.  Complicating matters even more, now is not the time to anger \cKing{} by denying the accusations too hotly, because the Queen has just commanded you to find out what \cKing{\they} knows of Water faction plots.  

Just to make your life even more difficult, you have to make sure that as few people as possible find out about your relationship with \cRomeo{}.  It goes without saying that you can't let the Queen find out, but most of the other elementals, regardless of faction, would also see you as a traitor.  \cPyro{}, as your overprotective brother, would certainly nag you to end the relationship as soon as possible for your own good (although you know that \cPyro{\they} was working very closely with a human scientist, \cMS{\intro}, and may have been involved in research to enable Azi to enslave elementals...so you could probably ``persuade'' \cPyro{\them} to leave you alone by threatening to tell the Queen about that).  You \emph{have} received much-appreciated encouragement from the human Azi diplomat \cDiplomat{\intro}, who thinks that your love story will do wonders for human-elemental relations.  President \cLeader{} is also sympathetic, though of course you know you can't trust \cLeader{\them} not to blackmail you.  Organizing a wedding would be even more of a challenge, because you'd have to find a supportive elemental to marry you!  (And \cRomeo{} keeps making noises about some sort of human marriage ceremony?  You should probably ask him why that is necessary.)

All in all, life is complicated, and you hope that this meeting won't make things even worse!

\begin{itemz}[Goals]
  \item Keep the Queen from finding out about your relationship with \cRomeo{}.
  \item Find a way to stay with \cRomeo{} forever.
  \item Find out what military technology the humans are developing and just how harmful it would be to elementals.
  \item Find out what, if anything, the Water elementals are up to.
  \item Keep \cRomeo{} from finding out about the plan to open the Conduit and bring over more Fire elementals.
  \item Convince \cRomeo{} that you did not blow up the airplanes.
  \item Figure out which elementals would be willing to perform a marriage ceremony.
\end{itemz}

\begin{contacts}
  \contact{\cQueen{}} The Queen of the Fire elementals, to whom you report.
  \contact{\cPyro{}} Your loving, if somewhat exasperatingly overprotective, brother.
  \contact{\cKing{}} The King of the Air elementals.  You act as an intermediary between \cKing{\them} and the Queen.
  \contact{\cRomeo{}} Quite simply, the love of your life.  Unfortunately, \cRomeo{\they} is human, an Azi soldier who is bodyguard to the human President.
  \contact{\cLeader{}} President of the humans.  Also (because the course of true love never does run smooth), \cRomeo{}'s Supervisor.
  \contact{\cDiplomat{}} An Azi diplomat who encourages your relationship with \cRomeo{}.
  \contact{\cDema{}} Secretary of State of the humans.  You don't know \cDema{\them} very well, but you have met.
\end{contacts}

\end{document}
