\documentclass[char]{elementals}
\begin{document}
\name{\cLeader{}}

You are President \cLeader{\intro}, the elected leader of the meta-government formed to replace the New United Nations when it was officially disbanded at the end of the 22nd century. You have your hordes of detractors and a steady base of supporters. You also find that you have to keep reminding people who blame you for every ill they experience that seeing as you possess no veto or legislative powers, you have considerably less influence over matters than they think. Most of your day-to-day activities involve keeping faction A from engaging in physical altercations with faction B because they refuse to censure faction C who doesn't agree with A's viewpoints on issue D. That said, you are still the elected representative of a good fraction of the human population, and when the need arose for a single individual to represent humans at the gathering today, you were it.

Your general approach to governance is mediation. When two forces oppose each other, you try your best to defuse the situation by whatever means possible. Although it's tricky, thus far you've managed to apply this philosophy even where the elementals are concerned. Whenever elementals wreak havoc -- and they do, all the time -- there is always a call for all out war with whatever faction of elementals caused the problem (or all elementals at once, because why not?). Your military advisors give you almost daily reminders that this would be a Very Bad Idea, and up until now you have done a good job of pacifying people. That said, you have also never really managed to extract any significant concessions or even apologies from the elementals involved: destruction of property, or even murder, seem like practically alien concepts to them. Still, this has gotten quite a bit better over the past 50 years or so. Improvements in agriculture, for example, have made modern farming quite a bit more resistant to a pack of fire elementals deciding that they want to bathe in the burning remains of a few thousand acres of farmland.

While things are a bit better than they were 100 years ago, they are still not good. The main reason you entered politics in the first place was that you feel very strongly that elementals act so boldly towards humans is because they know there are no real consequences to doing so. Elementals simply don't fear death or war on any scale the way that humans do. They do, however, fear each other. You are confident that if you could convince one of the elemental factions to support you, then humanity would be seen as a force to be left alone.

Despite your efforts, most of the elemental factions simply ignore humans, and, when pestered, resort to enslaving your diplomats for amusement or worse. But your persistence eventually paid off: \cKing{\intro}, the king of the air elementals, has agreed to establish persistent diplomatic relations with humans and is the reason you were invited to the meeting today. Unfortunately, he has thus far avoided agreeing to anything close to an official treaty -- he claims that while he finds humans interesting, they really have not proven that they have anything to offer air elementals in return for his protection. You are determined to prove him wrong, and this meeting is the perfect opportunity to do so. That said, many other elemental factions will be present and you will forge a treaty with however many factions you can.

Years of political engagements have taught you the wisdom of doing your research \emph{before} you come to a meeting like the one you're in charge of today. From what your spies have managed to discern, three different elemental factions will be present: fire, air, and earth. Water seems to be concerned about the situation but is keeping an eye from a distance.

%Idea: what's below could be literally told in the form of a ``report on the elemental factions'' whitesheet?

Fire has always been the faction that frightens you the most. The formidable \cQueen{\intro}, the queen of the fire elementals and one of the original four elementals who came to Earth 100 years ago, will be in attendance with a sizable contingent of servants. You have only been ``invited'' to an audience with her once before, and you wouldn't care to repeat the experience. No one really seems to have a great idea what \cQueen{} plans to accomplish today, but you figure you had better try and find out.

As best you can tell, the earth king will not be present; there is a rumor he is sick, which is a bit puzzling to you (you have made a mental note to ask some of your lead scientists more about how elemental physiology works). Still, several earth elementals will be present today, although with the king absent their hierarchy is unclear. You believe the leading earth elemental is called \cLoyal{\intro}, but humans have very few diplomatic ties to earth elementals and you don't know much beyond that.

There are always a huge stream of unresolved incidents with the elementals, but at the moment media and public attention is very focused on two airplanes that were destroyed over Hawaii, almost certainly by elementals. Your military advisors have not yet determined exactly which faction is responsible, but it is under active investigation and if you have time, you plan to get an update on the current situation from your diplomatic advisors. Perhaps you will be able to find out more at this meeting, but you are not willing to let it interfere with your plans for a lasting treaty.

Given the significant dangers posed by the elemental factions, you are acutely aware the people attending with you need to be united, and as the leader the task of making sure that happens falls on you. There are seven other humans coming with you, most of whom you already know. First there's your bodyguard \cRomeo{\intro}, an Azi soldier who you have known since you were very young and is like a brother to you. As is standard procedure for Azi bodyguards, you are also \cRomeo{}'s supervisor. Next there's the secretary of state, \cDema{\intro}, who is the only other member of your executive branch present. \cDema{\They} is a talented speaker who is good at playing up the emotions of a crowd; although you do not agree on every issue, in general \cDema{\they} serves as a good foil to your more conciliatory negotiation style. Also accompanying you are \cAvatar{\intro}, the head diplomat in charge of negotiating a peace treaty with the elementals, and \cAvatar{\their} Azi assistant \cDiplomat{\intro}, also a talented negotiator.

Accompanying the politicians is a sizable contingent of scientists. Officially all three scientists report to you, although in practice you've found scientists tend to pay little attention to the chain of command. The most infamous of the scientists is \cGD{\intro}, the great granddaughter of Konrad Strauss, the scientist who originally caused this mess 100 years ago. She's apparently made quite a name for herself in the scientific community, and specializes in researching the Conduit and the elemental plane. Also present is \cMS{\intro}, a more eccentric scientist who focuses on the elementals' mental powers. Finally, there is \cScientist{\intro}, an Azi scientist who your report indicates is (as expected of an Azi) a stable and capable individual who studies the chemical processes that underlie the elementals. Your reports indicate that there are fairly tense social interactions between the three scientists, and that \cMS{} has been accused of safety procedure violations in the past by \cScientist{}. Still, all three are present because, even after 100 years, no one fully understands what exactly makes elementals tick, and these are the three people best situated to learn more. In particular, the opportunity to study one of the elemental leaders in close proximity has almost never presented itself before. You're just going to have to keep an eye on these three to make sure they don't get incinerated or cause an inter-species war. You also suspect the scientists have their own research agendas and you are going to have to find out what exactly they are.

Given that elementals have the ability to mentally control humans, interactions between elementals and people who are ``politically or scientifically sensitive'' are supposed to be closely monitored. One interaction you are aware of is that your bodyguard \cRomeo{} is enamored with a young fire elemental. You don't know exactly what to make of this, but you trust \cRomeo{} and as long as he is cautious, you see nothing wrong with this. Still, your spies have reported that there is significant evidence that other humans at this gathering are having unsupervised interactions with elementals. This could indicate any number of things, but the more troublesome implications are that one or more of the members of your entourage are either willingly working with the elementals or are actively in thrall to one of the elemental leaders. You will have to get to the bottom of this, fast.

%does leader have some ``resist enslavement'' tech from MS?

%TODO: airplane incident

\begin{itemz}[Goals]
  \item Maintain peace between humans and the elementals at all costs.
  \item Keep all the humans attending the gathering alive and happy.
  \item Work with \cAvatar{} and \cDiplomat{} to negotiate a peace treaty with one or more of the elemental factions.
  \item You do not know what the various elementals are planning to do here; find out. Whatever it may be, prevent humanity from being marginalized by the elementals.
  \item Figure out what \cGD{}, \cMS{}, and \cScientist{} are up to and make sure it isn't too dangerous.
  \item Investigate humans that may be actively enslaved by elementals or working with them in secret.
\end{itemz}

\begin{contacts}
  \contact{\cRomeo{}} An Azi soldier serving as your bodyguard.
  \contact{\cDema{}} The secretary of state who helps keep the government together.
	\contact{\cAvatar{}} The head Cit diplomat in charge of helping you forge a peace treaty with the elementals. Talented, but often loses focus and has a rather absent-minded personality.
	\contact{\cDiplomat{}} An Azi negotiator who reports to \cAvatar{}.
	\contact{\cGD{}} The great granddaughter of Konrad Strauss. Specializes in the elemental plane and the Conduit.
	\contact{\cMS{}} An eccentric Cit scientist who specializes in understanding how elementals can enslave humans and each other. Has a history of procedural violations.
	\contact{\cScientist{}} A talented Azi scientist who researches elemental biochemistry.
	\contact{\cQueen{}} The queen of the fire elementals.
	\contact{\cKing{}} The king of the air elementals.
	\contact{\cNaturalist{}} \cKing{}'s trusted advisor, a high-ranking air elemental.
	\contact{\cLoyal{}} A high-ranking earth elemental.
\end{contacts}

\end{document}
