\documentclass[char]{elementals}
\begin{document}
\name{\cMiniWater{}}


You're on a mission. 

Today, the great council of elemental lords convenes once again. For the first time in more than a century, Water will not be attending.

Officially, that is.

Your queen, \cWaterQueen{}, thought it best to avoid the internecine plots of the other factions: Fire's brutal power, Earth's irritating conservatism, and Air's fickle destructiveness were all best left to their own devices. Relations between the elements have been neither stable nor sound in recent years, and, to make matters worse, the smelly, petty creatures native to this realm -- humans -- will be there to throw a wrench in the works. For some reason, the king of the Air elementals thought it would be a good idea to invite them to this most sacred of gatherings. Far better to stay away, to stay safe beneath the waves.

But dealing blindly with the whims of the other elements would be equally foolish. They're all up to something, that much is clear -- why else would the meeting be taking place at the old laboratory where your kin first arrived on this world? Too much could happen here to shift the balance of power against Water, if you're not careful. That's why you're here -- to serve as \cWaterQueen{}'s eyes and ears without interfering directly.

You've never been the most powerful of the Water elementals, nor the wisest, but your penchant for stealth and instinctive cunning -- not to mention your absolute loyalty to Water -- made you an ideal candidate for this task. With any luck, you should be able to mingle freely with the humans and the other elementals without attracting too much unwelcome attention. If anyone asks, you're just here for the food.

But, of course, you've been given explicit orders. You're to keep track of any bit of information that could present a threat to Water, or to the elementals as a whole. You've heard all sorts of distressing rumors already on your way here -- the elementals are losing their power, the humans want to drive you off their planet, one leader or another is bargaining with the human leader -- too much to keep track of without some concrete evidence.

But rumors aren't all you have to work with. A while ago, a member of \cWaterQueen{}'s court wandered off and simply vanished, never to be seen again. No one knows what happened to the missing elemental, or why, but perhaps the answers are to be found here. Personally, you have no doubt that Fire is to blame -- those fiends would be all too happy to boil a helpless Water elemental to death if no one were around to stop them. Your queen has given you a missive to give the Earth delegation, detailing her suspicions -- if \cWaterQueen{}'s fears are accurate, their king and his second-in-command, \cLoyal{\intro}, have every reason to assist you in finding an answer. 

There's also the matter of the Conduit. The location of the meeting is a human dwelling for a reason -- it's the only place on this world where the human and elemental planes fall into alignment. Today, the two planes will be close enough for beings to actually pass through -- and \cWaterQueen{} is convinced that the elemental lords are vying to pull more of their own kind through the portal. Fire, of course, would be the worst -- the last thing you need is more flaming monstrosities in this wonderfully lush world. Air and Earth rarely bother your kind, but it would still be less than ideal for them to shift the balance of power. If only there were some way to keep all of these forces in check at once... but that's just wishful thinking. 

Still, \cWaterQueen{} has told you that if you have a chance to call more water elementals through the portal, you should see what you can do. If there's a primal water elemental or two running around, it makes your job easier -- who knows what you might find out in all the chaos? You've already found a willing accomplice -- \cMiniAir{\intro}, a small but entirely mischievous Air elemental, who seems all too willing to spread a bit of anarchy by summoning another water elemental. Besides, if you can let \cMiniAir{\them} take the fall for the whole thing, so much the better.

The best you can hope to do, really, is confuse the rival factions enough to keep them from doing too much damage. Perhaps, if you overhear a particularly volatile secret, you might be able to spread it around and turn allies into enemies... you've always been good at wreaking havoc with your wits. That's why you're here, after all. Just make sure no one decides to make an example of you in the process. The last thing you want to do is call attention to yourself.

For that matter, perhaps the humans -- dirty and alien though they are -- might make useful allies. One on one, a human could never stand up to an elemental in its prime -- but there are millions of them on this planet, and only a few of you. Besides, they've been known to come up with all sorts of fascinating devices to change the world around them, and it's entirely possible that they're onto something genuinely useful. Or genuinely scary -- the difference between a cool gadget and a terrifying weapon is all too small. Either way, your responsibility is the same -- make sure the humans are pointing it away from you, figure out exactly what it does, and let \cWaterQueen{} know the instant you get back.

All of which, of course, requires that you make it out safely. So you'll hide, and you'll sneak, and you'll listen and befriend and spread confusion, and perhaps you'll make it through the day with something useful -- and maybe, just maybe, it'll be important enough that \cWaterQueen{} will reward you with a promotion. Wouldn't it be grand to be a powerful elemental?

\begin{itemz}[Goals]
	\item  Learn as many secrets as you can. In particular, figure out which of the elemental factions is the greatest threat.
	\item  Keep the other elementals (especially Fire) from calling more of their kind through the Conduit. If you can, summon a Water elemental or two yourself.
	\item  Make friends with powerful humans and see if their technology could be useful to Water.
	\item  Don't call attention to yourself. You want to make it out in one piece to report to \cWaterQueen{}.
	\item  Try to learn what happened to the missing Water elemental.
\end{itemz}

\begin{contacts}
	\contact{\cMiniAir{\intro}} A playful young Air elemental who seems quite willing to help you summon more of your own kind.
	\contact{\cLeader{\intro}} \cLeader{\They} seems to be in charge of the humans. Maybe you could make friends with \cLeader{\them}.
  \contact{\cQueen{\intro}} The ruler of the Fire elementals. \cWaterQueen{} has warned you to avoid \cQueen{\them} at all costs. You agree -- \cQueen{\they}'s terrifying.
\end{contacts} 

\end{document}
