\documentclass[char]{elementals}
\begin{document}
\name{\cNaturalist{}}

For as long as you can remember, you have been curious.  Curious about the wind patterns on which you float, curious about the lives of other elementals, curious about this strange world in which you were born, and curious about the elemental plane in which you should have existed.  For nearly a century, you have travelled the world and seen its wonders, and yet there is still more to see and know.  Of course, being an air elemental does give you some advantages in being able to move around the world; you can float where the wind takes you, and the wind will invariably take you where you want to go.  You are loyal to your King, \cKing{\intro}, not entirely because you agree with his policies, but mostly because your life force is tied to his.

For most of your century-long life, you only dealt with \cKing{} in official settings.  While \cKing{} remained locked in a power struggle between the leaders of air, fire, water, and earth, you were much more interested in seeing the world and the strange human creatures that occupied it.  For decades, you were a careful naturalist, observing humans from afar, never interfering with their lives and only rarely being observed by them.  Recently, though, \cKing{} has taken an inexplicable interest in the fleshy species he had so long ignored.  You had already seen so much of the human world that you were \cKing{\their} natural first choice when \cKing{\they} needed someone to assist \cKing{\them} in learning more about humans.  \cKing{\They} asked you to speak with the humans on his behalf, and you delighted in the opportunity to discover more about them, even if you have only been able to talk to a few, and only on official business.

You have been frequently meeting with \cDiplomat{\intro}, who, like you, has been given the task of communicating with the other side by \cDiplomat{\their} leader.  \cDiplomat{\They} is very interested in improving the relationship between humans and elementals.  You think this could be quite useful to your research, as it is much easier to study humans when they are alive and comfortable, and many other elementals treat them with careless abandon.  In addition, \cKing{} has recently been talking about forming a treaty between air and humanity.  You aren't entirely sure why \cKing{\they} wants to do this; it just seems to be part of his recent obsession with humans.  While you don't know what triggered it, you do find it useful for your studies, and \cDiplomat{} has also been encouraging you to pursue the alliance.  Hopefully you can finalize the treaty at the today's meeting.  In addition, this year's Elemental Council will be in close conjunction with the Conduit between the human plane and the elemental plane.  It is possible that the Conduit could be opened and bring more elementals into the human world.  You want to avoid allowing more elementals through.  \cKing{} is determined to keep the Conduit closed, and you certainly would rather not allow more powerful elementals to come in and kill all the humans you have worked so hard to observe, and have grown to like.

From \cDiplomat{}, you found out about two certain human scientists who will be present today, and whose research focuses heavily on elementals.  The first is \cGD{\intro}.  \cGD{\Their} great-grandfather had researched the elemental plane, and it was his experiment that had brought the first group of elementals (including your King!) into the human world.  You were so intrigued with her work, that you snuck into her lab disguised as a stray draft just to have a look around.  When you heard footsteps coming towards the lab, however, you quickly blew away instead of staying to introduce yourself.  The second is \cScientist{\intro}, a close friend of \cDiplomat{}'s.  You have heard that \cScientist{} is an honest and trustworthy scientist, who studies the physiology of elementals, among other things.  You hope to be able to meet them both at this council, and to that end, have sent them each a message introducing yourself and your research.  You initially sent the message in your native cloud-writing, but realized they probably could not read it, and managed to send a paper note with a quick lesson from \cDiplomat{} on how to use a ballpoint pen.

Of course, your studies have not always gone perfectly.  Recently, you were en route to report back to your King, when you saw two large metal birds in the air.  You decided to have a closer look.  They turned out not to be birds, but large, winged metal tubes, which had windows through which you could see human faces.  You paused for a moment, marveling at how these tiny, mundane humans had been able to nevertheless build a flying machine.  You watched the machines soar through the clear sky for a moment, and began to wonder if these human contraptions were carried by the winds in the same way air elementals were. In your years as a naturalist, you had learned that elementals were not always careful to control of their powers and often humans would be hurt as a result.  You had been meticuluous in avoiding harming your research subjects.  But this time, you were just too curious. You began to manipulate the air currents, and watched the planes smoothly move up and down, side to side, for a time not noticing the look of panic that was overtaking the human faces inside.  It was only when you managed to make one machine roll over to see if it could fly upside-down that you realized you were taking things too far.  However, startled by your own realization that you might be hurting the little humans inside, you briefly stopped paying attention to what you were doing with the wind, and the two flying machines collided with a mighty explosion before hurtling into the ocean below.  You watched the water ripple out from the crash site and nearly flood a coastal village on a nearby volcanic island, before fleeing the scene in a panic to confess all to \cKing{}.  \cKing{\They} at first did not understand why you were so upset, but eventually \cKing{\they} came to see that if the human leader found out you had crashed the airplanes, \cKing{\their} plan to pursue a treaty with the humans would likely be ruined.  \cKing{} suggested you blame \cJuliet{\intro}, a low-ranking fire elemental who is fire's liason to air (and who seems to be fire's liason to humans as well), who was traveling to the fire fortress inside the island's volcano that same day. \cJuliet{\They} could have come across the flying machines just as easily as you had.  There were enough flames in the crash, and fire elementals are responsible for a great deal of destruction to human buildings, so this story seems plausible enough, and should hold up as long as the humans have no way of uncovering other evidence against you.  

For now, you are content to keep the blame on \cJuliet{}.  If the humans found out the crash was your fault, it would not only make what the other air elementals were trying to do more difficult, but might also bar you from further research with the humans.  \cDiplomat{} would most certainly not approve.  Still, you cannot get the image of the terrified human faces in the airplane windows out of your head.  The guilt weighs heavily on your conscience, but you try to trust that \cKing{} knows what is best for all the air elementals. Anyway, \cKing{\they} will keep your secret as long as you keep \cKing{\their}...

In the incessant power struggle between elemental factions, \cKing{} has recently devised a disturbing plot.  He knew you had snuck into \cGD{}'s lab previously, and had been asking you for information about \cGD{their} equipment. He apparently broke into the lab with a captured low-ranking water elemental, and used the equipment to extract the water's essence.  While it is somewhat disconcerting that \cGD{} has equipment that can extract elemental essence, you are more concerned with what \cKing{} did.  What exactly he did with the water essence afterwards you don't know, but you do know he somehow used it to create a substance used to cause great illness in the earth King.  As a result, only lower-ranking earth elementals are present at this council, and you worry that they suspect foul play.  You might do well to avoid them if you can.  While you disagree with \cKing{}'s means to get ahead of other elements, you would rather not face \cKing{\their} wrath if you were to reveal the plot.  

\begin{itemz}[Goals]
  \item Use the time you have at this meeting to learn more about the lives of humans.
  \item Keep your involvement in the flying machine incident a secret, and prevent anyone from discovering evidence against you.
  \item Help \cKing{} finalize a treaty with the humans.
  \item Learn about what \cGD{} and \cScientist{} have been researching about elementals, and attempt to share your knowledge.  
  \item Avoid revealing \cKing{}'s plot to poison the earth King.
\end{itemz}

\begin{contacts}
	\contact{\cKing{\intro}} The King of the air elementals and your direct superior.  You still aren't sure why \cKing{\they} is suddenly taking an interest in humans.
  \contact{\cDiplomat{\intro}} A human diplomat who has been very interested in working with you and the other elementals.
  \contact{\cGD{\intro}} A human scientist by whom you are intrigued, and would like to meet.
  \contact{\cScientist{\intro}} Another human scientist with whom you are fascinated, and would like to meet.
  \contact{\cJuliet{\intro}} A low-ranking fire elemental whom \cKing{} has officially blamed for the airplane incident.  You hope \cJuliet{\they} doesn't know it was really you.
\end{contacts} 


\end{document}
