\documentclass[green]{elementals}
\begin{document}
\name{\cNewElemental{}}

\emph{The GM will tell you which type of elemental you are: either earth, air, fire, or water.}

You are an elemental. You have lived on the elemental plane for your entire life and know of no other existence. You love basking in your element, and occasionally you are commanded by your parents to go out and battle one of the other elemental factions. You are fairly weak, so few other elementals report to you, but one day you will be bigger. Mostly you interact with the four primal elements: earth, fire, and, or water. But sometimes when the fighting gets serious there are these other elementals called quintessence that come out and try to break up the fighting. You don't really like them but for some reason everyone seems to listen to them anyways.

You were nestled peacefully in your element when suddenly you heard a most beautiful song.  It was pretty and enticing, and you got sucked through a door... into this weird place.

There are elementals here that are very big. Most of them could easily enslave you, and you really don't feel safe being so close to elementals of different factions --- back on the elemental planes, they would kill you in an instant for approaching them like this. But things seem \emph{very} different here and you really don't know what to make of anything. And what are these other things that aren't elementals?

Your CR is 4 for the purpose of normal combat and enslavement (see ``The Elemental Enslavement Mechanic'' greensheet and your corresponding enslavement ability).

You start the game immediately after having been through the strange door, which promptly sealed shut behind you.

\end{document}
