\documentclass[char]{guildcamp1}
\begin{document}
\name{\cPassive{}}

%Passive's name is: Quarth
%Active's name is: Krung

Your name is Quarth. You are a prominent scholar of a galaxy-spanning species that calls themselves the \emph{Xenids}. Your species started off as an eight-legged race that relied upon bulky claws for fine-scale manipulation. Over the centuries your species shed its apprehension to large-scale genetic engineering and adopted a bipedial, two-armed form that you copied from several other successful species. Your civilization is very powerful, but is currently at war with a smaller but more advanced galaxy-spanning civilization called the \emph{Idrians}. The latest reports suggest you are losing the war and some of the planets on the border stars of your civilization are being conquered. This doesn't concern you too much; you are not a soldier and have little interest in the war, and the border stars are really just small colonies that are easily evacuated. You were born on the Xenid home world which is quite far away from the war front and not likely to be threatened anytime soon. Your passion is learning and studying new things from outside the Xenid civilization and bringing them back home.

The majority of the Xenids, although not strictly xenophobic, prefer to stay on Xenid-controlled planets and do not interact with other species. Depending on who you ask, you are either blessed or cursed with a personality that has no trouble interacting with foreign species. This gives you a clear advantage in the Xenid academic circles --- while others tend to sit around analyzing and debating data collected by others, you actively reach out and gather new knowledge. Towards this end you joined \emph{Contact}, the exploratory and scouting branch of the Xenid hierarchy. Contact's primary goal is to gather data on new species: ``How technologically advanced are they?''; ``How does their government work?''; ``Are they a military threat?''; ``Are they a potential ally?''. There are hundreds of billions of stars in the Milky Way and only some support life, so there are always plenty of uncharted stars out there.

Your current contact assignment is to investigate an unknown energy signature detected at a planetless blue dwarf star. You are in a two-person vessel, and your partner is Krung. She is a soldier from one of the border star systems. Her home planet is currently under siege and has possibly already fallen. In your previous encounters with her, you have found her to be very focused on finding allies or military technology from other civilizations to help with your war against the Idrians. Occasionally you find her overly zealous: she often violates the first-contact conventions that are designed to prevent a diplomatic miscommunication from developing into large-scale conflict. As she constantly reminds you, thus far nothing disastrous has happened, so you haven't had cause to formally censure her.

On your way to the blue dwarf, your sensors picked up what you believed to be an unknown ship traveling at a very high fraction of the speed of light. You and Krung debated for some time what action to take. You argued that the unknown ship was not emitting any signals and was clearly not interested in being discovered, so might destroy your small scout ship to maintain its stealth profile. Krung argued that the potential benefits outweighed the risks; a cursory material analysis suggests that whoever built this ship is technologically comparable to, and might even surpass, the \emph{Idrians}. While you were busy debating this, the ship's main power supply seemed to falter and die, and it started emitting a string of sequential binary-coded prime numbers. Your curiosity now peaked and taking the sequence of primes to be a distress signal of sorts, you both decided to get closer and investigate the ship.

The ship consists of four main components: a solar array, a battery system, an ion engine, and a massive computer. The solar array and battery system are superior to anything your civilization can manufacture, with an almost 100\% energy conversion ratio and almost no passive battery loss, while the ion engine is mediocre at best. The computer is the part that fascinates you the most, as it clearly surpasses both Xenid and Idrian design. It consists of a wide array of subatmoically packed memory cells tightly intermixed with equally small-scale processing units. There is no atmosphere on the ship, but there are three robot bodies wirelessly hooked up to the computer system.

After some analysis, you determine that the computer seems to be designed to run a giant simulation. The odd powering down of the ship's system you witnessed recently seems to have caused all but a very small part of the computer system to shut down, but fortunately has also opened up a simple debug layer to the simulation. This layer contains a rather lengthy tutorial clearly designed for contact with other species that starts with basic mathematics and works forward into the basics of science, culture, and language. The species that built this system refers to itself as ``human'', and if this tutorial can be trusted, this simulation and the ship that houses it, called the \emph{New Eden}, is most of what remains of their civilization.

For your own reasons, you and Krung are both eager to learn more about these humans. Unfortunately the information contained in the tutorial is not nearly sufficient. If you want to learn more, your only opportunity seems to be to try and interface with the simulation directly. Fortunately, the newly exposed debug layer and corresponding tutorial provides a simple way to do this; these humans seem to have been masters of the mind-machine interface, which only reinforces how important it is to learn more about them. Before you dive into the simulation, you take a moment to learn all that you can from within the ship.

%The human civilization seems to have somehow exhausted their sun's energy prematurely; you have no idea how such a feat is even possible. Since they had apparently never developed efficient inter-stellar drives, they decided to embed their civilization within a simulation and launch it to wander the galaxy, rebuilding its energy reserves as needed from nearby stars. 
You are not sure what caused this mysterious power-down of the ships systems, but you do know that there are only four hours of battery life remaining on the functioning part of the simulation. What greatly interests you is that there appears to be a very high-density entity within the subset of the simulation that is still active. This appears to be a backup copy of the operating system. The system seems to be designed to prevent you from accessing the backup copy externally, but you are fairly confident that if you could access it, it would serve as a perfect testbed for safely understanding and interacting with these humans. Your overriding goal upon entering the simulation is to find a way to secure this backup copy.

With a rudimentary knowledge of human language, the two of you wirelessly interface with the computer simulation. The first thing you notice is that the simulation is totally immersive and an effectively perfect recreation of reality: you are not sure exactly how to disconnect yourself from the simulation and return to your body. The tutorial claimed this would be easy, but the ``escape console'' it said would materialize in front of you upon connecting is nowhere to be found. You seem to have been put in control of one of these fleshy human bodies, what they refer to as a female. The tutorial was not very specific on what the phrase ``gender'' actually means or what the different between the two sexes are. You make a mental note to investigate that further.

You take a look at your surroundings. Your genetically-perfected memory comes in handy here, as you start mapping pictures to vocabulary. You are in a room with one window, there is a bed, a lamp, a small desk, a closet, and a small side room containing a toilet, a shower, and a sink. After some looking around you conclude that you are in what is called a ``hotel room''. Distressingly, you are alone and Krung is nowhere to be found. The technology level of whoever built this room also appears to be absurdly primitive compared to the civilization that built the ship currently housing your body. Why are the humans that built the ship so advanced while those in this simulation so primitive?

Just from studying the tutorial, you have decided that these humans are a most fascinating and unique species. Ideally you will simply return to your home planet with the backup copy of the world, but you are a very practical person, and know this may not be possible. You intend to find out as much as possible directly from the source. You have taken mental note of a list of the most important questions pertaining to human culture and behavior. In the mean time, you leave the hotel room and wander down the hallway in search of a human, eager to  begin your research.

You're not sure exactly how to find the backup. But you do know that it and anyone very close to it will be able to resist any corruption that you suspect might be present in the local environment. You have devised a way to test the corruption level of others, and suspect that someone who has little to no corruption is likely in possession of the backup copy.

The disconnection of your consciousness from your body poses an additional problem. Your species does not require sleep, but periodically your brain requires conscious maintenance to its memory network that you cannot provide. You are not sure what the consequences will be within the simulation, but you would like to find a way to avoid it.

You seem to have what is called a sticker adhering to your shirt. At the top is neatly printed ``Hello, my name is'' and at the bottom, in black ink: \cPassive{\intro}. You have spent enough time getting yourself situated. You set out to find out exactly what is going on with this confusing yet potentially quite powerful species.

%Convert to research journal format
%\begin{enumerate}
%\item You are mostly aware of the details of procreation, but the tutorial provided no idea as to how humans actually go about finding a mate.
%\item Why are the humans around you having a wedding? What purpose does a wedding serve?
%\item Given the existence of multiple religions, how does a human determine which one is correct? Gather at least two different perspectives on this subject.
%\item What star system do humans come from?
%\item Why is the technology level inside the simulation so primitive compared to the host ship? As far as you can tell, both were constructed by humans.
%\end{enumerate}

%QUESTIONS

\begin{itemz}[Goals]
  \item Find Krung in the simulation. She's likely stuck in a human body as well.
  \item Find the backup copy of the world, and somehow extract it from the simulation and back to your ship for analysis. It represents a perfect and pristine copy of the world, without being influenced by your presence or the recent power-down.
  \item Obey Contact's first-contact principles whenever possible. Keep Krung in line regarding these principles as well, although you rarely have much luck with that, so it will be difficult. \emph{(See the Xenid bluesheet.)}
  \item Find the answer to as many of the questions in your mental research journal as possible.
  \item Find a way to prevent the mental degradation of your body back on the human ship.
  
  %does she still want to kill one of the grooms? Stealing the backup copy is already alterning the world enough.
\end{itemz}

\begin{itemz}[Notes]
  \item The number combination to re-enter your ship through the air lock is 13-26-4
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  %\contact{\cActive{}}: A fellow Xenid and your primary partner within Contact.
  \contact{Krung} A fellow Xenid and your primary partner within Contact.
\end{contacts}

\starttag{mems}

  \memfold{if you see an item whose number starts with ``77''}{These people seem to have made quite respectable progress on the mind-machine interface front. With a little help, their work could be just what you need to get out of the simulation. With a \bf{completed head-mounted display} and a \bf{completed mental amplifier}, you might be able to jury-rig up something to get back into your original body. One problem is that you will need a lensing device of some kind: specifically, a ruby or sapphire gemstone. Open your $\Delta$ packet now.}

\endtag

\end{document}


%%Clarifaction about how aliens reproduce. otherwise has no context to ask questions about humans
%% Is there a ranking system within "contact" and do one of the aliens outrank the other
%%Clarification of what she knows/understand about the ship
%%Clarification about what she knows of the save state (that it is static)