\documentclass[char]{guildcamp1}
\begin{document}
\name{\cPastor{}}

You are a man of God, but you know what it’s like, to be lost. Suffering and self-destruction are no strangers to your door, and they reside not only in the hearts of your flock.

When you were younger, your wanderings took you deep into the underbelly of society. You drank from the cup of hedonism, and paid for it in the slow decay of your body and soul. You were dissatisfied, depressed, and anxious. You fell into taking {\bf Anaphmonine}, a potent drug that went by the street name of {\bf Bite}, named for its tendency to make one's teeth clench. It was the only thing that made you fulfilled and content, but the feeling always faded, and then there you were, lying on the ratty, filth-encrusted couch of the messy apartment that you shared with three other {Bite}-heads. Skull pounding from dehydration, your only desire was to start the cycle over again.

But still, you are thankful for that period of your life, because if you hadn’t been that desperate, perhaps you never would have found Virtuism. It was a member of the soup kitchen staff saved you. She was a woman of generous heart and glowing spirit, and she helped you to see the truth. You stepped out of your old life like a shed skin, ready to see the light of God with clear eyes.

Under that woman’s tutelage, you attended a seminary, and became a pastor of Virtue. You attracted a large flock, people attracted to your deep-seated belief that the only way to find grace was through prayer and religious practice. You fit into the patterns and traditions of Virtuism as though you were born to stand at the pulpit. You even wrote a book; one of the most prominent contemporary works applying the Tennants of Virtuism to modern life.

But throughout all of it, though you were able to give up the drink, the gambling, and the women of ill repute, there was one aspect of your previous existence that you just couldn’t seem to shake. The Bite. You tried, you really did, and then would come the tremors and the insomnia, the itching and the nausea. The withdrawal symptoms were so severe that you could barely function. And to add to the confusion, when you do take Bite, (which is more often then you’d like to admit) you feel lifted, elevated towards the light. You sometimes have ecstatic visions of angels and a heavenly chorus, and you feel as though, if you only climbed a bit higher, you could see the face of God.

Yet how can a drug, a chemical created by science, be at all connected to Virtue? After all, this is the same science that steals your flock away, charming them away from Virtuism with shining technological toys! How can anything good come of that?

You just need help, that’s all. The temptations of sin seem too great for a single man to break. But Virtuism teaches that one should rely one oneself and one's own inner strength to pull through adversity, for Marcrox helps those who help themselves.

You would lose your flock, if anyone were to find out about your transgressions. And you know that if you were to lose your respected position, you would be at even greater spiritual danger of falling back to the degenerate excess of your youth. Your soul is already burdened, and you often feel as though you are balanced on the point of a precipice, and leaning any one way or another would send you tumbling down the slope.

You can’t let that happen, so you bear your spiritual torture with the grace of a saint.

You have discovered that the more expensive, pure-based Anaphmonine is better at keeping the withdrawal symptoms away with minimal side effects, and that regular injected doses of pure Anaphmonine is enough to get you through the day without suffering too badly. You need to inject it, not eat it, as eating it causes more intense hallucinations. (If you inject Bite, you will hallucinate for 2 minutes, while if you eat if you will hallucinate for 5 minutes). Unfortunately, Bite is expensive, more than you can afford. You’ve already sold as many of your personal belongings as you can without the lack being publicly noticed, and take as much from the church’s donation box as you can. You've even taking to explicitely requesting donations, which only works a few times on any one person.

And then, sometimes people leave valuable things in the church, after services. They should be returned, of course they should, but couldn’t they also be viewed as {\em donations}? And with misplaced items, it’s not as though their owners will ever remember where they were lost?

It’s a short jump from there to direct stealing, and you tell yourself that since you’re a preacher, you’re doing so much good for others already that the damnation of your own soul is less important. A few thefts here and there, for the sake of your own health and sanity, which in turn saves souls… it all works out, doesn’t it?

For now, you just make your way from day to day, from theft to theft, and from one sermon to the next. You are going to be ministering a wedding at the Hotel Virtuoso, joining \cGroomA{} and \cBride{} in holy matrimony. It’s going to be a grand celebration.

You were walking along the hallway, going back to your room at the hotel, when you saw  \cGroomA{} standing at a doorway. You opened your mouth to greet him, when an alarm blared in your ears, and everything went black.

The next thing you knew, you were lying in a metal box, a loud alarm making your teeth vibrate. You sat up with a start, and saw a cramped metal room with the walls covered with buttons. You turned to the side and saw a horrible demon, a man made of metal and plastic, and you yelled in fright. The being leapt from its box and dashed about the room, but you looked down and saw that \emph{you yourself} were made out of metal.

It was as though you had taken Bite, but you did not remember taking it, and the sensations were altogether too clear, to vivid, to be a result of the drug. This was really happening.

You held your head in your metal hands and moaned. You had heard people talking about things like this. Ridiculous secular fictions that the youth talked about, robots and ``virtual realities''. But that’s what this was. Your whole life, you realized, had been the fiction. You were a robot, dreaming. What was God’s creation, then? The meticulous silver innards of a computer?

After an interminable time had passed in that cramped hell, you heard a voice, speaking from on high:

\emph{EMERGENCY SHUT-DOWN INITIATED. FOUR HOURS OF BATTERY LIFE REMAINING.}

Then, it ended, as suddenly as it had begun. You were lying on the ground in the hallway. You lay there for some time.

What you had seen was not a false vision. After years of imbibing Bite, you had become skilled at differentiating true happenings from hallucinations. Unreality was the truth of the world.

You nearly fell, then. The world was not real. God was not real. You were not real.

But then another voice came, a still small voice in the back of your mind. \emph{Perhaps,} this voice said. \emph{Perhaps what you have seen is not a disproof of God, but rather a look into His mind? Perhaps it was heaven that you saw?}

Could it be? Could you be a chosen Prophet, to see into the mind of the Virtuous One? Was that the Truth?

You got up, slowly rising to your feet. Yes, that is it. This is a sign that you must spread the Word, and bring more souls into the flock.

\emph{Emergency shut down? Four hours of battery life?} What was going to happen in four hours? You remembered the prophecy of the End of Days, and shivered to your core. Is it possible that \emph{you} are to minister the wedding that was prophesied to save the world?

As you moved forward with new purpose in your step, you saw a key lying on the floor. You picked it up, grateful to God that you had something more to sell and keep yourself sane until the holy time comes.

\begin{itemz}[Goals]
  \item Minister the wedding, according to ritual. It may be that all of Creation depends on it.
  \item Convince people to donate items to the church, particularly valuable ones, in order to feed your drug addiction. 
  \item Purchase some Bite, which is a white powder that you can mix with water and inject with a syringe. You'll need it to stave off withdrawal.
  \item Convert nonbelievers to Virtuism.
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}

\begin{itemz}[Contacts]
  \contact {\cBride{}} A kind, pious woman. You are gladdened to see someone so young taking to Virtuism as she does. Her generous monthly donations have endeared her to you greatly.
  \contact {\cGroomA{}} A fine man. You wish him the best of happiness. Though you'd love it if he donated more.
  \contact {\cRival{}} An intense young man. Comes to church maybe twice a year. You know he's quite wealthy, and you would like to add him (and his donations!) to the flock.
\end{itemz}

%%% I need mempacks and items.
\end{document}


%%QUESTIONS: Details on the nature of Bite and virtuism
