\documentclass[char]{elementals}
\begin{document}
\name{\cPyro{}}

You are \cPyro{\intro}.  You are a powerful member of a powerful race of fire elementals.  You are one of the strongest 2nd-tier elementals on this plane, and defer to your Queen.  However, you have \cQueen{\intro}'s ear when it comes to important state decisions.  \cQueen{\they} is generally less inclined to exercise Fire's full potential than you are.  While \cQueen{\they} must keep up appearances and show diplomacy when working with other elementals or humans, you have no such reservations.  While other elementals, particularly those that rank highly, can be formidable foes, you can hardly understand why they bother with the weakling species that occupies this plane.

While you have heard a great deal about the elemental plane, you have never been there yourself.  You came into being after the incident that somehow brought a number of powerful elementals into the human world.  While you sometimes wish you could see the plane on which you were meant to exist, you have no real desire to leave the delightfully flammable human world.  Here, you can release your power fully, and spread fire in a way that would likely be repressed by stronger members of other elements were you on the elemental plane.  Here, you can be one of the strongest Fire Elementals.  Here, you can prove that Fire is the strongest.  And here, you can be sure of your ability to protect your little sister, \cJuliet{\intro}.

Although it is a quaint monniker, and human familial relationships make little sense to you, you do believe the term ''sister'' does seem to best describe how you feel about \cJuliet{}.  \cJuliet{\they} was spawned on the human plane just after you were, and you spent your first day of existence burning down a forest to provide enough fire to protect \cJuliet{\them} from a sudden rainstorm, which you secretly suspect was an attempt by Water elementals to neutralize you and your newly-spawned siblings.  You and \cJuliet{} were separated from the others by the downpour, and you believe you were the only ones to have survived. \cJuliet{\they} is not as strong or as high-ranking as you, and you fear if Water, or even Earth or Air, tries to gain more control over the human plane, \cJuliet{\they} would be one of the first Fire elementals to fall. For this reason, when you found out \cQueen{} was looking for someone to infiltrate the human ranks and spy on them, you were quick to recommend \cJuliet{}.  You knew that keeping \cJuliet{\them} in the Queen's favor would give her more protection, and even provisionally increase \cJuliet{their} power.  However, you now worry that perhaps you were too hasty.  \cJuliet{} began as the intermediary between \cQueen{} and the Air King, and now all the Air elementals are blaming \cJuliet{\them} for a disaster you are almost certain was caused by an Air elemental.  While you thrive on destruction and don't really understand why blow up some human vehicles is such a big deal (hey, accidents happen!), you do think that \cJuliet{} taking the blame will undo all of the work with humans \cJuliet{\they} was able to do, and would likely lower both of your standing with \cQueen{}.

While many humans are little more than easily flammable playthings, or perhaps potential slaves, there are a select few who are much more useful.  

%to be continued with description of mad scientist cooperation and enslave elementals plot.

And that is what brought you here, to this meeting of humans and elementals.  While most are here to talk of peace, you know that many will also attempt to gain power for their own faction.  You are here to support your Queen, but more importantly, you are here to maintain Fire's authority on this plane.
% to be continued with Pyro's opinions on the conduit, the treaty, etc.

\end{document}
