\documentclass[char]{elementals}
\begin{document}
\name{\cRogue{}}

You are \cRogue{\intro}, a high-ranking earth elemental who has broken with the hierarchy.

You were the first of the earth elementals in this plane to separate from your King, \cEarthKing{}.  Though many others followed, for a brief period it was just the two of you.  As a result, you are closer to the King than those who followed.  \cEarthKing{\They} views you as closer to an equal than the others, and respects your autonomy even when you disagree.  Whereas with even the strongest of your siblings, such as \cLoyal{\intro}, \cEarthKing{} might enforce his orders with enslavement, \cEarthKing{\they} has always been more lenient with you.  You appreciate this trust, and do your best to deserve it.  You only go against the King's orders when you feel it is truly necessary.  Unfortunately, this has been all too common lately.

The other elementals know that you are close to the King, and that he allows you to act independently, but they do not know that you were the first to separate and therefore the most powerful.  \cLoyal{}, in particular, has never figured out whether \cLoyal{\they} is senior to you or not.  Because of \cLoyal{\their} obsession with hierarchy, this drives \cLoyal{\them} crazy.  Though \cLoyal{\they} suspects you are the most senior, you let \cLoyal{\them} believe \cLoyal{\they} is more powerful than you by holding back in combat and pretending to be enslaved whenever \cLoyal{\they} attempts it.  \cLoyal{} is so thoroughly bound by the King's word that \cLoyal{\they} has never thought to command you to do anything particularly distasteful, and so you've always just played along.  You're not overly fond of hierarchy, and enjoy making life difficult for those who are.

Because you have been around for nearly a hundred years, you have had plenty of time to observe the changing strength of the elementals.  You have noticed not only yourself and your King getting weaker, but all the members of the other factions that you have done battle with on and off.  Most frighteningly, though, \cEarthKing{} seems to be weakening faster than any of the others.  Ever since you realized this, you have been searching desperately for a way to reverse it.  Through covert observation and interrogating humans, you've confirmed that none of the other elemental leaders are being affected the same way.

When you returned to your King and informed him that he was weakening faster than the other leaders, he was appropriately shocked, but concluded that he must just be ill.  Apparently before coming to this plane, whenever \cEarthKing{\they} was feeling weak \cEarthKing{\they} would seek out ``the quintessence,'' a fifth type of elemental who would give \cEarthKing{\them} some mystical healing substance.  \cEarthKing{\Their} response to your news has been an obsession with obtaining this substance, which may or may not exist in this plane.  You, however, think that the substance will be only a temporary solution at best.

While you haven't been able to produce any evidence, and the other earth elementals including both \cEarthKing{} and \cLoyal{} just laugh whenever you bring it up, you're convinced that \cEarthKing{}'s weakness must somehow be the doing of air elementals.  Unfortunately, you've been completely unable to find any information on how they're doing it or how to stop them.  And even if you could convince your fellow earth elementals that the air elementals were at fault, the King's weakness means that their faction is now decidedly more powerful than yours.  As a result, you have little hope for putting a stop to their plans.  This has led you to the conclusion that the balance of power on this plane is tilted too far in favor of air.  Your best course of action, you've concluded, is to return all the elementals to the original plane your King described, where balance is maintained by the quintessence and air would not be able to overpower earth.  You would lose some freedom, certainly, and you're not fond of the idea that the more powerful earth elementals there could enslave both you and your King, but it's a small price to pay for your parent's survival.

You've heard that there is a human scientist attending the meeting this evening who studies the Conduit, and you suspect this scientist and perhaps some other humans may be willing and able to help you toward your goals.  After all, elementals in general (including you, really) haven't exactly made life easy for humans, and this is their home plane.  It might take some delicacy to broach the subject, however, since  the humans might be hesitant to admit to elementals that they're looking to banish them all.  To make matters worse, you're not great at telling humans apart, you've never met this particular human, and there are a few scientists attending the meeting so you'll need to ask around while revealing as little of your intentions as possible.

\cLoyal{}, of course, is here on the King's orders to try to obtain the mysterious healing substance by any means necessary.  If that turns out to be impossible, you might be able to convince \cLoyal{\them} (and, by extension, \cMinion{}, who  dutifully follows \cLoyal{}'s commands or risks enslavement) to help you with your goal of returning to the elemental plane.  However, due to \cLoyal{}'s temperament, proving to \cLoyal{\them} that the substance is unattainable might require substantial work.  You could also give up your game and enslave \cLoyal{\them}, but even showing that you outrank \cLoyal{} might not be sufficient to earn \cLoyal{\their} obedience at this point, since your consistent displays of disregard for ranking have given \cLoyal{} a rather low opinion of you.

\begin{itemz}[Goals]
\item Find a way to return all the elementals to the elemental plane.  At a minimum, you want to return all of the earth elementals.  You don't particularly care what happens to the others.  Since \cEarthKing{} is neither present nor willing, however, you may need to send the other factions back, too.
   \item Don't tip off the other elementals about your plan to send them all home.  They likely won't want to go, and will make life difficult for you if they find out.
   \item Watch out for your King and your faction.  If you cannot return to the elemental plane, do what you can to help your King in this plane and restore the balance between earth and air.
	\item Find evidence that the air elementals are up to something.  Make life difficult for them in any way possible.
	\item Mess with \cLoyal{}.  You don't particularly like \cLoyal{\them}.  However, you might need to work with \cLoyal{\them} at some point, so don't completely burn the bridge.
\end{itemz}

\begin{contacts}
	\contact{\cLoyal{}}  The official representative of \cEarthKing{} at this gathering.  Bossy, obsessed with hierarchy, and just all-around annoying.
	\contact{\cMinion{}}  A young earth elemental who \cEarthKing{} sent to work with \cLoyal{}.  Obedient because \cMinion{\they} has to be, around \cLoyal{}, but you get the sense \cMinion{\they}'s  alright.
  \contact{\cMiniEarth{}}  Another young earth elemental who \cLoyal{} ordered to attend the meeting.  \cMiniEarth{\They} seems less content with subservience than \cMinion{}.
\end{contacts}

\end{document}
