\documentclass[char]{elementals}
\begin{document}
\name{\cRomeo{}}

You are \cRomeo{\intro}, bodyguard to \cLeader{\intro}, the President of the humans.

You are an Alpha Azi, meaning you are among the elite, genetically modified to have genius-level intelligence, psychologically designed to be self-directed and capable of independent thought within the constraints of your programming.  That is to say, \cLeader{} can give you a broad directive, and you can interpret and enact it without getting step-by-step instructions.  In your childhood, you received training in the Barracks with the other Azi selected to be soldiers or security guards: the Alphas, who are generally partnered with a Cit of equal intelligence; the Betas, who are methodical and diligent and do well as long as they report to a Cit or an Alpha Azi; the Gammas, who have less initiative and require detailed instructions; and so on.

After you completed all your training, you were assigned to \cLeader{}, the scion of a family that has been prominent in human society since the first Opening that brought elementals to earth a hundred years ago.  \cLeader{\Their} forebears played an important role in rallying humans during those dark times, when the elementals ravaged the cities and wantonly incinerated, smothered, or drowned any living creature in their path.  Over the years, as humans adapted to coexistence with the elementals, \cLeader{}'s family was instrumental in initiating diplomatic relations with them.  As a result, when Cits re-established the birth labs and began producing Azi again, the son of the \cLeader{\formal} family was among the first to receive an Alpha Azi companion, namely you.

As soon as you finished your Barracks training, you were called to your training supervisor's office to receive your formal Contract binding you to \cLeader{}.  \cLeader{\They} is your Supervisor, the one in whom you have complete trust, to whom you turn when you experience any psychological conflict.  Azi are very logical, while Cits are bafflingly emotional -- dealing with them can be very confusing, and yet, it is unavoidable in your role as head of security.  \cLeader{} is the one who resolves all difficulties.  This is in your Contract.  The two of you have been together since you were both youths, before \cLeader{\they} began his ascent to power, and you are like family.  You are absolutely loyal to \cLeader{\them}.

As \cLeader{}'s head of security, your responsibility is to protect and aid \cLeader{\them}.  Because the human-elemental peace treaty is very important to \cLeader{\them}, you collect information about key players that might be helpful, functioning as \cLeader{\their} intelligence officer.  You also forestall assassination attempts from both humans and elementals who disagree with \cLeader{\their} political views, meaning you investigate everyone with whom \cLeader{\they} comes into contact, including \cLeader{\their} second-in-command, the smooth-tongued Secretary of State \cDema{\intro}.  To make your job easier, the scientist Galina Schwartz, whose Azi assistant \cScientist{\intro} is also attending the meeting, has sent you an experimental belt that may offer some protection against elemental attacks.  It is not fully functional yet, but perhaps you can get it to work so you can give it to \cLeader{}.

One elemental you meet regularly is King \cKing{\intro} of the Air faction, who has expressed interest in an alliance with humans.  The Air elementals are the most friendly of the four factions, but you remain wary of them on principle.  Another elemental you see often is \cJuliet{\intro}, a Fire elemental who acts as an intermediary between the Fire Queen, \cQueen{\intro}, and King \cKing{}.  Even though Fire elementals in general aren't particularly friendly towards humans and all too frequently incinerate humans by accident or through neglect, \cJuliet{} seems different.  The more you interacted with \cJuliet{\them}, the more you grew to appreciate \cJuliet{\their} company.  \cJuliet{\They} is intelligent and trustworthy (or so you thought), and at some point you examined your feelings and concluded that you love \cJuliet{\them}.  Luckily \cLeader{} has been cautiously supportive of your relationship, mostly because \cLeader{\they} cares about you and wants you to be happy.  You've also received encouragement from one of the diplomats, an Azi named \cDiplomat{\intro}, which you appreciate, but you remain suspicious of anyone who is not your Supervisor.  Besides, unlike \cLeader{}, \cDiplomat{\they} has an ulterior motive for being helpful: \cDiplomat{}'s goal is to achieve a human-elemental treaty.

Even with \cLeader{} and \cDiplomat{}'s help, though, finding opportunities to meet \cJuliet{} in private has been challenging.  Negotiating all the cultural and \emph{species} differences has also been tricky.   But you've been making things work.  In fact, the two of you have even been talking about marriage recently!  \cLeader{} could perform the ceremony, of course, but  \cLeader{\they} worries too much, and you just know you'll get a lecture (possibly even during the ceremony) about how you might get toasted (ha ha ha) by a Fire elemental on your wedding night.  \cDiplomat{} could also perform the ceremony, but he'd probably want to make a huge deal of it publicly: ``Look, humans and elementals \emph{can} coexist peacefully!"  Neither you nor \cJuliet{} likes that idea much....  That leaves the other diplomat, \cAvatar{\full}.  Perhaps you could quietly investigate whether \cAvatar{\they} is certified to perform marriages, and if so, whether \cAvatar{\they}'d be a good choice.  (And, of course, you'd have to convince \cJuliet{} that a human wedding is necessary.  Apparently elementals have their own sort of marriage ceremony?)

Basically, things were going so well between the two of you -- up until recently, when two airplanes were knocked out of the sky by an elemental, killing hundreds of humans.  King \cKing{} has told \cLeader{} that \cJuliet{} did it.  \cJuliet{\They} denies it, but you still want to have a private conversation with her to confirm that.  If \cJuliet{\they} is guilty, you will have no choice but to break up with her and report her crime to your Supervisor.  You hate the thought of doing so, but it is the only action that is consistent with logic and with your programming.  If \cJuliet{} is innocent, though, let the wedding bells ring!  One way or another, the future of your relationship will be decided at this meeting!




\begin{itemz}[Goals]
  \item Investigate everyone around \cLeader{\full}!  \cLeader{\They} has many enemies, both elemental and human, and it is your duty as head of security to identify them.
  \item Help \cLeader{} get the human-elemental peace treaty signed by finding out information about key players.
  \item Look after \cScientist{\full} and see if you can help \cScientist{\them}, for example by kicking intruders out of \cScientist{\their} lab so \cScientist{\they} can focus!  It's the least you can do for Galina Schwartz, who has done you a favor by sending you the experimental belt.
  \item Keep any elementals from finding out about your relationship with \cJuliet{}.
  \item Find out what \cJuliet{} had to do with those airplanes, if anything.
  \item Investigate different ways that a human and elemental could get married.
  \item Keep an eye on Secretary of State \cDema{\full}.  \cDema{\Their} family was prominent in the Extinguishers group, \cDema{\their} parents were executed for their crimes, and 
  \cDema{\they} \cDema{\themself} was once a member.
\end{itemz}

\begin{contacts}
  \contact{\cLeader{}} President of the humans and your Supervisor.  You are absolutely loyal to \cLeader{\them}.
  \contact{\cAvatar{}} Head diplomat, whose life goal is to negotiate a human-elemental peace treaty.
  \contact{\cDiplomat{}} An Azi diplomat who encourages your relationship with \cJuliet{} for political reasons.
  \contact{\cScientist{}} An Azi scientist, whom you've promised to look after at the meeting.
  \contact{\cDema{}} Secretary of state of the humans.  You're keeping an eye on \cDema{\them}, just in case \cDema{\they} gets over-ambitious.
  \contact{\cJuliet{}} A Fire elemental who acts as an intermediary between the Fire Queen and Air King.  Also the love of your life.
  \contact{\cKing{}} King of the Air elementals who may sign a peace treaty with humans.
\end{contacts}






\end{document}
