\documentclass[char]{guildcamp1}
\begin{document}
\name{\cScientist{}}

Thirty days.  That is the expected length of your life.  You have an inoperable brain tumor, and there's nothing you can do to save yourself.  You've researched every case recorded on any database of medical records, even the databases that required some hacking to access, and you haven't found word of a cure anywhere.  All you've found is cold, hopeless statistics.  The standard deviation of the length of your life is twenty days.  You had better make the best of the time you have.

You are a world-renowned artificial intelligence researcher. You specialize in creating simulated worlds that are incomparably more realistic than any previous game or simulation.  Twenty years ago, a breakthrough in custom circuit design allowed researchers to start making neural networks with a trillion simulated neurons, ten times the number there are in the human brain.  Of course this terrific hardware is useless without the machine learning software to run on it, and that is were you came in.  You received your PhD  22 years ago for creating a revolutionary new approach to machine learning on this custom hardware.  Ever since then you have been working in the largest research lab in the world improving your ideas and making them a reality. Your most recent project is the Mental Amplifier, a machine that can 'read' brainwaves and translate them into images.

One of the goals of your life has been to win the International Medal of Science Award, the highest honor a scientist in any field can receive, for your work.  You had thought that you had decades to win this award, but with you brain tumor you realize you will either win it this year - tomorrow in fact - or you will never experience that achievement.  The two serious contenders for the award are you and Dr.~\cRival{\intro{}}, whom you have a bit of a history with.  

You and \cRival{} became enemies when he was still in high school.  You were proctoring the International Computing Olympiad, and caught \cRival{} sabotaging another competitor's computer, attempting to fail them. You quickly disqualified them, but to your amazement \cRival{}'s sponsoring school gave them nothing more than a slap on the wrist. Years later, you read \cRival{}'s papers, many of which bordered on plagiarism of your colleagues' unfinished work, as well as your own. How is this punk kid finding out about the work of senior scientists? Unable to fight back, you have tried to discredit \cRival{}'s work whenever possible, even when it models your own. You have learned to back up your work, encrypted, on several different servers, to always carry an extra laptop in case the first is hacked into, and to never turn you back on \cRival{} when you are at conferences together. Rather than carry around the paper portion of your submission to the International Medal of Science Award, you have stashed it safely in your room, and modified the lock on the room so it is harder for anyone to break into.

But that's professional misconduct. \cRival{}'s latest insult was far more personal.

Six months ago \cRival{} hacked into your doctor's computer, learned of your disease, and forwarded the details to several blogging sites. That was too far. At least \cKid{} hasn't found out yet. You are sure it would devastate him. You dove into \cRival{}'s past, and unearthed his political affiliations. He had frequent correspondence with radical political groups, and often visited websites with radical content. None of this was illegal, but you're sure that if this were made public, it would ruin \cRival{}'s budding career.

You have done some contracting for the military in the past.  Using your artificial brain, they have created drones that can follow high level commands like ``Find and capture a person who looks like this picture and lives in that village.''  You are very pleased with the models, and are sure that it will perform famously. You have found out that a blueprint of your drone is actually being stored in a high security room at this very hotel. You aren't sure why, but it is turning out to be a golden opportunity.  When you were doing your investigation into \cRival{}, you read an email that suggested that he is planning to steal the prototype.  To secure the drone blueprint and show the world once and for all what a delinquent \cRival{} is, you have a plan to install a camera in the room where your prototype is stored.  You hope to catch Rival in the act of stealing it.

You've never been a social butterfly, usually dedicating yourself wholeheartedly to your work. But you have allowed yourself one romantic relationship.  Nine years ago, you fell in love with \cGroomA{\intro{}} when you met him through your military consulting work.  You are not usually sentimental, but your research had been going poorly at the time and your hormones took control. For two years you spent almost all your waking time (and all your sleeping time) with \cGroomA{}, even spending less time on your precious research to spend more time with him.  You became pregnant and were planning to raise a child with him. You were just about to tell him, when you discovered his betrayal.  He was selling your drones to authoritarian dictators to help them track down dissenters.  How could be abuse your work like that, using elegant ideas for evil?  You left him the next day.  You mentioned the child in your womb, but you decided you didn't want anything more from this man.
 
Well, at least your relationship with \cGroomA{} did produce one remarkable result, your child \cKid{}. You had never pegged yourself as a motherly type, but you have loved \cKid{} since the first moment you laid eyes on \cKid{\them}.  You're sorry to say that \cKid{} has probably spent more time with your nanny than with you, but the times you have shared have been truly special.  It is essential that \cKid{\they} has a good home after you pass away, and since you have no close living relatives, you have decided to forgive \cGroomA{} and transfer custody of \cKid{} to \cGroomA{\them}}.  You've been telling \cKid{} about \cKid{\their} wonderful father for the last month, and you're sure \cGroomA{} will melt and accept \cKid{} when \cGroomA{\they} sees how excited \cKid{} is to be with \cKid{\their} father.

The doctors have prescribed you painkillers, a chemical similar to a street drug called ``Bite.'' It works well, though there are hallucination-like side effects. You've noticed that if you inject it, the side effects are less powerful than if you eat it (if eaten, Bite causes hallucinations for 5 minutes. If injected with a Syringe and water, the hallucinations last for 2 minutes).

You have always been a strong atheist.  Ever since you learned of your tumor you have vaguely wished there were a life after death, or some supernatural way to cheat an untimely death.  But you value truth far too highly to entertain wishful thinking.  The cold, hard truth is that this universe and this life are all you have.




\begin{itemz}[Goals]
  \item Convince \cGroomA{} to take care of \cKid{} once you're gone.
  \item Make sure \cKid{} doesn't find out about your disease. You couldn't bear \cKid{\them} to know \cKid{\they}'s going to lose \cKid{\their} mom yet.
  \item Catch \cRival{} stealing military secrets.
  \item Complete your Mental Amplifier. You still want to win the International Medal of Science, after all!
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cRival{}} That hooligan, who seems to slip through all the cracks and steal your credit! You're going to bring them to justice this time.
  \contact{\cGroomA{}} Your old flame. His dealings were shady, but he really was a decent fellow. He's getting married, but with so little time left you don't have a choice but to confront him now.
    \contact{\cKid{}} Your beloved \cKid{\offspring}, 7 years old. \cKid{\they}'s a rascal, but you adore \cKid{\them}.
\end{contacts}


\end{document}
