\documentclass[white]{guildcamp1}
\begin{document}
\name{\wHeadMountedDisplay{}}

\emph{(This counts as a transferable ability)}

This is a stack of research notes on how to build a head-mounted display, and modify it to read and respond to the mental patterns of the wearer. If you are not the original owner of this whitesheet, you will have to spend five minutes studying it before you can begin any of the tasks.

The display is meant to be completed in a suitably-equipped workshop, but you think it might be possible using household materials. To create the ``Completed head-mounted display'' (Item \#772), you must complete the following tasks:

\begin{enumerate}
\item Bounce your ideas for jury rigging the display off of someone. To do this, spend 2 minutes explaining what you plan to do to another character.
\item Test the incomplete head-mounted display on someone other than yourself. To do this, declare that you are putting the head-mounted display on. You must have a willing or helpless (but conscious) volunteer. Hand the item card ``Incomplete head-mounted display'' to the character you are putting it on. They spend 3 minutes in a unable to interact with anyone or anything, since they have the non-functional display on.
\item  Next you need to collect the following items:
\begin{enumerate}
\item The  ``Incomplete head-mounted display'' (Item \#771)
\item A \bf{processor} (often found in personal laptops)
\item A \bf{magnet}
\item A \bf{soldering iron}
\end{enumerate}
\item Then, spend three minutes in total secrecy with all of the items, assembling the display. Constructing the display will destroy all of the items.  When this is complete, you can see a GM to receive the item card, or simply modify Item \#771.
\item Test the completed head-mounted display on someone else. To do this, declare that you are putting the head-mounted display on someone, and hand them the item. You must have a willing or helpless (but conscious) volunteer. They spend 3 minutes inside a simulated war game, and see everything around them as a war zone. This includes seeing other characters as soldiers. Roleplay accordingly.
\end{enumerate}

Once it has been tested, your head-mounted display is ready for use. Congratulations.

\end{document}
