\documentclass[white]{guildcamp1}
\begin{document}
\name{\wMentalAmplifier{}}

\emph{(This counts as a transferable ability)}

This is a stack of research notes on how to build a mental amplifier, which increases a wearer's brain patterns so they are easier to read by other machines such as MRIs. If you are not the original owner of this whitesheet, you will have to spend five minutes studying it before you can begin any of the tasks.

The amplifier is meant to be completed in a suitably-equipped workshop, but you think it might be possible using household materials. To create the ``Completed mental amplifier'' (Item \#774), you must complete the following tasks: 

\begin{enumerate}
\item Bounce your ideas for jury rigging the amplifier off of someone. To do this, spend 2 minutes explaining what you plan to do to another character.
\item Test the incomplete mental amplifier on someone other than yourself. To do this, declare that you are activating the mental amplifier. You must have a willing or helpless (but conscious) volunteer. Hand the item card ``Incomplete mental amplifier'' to the character you are activating it on. They spend 3 minutes unable to speak or otherwise communicate with anyone. When you turn the amplifier off, they can't remember anything and have total amnesia for three minutes (their memories return intact at the end of this time) role-play accordingly. 
\item  Next you need to collect the following items:
\item Collect the following items:
\begin{enumerate}
\item The  \bf{Incomplete mental amplifier} (Item \#773)
\item A \bf{solenoid} (often found in television sets)
\item Some \bf{copper wire}
\item Some \bf{steel wool}
\end{enumerate}
\item: Then, spend three minutes in total secrecy with all of the items, assembling the display. Constructing the display will destroy all of the items.  When this is complete, you can see a GM to receive the item card, or simply modify Item \#773.
\item Test the completed mental amplifier on someone else. To do this, declare that you are activating the mental amplifier on someone, and hand them the item. You must have a willing or helpless (but conscious) volunteer. They spend 3 minutes babbling incessantly in a ``stream of consciousness'' fashion.
\end{enumerate}

Once it has been tested, your mental amplifier is ready for use. Congratulations.

\end{document}
