\documentclass[green]{elementals}
\begin{document}
\name{\gElementalEggs{}}

These tiny elementals you have found correspond to the infantile forms of powerful elementals. They are strong enough that, once grown up, they could significantly disrupt the balance of power in their faction's power. Unfortunately, elementals age slowly and it will be over a decade before their power starts to manifest. In the meantime, you will have to look after them.

Young elementals require periodic attention to develop properly, especially in their current form when they are just starting to form an independent consciousness. Proper care involves the following steps:
\begin{enumerate}
  \item They must be kept constantly immersed in their element. This typically means keeping them on or near the body of an elemental.
  \item Once every thirty minutes, the eggs should be cleansed in a ``natural source'' of elemental power for one minute. For fire elementals, this would be lava or a pool of fire, for water elementals a pond, and so on. Roleplay their cleansing accordingly.
  \item Periodically (approximately once every ten minutes) the elementals must be shaken to prevent them from falling asleep; sleepiness breeds weakness and prevents them from developing a strong and independent psyche. \emph{Bounce the physrep a few times to shake the elemental.}
\end{enumerate}

Properly cared for, these elementals will prove a valuable asset. On the other hand, if the baby elementals go for too long without being in the presence of their element they may suffer greatly or even die of starvation.

Typically, elementals are very protective of their young and taking or attack them is comparable to attacking a human child.

\end{document}
%%Machine has 1 number and instructions
%%Each conduit location has 2 pages. covered page has list of numbers that are active at different times
%%Check for prime(?) factors