\documentclass[green]{elementals}
\begin{document}
\name{\gEnslave{}} 

Enslavement is a CR driven ability. The mechanic works like this:

\begin{enumerate}
 \item The user points at their target and states ``Enslave'' and their base CR (do {\bf not} count assists or item modifiers. Any CR \emph{penalties} {\bf do} affect CR for this ability). For example, if I have a CR of 2 and the ability, I would point at my target and say ``Enslave 2''. 
 \item The target player may resist this ability with their CR (do {\bf not} count item modifiers. Any CR \emph{penalties} {\bf do} affect CR for resisting this ability) if they are able to do so (like any Dark Water combat ability). If they do so, the ability fails to take effect immediately. For example, if my target has a CR of 3, they can simply say ``Resist'', and my ability fails.
 \item If the target player does {\bf not} resist, the user of the ability must now incant ``I enslave you 1'', ``I enslave you 2'', etc, up to a count of 10. {\bf The target player is completely mesmerized and can take no action during the count.}
 \item Any {\bf other} player can interrupt the action during the count by saying ``I stop you'' from within 1 Zoc.
\end{enumerate}

If you are enslaved, you are compelled to do as your enslaver ask for 5 minutes. You {\bf can} be compelled to perform any action that is not suicide. You {\bf can} be compelled  to discuss a given topic. You {\bf cannot} be compelled to reveal specific information unless you know otherwise. For example: ``Tell me about this machine'' is a valid command, ``Tell me exactly what you plan to do with this machine'' is not.

{\bf Someone who is successfully enslaved once is not vulnerable to being enslaved a second time for 30 minutes.}

\end{document}
