\documentclass[green]{elementals}
\begin{document}
\name{\gConduit{}}

You know how to use ``\iCart{}'' to open a conduit to the elemental plane.

Read the entire process before beginning. A GM must be present before step 2 begins.

If you would like to open the conduit, you must follow these steps:
\begin{enumerate}
  \item Locate the current point of closest contact. (See \gConduitCover{})
  \item Consume 1 energy source. (Tear up the item card)
  \begin{itemize}
  	\item \iBattery{} may be used if a human is participating in the opening.
  	\item \iCrystalGeode{} containing a blue geode may be used if an earth elemental is participating.
  	\item \iLavaEmber{} may be used if a fire elemental is participating.
  	\item \iHandCrank{} may be used if an air elemental is participating
  	\item you only need {\bf 1} energy source.
  \end{itemize}
  \item Declare which ability/abilities are being used for the opening. Each participant my contribute only one ability. Hold the ability card in your hand so it is visible for the duration of the ritual. At least 1 participant must use the ability ``\aWorkConduit{}''. 
  \item All players participating in the opening spend 3 minutes opening the conduit, roleplay accordingly.
  \item The GM will reveal what happens.
\end{enumerate}

\vspace{10mm}

{\large Important notes:}

\begin{itemize}
  \item Anyone who is not involved in opening the conduit or modifying the process in some way can walk up and observe the abilities being used. (\emph{The actions you are performing are obvious}).
  \item \emph{Withdrawing} abilities
  \begin{itemize}
  	\item If you participate in darkwater combat, notice a waylay attempt, or talk to a player not involved in opening the conduit, you \emph{withdraw} your action.
  	\item You may at any time choose to \emph{withdraw} your action and stop participating in the ritual. 
  	\item \emph{Withdrawn} abilities will not affect the outcome of the ritual.
  	\item ``\aWorkConduit{}'' is a special case. See ``Interrupting'' below.
  \end{itemize}
  \item \emph{Interrupting} the ritual
  \begin{itemize}
  	\item If the ``\aWorkConduit{}'' ability is withdrawn, the whole ritual is interrupted. It stops immediately and no effects are proccessed.
  	\item Someone {\bf not} participating in the ritual may interrupt the ritual by saying ``I stop you.'' Individual abilities may not be targeted in this way, the whole ritual must be interrupted.
  \end{itemize}
\end{itemize}
\end{document}
