\documentclass[green]{elementals}
\begin{document}
\name{\gSealingLocations{}}

In the name of maintaining your advantage on this plane you intend to prevent anyone from opening the conduit tonight.  To do this, you will have to seal the possible conduit locations. This also leads to your ultimate goal of sealing the conduit permenantly. To seal the conduits, you will need to draw a rune of sealing across the location in a mixture of human blood and elemental essence.

To seal a conduit location:
\begin{enumerate}
  \item Acquire a vial of human blood. To do this you must first have a vial (item number: ). Then draw blood for 30 seconds using a syringe (item number: ) on a willing or helpless target. You may also take up to 2 vials of blood from a wounded target without a syringe. Write on the item card that this vial contains human blood.
  \item Acquire an elemental essence. You can either use an essence that already exists, or you can make one. If you desire to make one, acquire a vial. Take the vial to the Kitchens (Room -032), Pond (Room -), Cellar (Room -) or the Tower (Hallway off of -002). Leave the vial for 10 minutes to collect essence (You have given it the power to attract residual essence, but this is un-obvious. To anyone else it is just an empty vial). You do not have to stay in the location for this period of time. Once you retrieve the vial that has been imbued with elemental essence, write on the item card that this vial contains elemental essence.
  \item Empty the contents of both vials over the location you wish to seal (tear up the item cards)
  \item Spend 2 minutes mixing the blood and essence and shaping the rune of sealing. If anyone asks you what you are doing (``What do I see''), explain to them that they see you spreading a dark, sticky substance over this location.
  \item Place a ``SIGN OF INDETERMINATE NAME'' over the conduit location to indicate that it has been sealed. This sign contains instructions for un-sealing the location.
  \item Wash your hands at the kitchen sink or in the pond. (spend 30 seconds with your hand on the sign). Until you do so, your hands are covered in a dark, sticky substance that smells strongly. You must announce this to anyone who attempts to engage you in conversation.
\end{enumerate}
Unfortunately, this seal is not permenant until it sets. The mixture will not set for several hours. Until then, someone could wash your seal off.

\end{document}
