\documentclass[green]{elementals}
\begin{document}
\name{\gTreaty{}}

Formalizing a human/elemental treaty is a big step toward eventual peace between humans and elementals. Like all such political documents, there is a formal process for formalizing a treaty.

If you would like to formalize a treaty between humans and an elemental faction, you must follow these steps:
\begin{enumerate}
  \item Obtain verbal confirmation from the current leader of the humans, and the current leader of the elemental faction in question that they agree to a treaty.
  \item Compose an introductory paragraph expressing your desires for the treaty.  Write it down.
  \item Obtain a \emph{written} paragraph from the leader of the humans enumerating the commitments that humans offer. (If necessary, transfer it to the same page with your introduction.)
  \item Obtain a \emph{written} paragraph from the leader of the elemental faction enumerating the commitments that the elementals offer. (If necessary, transfer it to the same page with your introduction.)
  \item Once both leaders agree to the terms of the treaty, have both of them sign the treaty at a public ceremony.  The audience should include at least 3 humans, all surviving members of the elemental faction committing to the treaty, and one elemental from a different faction. At the ceremony someone must make a brief speech summarizing the key points of the treaty. 
  \item Ask if there are any objections. If anyone objects, for any reason, the treaty cannot be formalized until their objection is met. Once any objections are addressed, you may proceed.
  \item Sign the treaty yourself and obtain the signature of 1 other witness. (There should be 4 signatures on the treaty at this point.)
  \item Make a public announcement of the treaty by telling at least 2 people who were not at the ceremony.  Then post the treaty in a public location.
\end{enumerate}

Once the treaty has been signed by the leaders at the ceremony, both parties are expected to abide by the terms. Make sure everyone understands this before he or she signs.

\end{document}
%%Machine has 1 number and instructions
%%Each conduit location has 2 pages. covered page has list of numbers that are active at different times
%%Check for prime(?) factors